---
title: "PenaltyComp_MissingData"
output: pdf_document
date: "2025-07-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(igraph)
library(network)
library(intergraph)
library(ergm)
library(gridExtra)
library(RColorBrewer)
library(ggpubr)
library(kableExtra)
library(ggside)
```


## Reading te data files and the combination files.
Box folder                                               Initparam Files                          Notes:
PenaltyCompContRandInitMissing                           InitParamMiss_DegInit_Missing            Rerun this. The undirected networks did really well here. This is uspiscious .INITIALIZE with random INIT instead of DEG INIT.

PenaltyComparisonGLMNETDegInit                           InitParamMiss_DegInit_Missing                      
PenaltyCompContRandInitMissingDirOnlyNoCov               InitParamMiss_DegInit_MissingDirOnly
PenaltyCompContRandInitMissingDirOnly                    InitParamMiss_DegInit_MissingDirOnly
PenaltyCompContRandInitMissingDirOnlySeedSet             InitParam_DegInit_Miss_MultCovInit_Dir
PenaltyCompContDegInitMissingDirOnlySeedSet              InitParam_DegInit_Miss_MultCovInit_Dir
PenaltyCompContDegInitMissingDirOnlySeedSetDriNode       InitParam_DegInit_Miss_AllCovInit
PenaltyCompContDegInitMissingDirOnlySeedSetDriNodeNocov  InitParam_DegInit_Miss_AllCovInit
NWMetrics TTT                                            InitParam_NetworkMetrics
InitParam_DegInit_Miss_Med FTF                           InitParam_DegInit_Miss_Med


```{r}
getwd()
## Reading combination of parameters
filePath <- "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Code/InitParam_NetworkMetrics_comb.rds"
S <- readRDS(filePath)

## Reading names of files
boxFolder <- "C:/Users/gauph/Box/SimulationOutput/CoDAOP/NWMetrics/"
files <- list.files(boxFolder)

```

```{r}
## Set these based on nocov or cov
nocov = T
NWmetrics = T
regcov = T
if(NWmetrics == TRUE){
  metricsMat <- matrix(0, nrow =0 , ncol = 18)
}

if(nocov == TRUE){
  df_nocov <- matrix(0, nrow =0, ncol = 9)
}
if(regcov == TRUE){
  df_reg <- matrix(0, nrow =0, ncol = 12)
}

nc <- 3
N <- 100
nsim <- S$Nsim[1]
bigN <- S$bigN[1]
p <- matrix(0, nrow =0, ncol = 8)
dir <- c("directed","undirected")
bigNv <- rep(1:bigN , each = nsim*length(dir))
nsimv <- rep(rep(1:nsim, each = length(dir)), times = bigN)
dirv <- rep(dir, times = bigN*nsim)
corMat <- matrix(0, nrow =0 , ncol = 21)

for(fn in files){
  df_rds <- readRDS(paste0(boxFolder,fn))
  sIdx <- as.numeric(str_extract_all(fn, "\\d+")[[1]])[1]
  seqv <- 1:length(df_rds[[1]])
  for(i in seqv){
    
    ##find the output from graph laplacian 
    #eig <- list(0,0)#FindGraphLaplacian(df_rds[[6]][[i]], dirv[q])
    df_reg <- rbind(df_reg, c(tail(df_rds[[1]][[i]]$OmegaIndex,1),
                              tail(df_rds[[1]][[i]]$MSE,1),sIdx, 
                              df_rds[[1]][[i]][[20]],
                              length(df_rds[[1]][[i]]$Loglik[,1]),
                              bigNv[i],nsimv[i],
                              as.character(df_rds[[8]]$penalty[[1]]), 
                              dirv[i],S$dist[sIdx][[1]] ))
  }
  
  params <- as.data.frame(df_rds[[8]])
  tmp_p <- as.data.frame(cbind(unlist(params$alpha), unlist(params$alphaLL), 
                               unlist(params$lambda),unlist(params$alphaLin), 
                               S$pClustOL[[sIdx]],
                               ifelse(is.null(params$missing[[1]][[1]][1]), 
                                      0, 
                                      params$missing[[1]][[1]][1]),
                               S$covInit[[sIdx]]))
  p <- rbind(p,tmp_p)# %>% uncount(weights = length(dir)))
  
  
  if(NWmetrics == TRUE){
    metricsMat <- rbind(metricsMat,cbind(df_rds[[9]],sIdx))
  }
  
  if(nocov == TRUE){
    if(length(df_rds[[2]]) > 0){
      for(i in seqv){
        if(!is.null(df_rds[[2]][[i]])){
          df_nocov <- rbind(df_nocov, c(tail(df_rds[[2]][[i]]$OmegaIndex,1),sIdx, 
                                        df_rds[[2]][[i]][[20]], S$alpha[[sIdx]], 
                                        dirv[i], S$pClustOL[[sIdx]],bigNv[i],nsimv[i],
                                        length(df_rds[[2]][[i]]$Loglik[,1])))
        }
      }
    }
  }
}

p <- as.data.frame(apply(as.data.frame(p), 2, unlist))
df_reg <- as.data.frame(df_reg)
df_reg <- cbind(df_reg, p)
colnames(df_reg) <- c("OI","MSE1","MSE2","MSE3","Idx","Failure","iter_reg","bigN",
                      "Nsim","penalty","dir", "dist","alpha", "alphaLL","lambda",
                      "alphaLin","OL","MissPct", "covInit")
df_reg <- as.data.frame(df_reg)
#df_reg$bigN <- #c(rep(1:30, each =2))
df_reg$Failure <- ifelse(df_reg$Failure == 1, "TRUE", "FALSE")
df_reg$Wts <- TRUE
df_reg$OI <- as.numeric(df_reg$OI)
df_reg$MSE1 <- round(as.numeric(df_reg$MSE1),3)
df_reg$MSE2 <- round(as.numeric(df_reg$MSE2),3)
df_reg$MSE3 <- round(as.numeric(df_reg$MSE3),3)
df_reg$iter_reg <- as.numeric(df_reg$iter_reg)

df_reg$bigN <- as.numeric(df_reg$bigN)
df_reg$Nsim <- as.numeric(df_reg$Nsim)
df_reg$Idx <- as.numeric(df_reg$Idx)
df_reg <- df_reg[order(df_reg$Idx),]
metricsMat <- as.data.frame(metricsMat)
metricsMat$sIdx <- as.numeric(metricsMat$sIdx)
metricsMat <- metricsMat[order(metricsMat$sIdx),]

```



## Reading nocovariate simlations

```{r}
## Reading nocov if done separately
filePath <- "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Code/InitParam_DegInit_Miss_AllCovInit_comb.rds"
S <- readRDS(filePath)
boxFolder <- "C:/Users/gauph/Box/SimulationOutput/CoDAOP/PenaltyCompContDegInitMissingDirOnlySeedSetDriNodeNocov/"
filesNC <- list.files(boxFolder)
nc <- 3
N <- 100
nsim <- S$Nsim[1]
bigN <- S$bigN[1]
dir <- c("directed")
bigNv <- rep(1:bigN , each = nsim*length(dir))
nsimv <- rep(rep(1:nsim, each = length(dir)), times = bigN)
dirv <- rep(dir, times = bigN*nsim)
corMat <- matrix(0, nrow =0 , ncol = 21)
df_nocov <- matrix(0, nrow =0, ncol = 9)

for(fn in filesNC){
  df_rds <- readRDS(paste0(boxFolder,fn))
  sIdx <- as.numeric(str_extract_all(fn, "\\d+")[[1]])[1]
  seqL <- seq(1,length(df_rds[[2]]), by = 2)
  j <- 1
  if(length(df_rds[[2]]) > 0){
    for(i in seqL){
      if(!is.null(df_rds[[2]][[i]])){
        df_nocov <- rbind(df_nocov, c(tail(df_rds[[2]][[i]]$OmegaIndex,1),sIdx, 
                                      df_rds[[2]][[i]][[20]], S$alpha[[sIdx]], 
                                      dirv[j], S$pClustOL[[sIdx]],bigNv[j],nsimv[j],
                                      length(df_rds[[2]][[i]]$Loglik[,1])))
        j <- j+1
      }
    }
  }
}
```

```{r}
df_nocov <- apply(df_nocov,2,unlist)
df_nocov <- as.data.frame(df_nocov)
colnames(df_nocov) <- c("OI_nocov","Idx","Failure","alpha","dir","OL","bigN", "Nsim","iter_nocov")
df_nocov$OI_nocov <- as.numeric(df_nocov$OI_nocov)
df_nocov$bigN <- as.numeric(df_nocov$bigN)
df_nocov$iter_nocov <- as.numeric(df_nocov$iter_nocov)
df_nocov$Nsim <- as.numeric(df_nocov$Nsim)
df_nocov$Idx <- as.numeric(df_nocov$Idx)
df_reg <- left_join(df_reg, df_nocov , by = c("Idx","alpha","dir","OL","bigN","Nsim"))
df_reg$OIDiff <- df_reg$OI - df_reg$OI_nocov
df_reg$Failure <- df_reg$Failure.x

df_reg$alpha <- as.numeric(df_reg$alpha)
df_reg$alphaLin <- as.numeric(df_reg$alphaLin)
df_reg$alphaLL <- as.numeric(df_reg$alphaLL)
df_reg$lambda <- factor(as.numeric(df_reg$lambda))
#df_reg$OL <- factor( df_reg$OL)
#df_reg$OL <- factor( df_reg$OL, levels = c("NoOL","2GrpOL1", "2GrpOL2", "2GrpOL3"))

```


## check if the network or the instance within the network makes a big difference

```{r, fig.height=9, fig.width=20, warning=FALSE}

## For each bigN check the percentage of vaues greater than 0.85
df_reg$goodOI <- df_reg$OI >= 0.85

NWprop <- df_reg %>% group_by(bigN, Nsim, OL, dist, dir) %>%
  summarise(meanOI = mean(OI),
            varOI = var(OI),
            goodOIprop = sum(goodOI))

NWprop %>% filter(dir == "directed") %>%
  ggplot()+ 
  geom_point(aes(y = meanOI, x = factor(Nsim), color = factor(bigN)))+
  facet_wrap(OL~dist)

df_reg %>% filter(dir == "directed") %>%
  ggplot()+ 
  geom_jitter(aes(y = OI, x = factor(bigN), color = factor(Nsim)),size = 0.5, alpha = 0.8,width = 0.3, height = 0)+ 
  scale_color_manual(values = c("darkblue","darkred","darkgreen","yellow4"))+
  facet_wrap(OL~dist)+
  theme(legend.position = "bottom", panel.background = element_blank())

df_reg %>% filter(dir == "directed") %>%
  ggplot()+
  geom_bar(aes(x = factor(bigN), color = factor(Nsim), fill = goodOI),linewidth = 1 ,alpha = 0.8, position = "dodge")+
  facet_wrap(OL~dist, scales = "free")+  scale_fill_manual(values= c("cornsilk3", "cornsilk4"))+ scale_color_manual(values = c("darkblue","darkred","darkgreen","yellow4"))+  # Uses ColorBrewer palette
  theme(legend.position = "bottom", axis.text.x = element_text(),  # Show x-axis text on all facets
        axis.ticks.x = element_line(),panel.background = element_blank())

## group_by the different factors and find the ones with the nightest number of goodOI
df_goodOI <- df_reg %>%
  group_by(OL,dist,bigN,Nsim, goodOI) %>%
  summarise(count = n(),prop = n()/60) %>%
  filter(goodOI == TRUE)

for(ol in unique(df_reg$OL)){
  #for(mp  in unique(df_reg$MissPct)){
  for(d in unique(df_reg$dist)){
    print(df_goodOI %>%
            filter(OL == ol,  dist == d) %>%
            ggplot(aes(x = factor(bigN), y = as.factor(as.numeric(Nsim)), fill = count))+
            geom_tile() + scale_fill_gradient(limits = c( min(df_goodOI$count), max(df_goodOI$count))) + ggtitle(paste(ol, ",",d)))
    # }
  }
}

# 
# NWprop %>% filter(dir == "undirected") %>%
#   ggplot()+ 
#   geom_point(aes(y = meanOI, x = factor(Nsim), color = factor(bigN)))+
#   facet_wrap(OL~dist)
# 
# df_reg %>% filter(dir == "undirected") %>%
#   ggplot()+ 
#   geom_jitter(aes(y = OI, x = factor(bigN), color = factor(Nsim)), alpha = 0.7,width = 0.3, height = 0)+
#   facet_wrap(OL~dist)+
#   theme(legend.position = "bottom", panel.background = element_blank())
# 
# df_reg %>% filter(dir == "undirected") %>%
#   ggplot()+
#   geom_bar(aes(x = bigN, color = factor(Nsim), fill = goodOI),linewidth = 1 ,alpha = 0.8, position = "dodge")+
#   facet_wrap(OL~dist, scales = "free")+  scale_fill_manual(values= c("cornsilk3", "cornsilk4"))+ scale_color_manual(values = c("darkblue","darkred","darkgreen"))+  # Uses ColorBrewer palette
#   theme(legend.position = "bottom", axis.text.x = element_text(),  # Show x-axis text on all facets
#         axis.ticks.x = element_line(),panel.background = element_blank())

```

## filtering for grplvl1 dirdep nsim 3 aand bigN 13

```{r}
gbg <- df_reg %>% filter(bigN == 13, Nsim == 3, dist == "DirDep", OL == "2GrpOL1")

## Look at init params for 21, 22 and 141, 142
df_rds21  <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingDirOnly21.rds"))
df_rds22  <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingDirOnly22.rds"))
12*4+3

view(cbind(df_rds21[[1]][[51]]$Forig, df_rds21[[1]][[51]]$Horig))
view(cbind(df_rds21[[1]][[52]]$Forig, df_rds21[[1]][[52]]$Horig))

view(cbind(df_rds22[[1]][[51]]$Forig, df_rds22[[1]][[51]]$Horig))
view(cbind(df_rds22[[1]][[52]]$Forig, df_rds22[[1]][[52]]$Horig))

## Common problem is one of the initial weights is 1e-05 for the ones that do not do well.... in the above
df_rds141  <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingDirOnly141.rds"))
df_rds142  <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingDirOnly142.rds"))
12*4+3

view(cbind(df_rds141[[1]][[51]]$Forig, df_rds141[[1]][[51]]$Horig))
view(cbind(df_rds141[[1]][[52]]$Forig, df_rds141[[1]][[52]]$Horig))

view(cbind(df_rds142[[1]][[51]]$Forig, df_rds142[[1]][[51]]$Horig))
view(cbind(df_rds142[[1]][[52]]$Forig, df_rds142[[1]][[52]]$Horig))


```

## level 3 overlap CaseStudy

In overlap level 3 the 3rd (3rd) and 5th(2nd , 3rd) Networks

```{r}
df_lvl3 <- df_reg %>% filter(OL == "2GrpOL3", dir == "directed")

for(l in unique(df_lvl3$lambda)){
  for(c in unique(df_lvl3$covInit)){
    print(df_lvl3 %>% filter(lambda  == l, covInit == c) %>%
            ggplot()+
            geom_bar(aes(x = bigN, color = factor(Nsim), fill = goodOI),linewidth = 1 ,alpha = 0.8, position = "dodge")+
            facet_wrap(penalty~dist, scales = "free")+  scale_fill_manual(values= c("cornsilk3", "cornsilk4"))+
            ggtitle(paste(l, " ,", c))+
            scale_color_manual(values = c("darkblue","darkred","darkgreen"))+  # Uses ColorBrewer palette
            theme(legend.position = "bottom", axis.text.x = element_text(),  # Show x-axis text on all facets
                  axis.ticks.x = element_line(),panel.background = element_blank()))
  }
}
## for different lambda values how do the data behave
df_lvl3 %>% ggplot()+
  geom_point(aes(x = log(avgMSE), y = OI, 
                 color = factor(as.numeric(Nsim)) ) , alpha =0.5)+
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~bigN)+
  #scale_color_manual(values = c("darkblue","darkred","darkgreen"))+
  theme(legend.position = "bottom", 
        axis.text.x = element_text(),
        axis.ticks.x = element_line(),
        panel.background = element_blank())

## subset of lvl3 OL NW 3
df_lvl3_3 <- df_lvl3 %>% filter(bigN == 3)
df_lvl3_3 %>% ggplot()+geom_point(aes(x = OI, y = Conductance, color = MissPct))+
  facet_wrap(~Nsim, nrow = 3)+
  theme(legend.position = "bottom", 
        axis.text.x = element_text(),
        axis.ticks.x = element_line(),
        panel.background = element_blank())

## plotting the igraph bigN and Nsim
df_lvl3_op17 <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingData41.rds"))[[1]][[17]]
df_lvl3_op15 <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingData41.rds"))[[1]][[15]]
plot(1:9103, df_lvl3_op15$Loglik[,2])
plot(1:5883, df_lvl3_op17$Loglik[,2])
G1 <- readRDS(paste0(boxFolder,"MultParamCoordPenaltyCompMissingData41.rds"))[[6]][[17]]
print(igraph::plot.igraph(G1,vertex.label = NA, vertex.size = 5,
                          vertex.color = as.factor(V(G1)$Cluster),
                          edge.arrow.size= 0.1, edge.color = "grey28"))
#view(cbind(df_lvl3_op15$Forig, df_lvl3_op17$Forig))
#view(rbind(df_lvl3_op15[[22]][1,],df_lvl3_op17[[22]][1,]))
```

## Community cohesiveness metrics

```{r, fig.height=9, fig.width=10, warning=FALSE}
#metricsMat <- as.data.frame(metricsMat)
metricsMat$index <- 1:nrow(metricsMat)

#plotting cluster coefficent for this isolated set of data
cc  <- cbind(metricsMat, OI = df_reg$OI, OL = df_reg$OL) 
cc <- cc %>% filter(cc$randOI != "undirected",dir == "directed")
cc %>% 
  ggplot()+
  geom_point(aes(y = as.numeric(CC), x = OI, color = OL),alpha =0.6)+
  theme(legend.position = "bottom", panel.background = element_blank())

undirMetrics <- metricsMat[metricsMat$randOI == "undirected",]
dirMetrics <- metricsMat[metricsMat$randOI != "undirected",]
undirMetrics <- undirMetrics[,-17]
colnames(undirMetrics) <- c("Cond","PD","Q_HP","Q_OL","CQ","OnCut","OP","PLFit",
                            "NetA","oi_b1","oi_b2","oi_cov","randOI","dir",
                            "bigN","nsim", "sIdx","index")




dirMetrics <- dirMetrics %>% select(-c(CC))
#undirMetrics <- undirMetrics[,-ncol(undirMetrics)]

#dirMetrics$index <- seq(1,nrow(metricsMat),by =2)
#undirMetrics$index <- seq(2,nrow(metricsMat),by =2)

combMet <- rbind(dirMetrics, undirMetrics)
combMet <- combMet[order(combMet$index), ]

combMet[, c(1:13,15:18)] <- lapply(combMet[, c(1:13,15:18)], as.numeric)

gbg <- cbind(df_reg, combMet[,c(1:13,17)])

for(ol in unique(gbg$OL)){
  for(d in unique(gbg$dist)){
    for(di in unique(gbg$dir)){
    p <- list()
    p[[1]] <- gbg %>% 
      filter(OL == ol, dist == d, dir == di) %>% 
      ggplot()+
      geom_point(aes(x = OI, y = Cond, color = interaction(penalty, lambda)))+
    theme(legend.position = "none", panel.background = element_blank())
    p[[2]] <-  gbg %>% 
      filter(OL == ol, dist == d, dir == di) %>% 
      ggplot()+
      geom_point(aes(x = OI, y = PD, color = interaction(penalty, lambda)))+
    theme(legend.position = "none", panel.background = element_blank())
    p[[3]] <-  gbg %>% 
      filter(OL == ol, dist == d, dir == di) %>% 
      ggplot()+
      geom_point(aes(x = OI, y = PLFit, color = interaction(penalty, lambda)))+
    theme(legend.position = "none", panel.background = element_blank())
    p[[4]] <-  gbg %>% 
      filter(OL == ol, dist == d, dir == di) %>% 
      ggplot()+
      geom_point(aes(x = OI, y = NetA, color = interaction(penalty, lambda)))+
    theme(legend.position = "none", panel.background = element_blank())
    p[[5]] <-  gbg %>% 
      filter(OL == ol, dist == d, dir == di) %>% 
      ggplot()+
      geom_point(aes(x = OI, y = randOI, color = interaction(penalty, lambda)))+
    theme(legend.position = "none", panel.background = element_blank())
    
    pt <- ggarrange(plotlist = p,nrow = 2,ncol =3,common.legend = TRUE,legend = "bottom")
    #print(pt)
    #pt <- ggpubr::ggarrange(plotlist = p,legend)
    print(annotate_figure(pt,top = text_grob(paste0("OL ", ol," dist ", d," dir ", di))))
    }
  }
}

## Assortavity of networks
# gbg %>% filter(dir == "directed") %>% ggplot()+
#   geom_point(aes(x = OI, y = NetA, color = interaction(penalty, lambda)))+
#   theme(legend.position = "bottom", panel.background = element_blank())+
#   ylim(min(gbg$NetA), max(gbg$NetA))+
#   facet_grid(vars(OL), vars(dist))
# gbg %>% filter(dir == "undirected") %>% ggplot()+
#   geom_point(aes(x = OI, y = NetA, color = interaction(penalty, lambda)))+
#   theme(legend.position = "bottom", panel.background = element_blank())+
#   ylim(min(gbg$NetA), max(gbg$NetA))+
#   facet_grid(vars(OL), vars(dist))
gbg %>% filter(dir == "directed") %>% ggplot()+
  geom_point(aes(x = OI, y = NetA, color = OL))+ylab("Assortativity")+
    ggtitle("Compare assortavity with OI directed")+
  theme(legend.position = "bottom", panel.background = element_blank())

gbg %>% filter(dir == "undirected") %>% ggplot()+
  geom_point(aes(x = OI, y = NetA, color = OL))+ylab("Assortativity")+
      ggtitle("Compare assortavity with OI undirected")+
  theme(legend.position = "bottom", panel.background = element_blank())

## Powerlaw fit
gbg %>% filter(dir == "directed") %>% ggplot()+
  geom_point(aes(x = OI, y = PLFit, color = OL))+ylab("Power law fit")+
  ggtitle("Compare Powerlaw fit with OI directed")+
  theme(legend.position = "bottom", panel.background = element_blank())

gbg %>% filter(dir == "undirected") %>% ggplot()+
  geom_point(aes(x = OI, y = PLFit, color = OL))+ylab("Power law fit")+
    ggtitle("Compare Powerlaw fit with OI undirected")+
  theme(legend.position = "bottom", panel.background = element_blank())

## Randoi Compare null model with features scrambled
gbg %>% filter(dir == "directed") %>% ggplot()+
  geom_point(aes(x = OI, y = randOI, color = OL),alpha =0.8)+ ylab("Scrambled OI")+
  theme(legend.position = "bottom", panel.background = element_blank())+
          ggtitle("Compare Full model  to scrambled features directed")+
  facet_wrap(~dist)

gbg %>% filter(dir == "undirected") %>% ggplot()+
  geom_point(aes(x = OI, y = randOI, color = OL),alpha =0.8)+ylab("Scrambled OI")+
  theme(legend.position = "bottom", panel.background = element_blank())+
            ggtitle("Compare Full model  to scrambled features undirected")+
  facet_wrap(~dist)


## feature struct. Compare covariate only to ground truth
gbg %>% filter(dir == "directed") %>% ggplot()+
  geom_boxplot(aes(x = penalty, y = oi_cov, color = OL),alpha =0.8)+ylab("cmeans Vs GT")+
  theme(legend.position = "bottom", panel.background = element_blank())+
        ggtitle("Compare cmeans to GT directed")+
  facet_wrap(~dist)

gbg %>% filter(dir == "undirected") %>% ggplot()+
  geom_boxplot(aes(x = penalty, y = oi_cov, color = OL),alpha =0.8)+ylab("cmeans Vs GT")+
  theme(legend.position = "bottom", panel.background = element_blank())+
          ggtitle("Compare cmeans to GT undirected")+
  facet_wrap(~dist)

## Compare cmeans OI to Full model OI
gbg %>% filter(dir == "directed") %>% ggplot()+
  geom_point(aes(x = OI, y = oi_cov, color = OL),alpha =0.8)+ylab("cmeans Vs GT")+xlab("Full model Vs GT")+
  theme(legend.position = "bottom", panel.background = element_blank())+
          ggtitle("Compare cmeans to full model directed")+
  facet_wrap(~dist)

gbg %>% filter(dir == "undirected") %>% ggplot()+
  geom_point(aes(x = OI, y = oi_cov, color = OL),alpha =0.8)+ylab("cmeans Vs GT")+xlab("Full model Vs GT")+
  theme(legend.position = "bottom", panel.background = element_blank())+
          ggtitle("Compare cmeans to full model undirected")+
  facet_wrap(~dist)


## feature struct.Compare nocov to Full model
gbg %>% filter(dir == "directed") %>% ggplot()+
  geom_boxplot(aes(x = penalty, y = oi_b1, color = OL),alpha =0.8)+ylab("nocov vs Full model")+
  theme(legend.position = "bottom", panel.background = element_blank())+
        ggtitle("Compare nocovariate to Full model directed")+
  facet_wrap(~dist)

gbg %>% filter(dir == "undirected") %>% ggplot()+
  geom_boxplot(aes(x = penalty, y = oi_b1, color = OL),alpha =0.8)+ylab("nocov vs Full model")+
  theme(legend.position = "bottom", panel.background = element_blank())+
      ggtitle("Compare nocovariate to Full model undirected")+
  facet_wrap(~dist)

## feature struct.Compare cov to Full model
gbg %>% filter(dir == "directed") %>% ggplot() +
  geom_boxplot(aes(x = penalty, y = oi_b2, color = OL),alpha =0.8)+ylab("cmeans vs Full model") +
  theme(legend.position = "bottom", panel.background = element_blank()) +
  ggtitle("Compare cmeans to Full model, directed") +
  facet_wrap(~dist)

gbg %>% filter(dir == "undirected") %>% ggplot() +
  geom_boxplot(aes(x = penalty, y = oi_b2, color = OL),alpha =0.8)+ylab("cmeans vs Full model") +
  theme(legend.position = "bottom", panel.background = element_blank()) +
    ggtitle("Compare cmeans to Full model undirected") +
  facet_wrap(~dist)
```


## OI comparison

```{r, fig.width=12, fig.height=6, warning=FALSE}
library(legendry)

#for(a in unique(df_reg$alpha)){
for(miss in unique(df_reg$MissPct)){
  for(ol in unique(df_reg$OL)){
    for(pen in unique(df_reg$penalty)){

             df <- df_reg %>% filter( OL == ol, penalty == pen, MissPct == miss)
      if(nrow(df) > 0){
        p <- df %>%
          ggplot() +
          geom_boxplot(aes(x = interaction(covInit,dist,sep= "/"), y = OI, color = factor(as.character(lambda)))) +
          coord_cartesian(ylim = c(0, 1)) + 
          ggtitle(paste0(ol, " ", pen, " misPct ", miss)) +
          theme(legend.position = "bottom", panel.background = element_blank())+
          facet_wrap(~dir)
        
        print(p)
      } 
    }
  }
}
#}
```

## Plottin OI difference

## Comparing difference in OI

```{r, fig.width=12, fig.height=6, warning=FALSE}

for(ol in unique(df_reg$OL)){
  for(pen in unique(df_reg$penalty)){
    #unique(df_reg$OL)
    #for(a in unique(df_reg$alpha)){
    p <- list()
    i <- 1
    for(d in unique(df_reg$dir)){
      for(w in unique(df_reg$MissPct)){
        df <- df_reg %>% filter(MissPct == w, dir == d, OL == ol, penalty == pen)
        if(nrow(df) > 0){
          p[[i]] <- df %>%
            ggplot() +
            geom_boxplot(aes(y = as.numeric(OIDiff), x =dist,color = lambda)) + 
            ylab("Diff in OI")+ xlab("dist")+ ylim(-1,1)+
            geom_hline(yintercept = 0, linetype = "dashed", color = "grey23", linewidth = 0.5)+
            #scale_x_discrete(guide = guide_axis(angle = 45)) +
            facet_wrap(~alphaLL) + 
            ggtitle(paste0(w , ", ",d, ", ", ol, " ,", pen)) +
            theme(legend.position = "none", panel.background = element_blank())
          i<- i+1
        }
      }
    }
    if(length(p) > 0){
      pt <- ggpubr::ggarrange(plotlist = p)
      print(pt)  
    }
    
  }
}

```



## OI by paramteter comparison

```{r, fig.width=12, fig.height=6}

for(ol in unique(df_reg$OL)){
  for(miss in unique(df_reg$MissPct)){
    for(dis in unique(df_reg$dist)){
      df <- df_reg %>% filter( OL == ol, MissPct == miss, dist == dis)
      if(nrow(df) > 0){
        print(df %>%
                ggplot()+
                geom_boxplot(aes(y = OI, x = interaction(factor(as.numeric(as.character(lambda))),penalty,sep = "/"),color = covInit)) +
                #geom_hline(aes(yintercept = max(median(OI))))+
                scale_x_discrete(guide = guide_axis(angle = 45))+
                ylim(0,1)+
                facet_wrap(~dir)+
                ggtitle(paste0( "Miss pct: ",miss, " NW, ", ol, " dist ",dis )) +
                theme(legend.position = "bottom", 
                      panel.background = element_blank(),
                      strip.text = element_text(size = 7),
                      strip.background = element_rect(fill = "white")))
      }
    }
  }
}

```


## plotting MSE

```{r, fig.width=14, fig.height=6}
df_reg$avgMSE <- rowMeans(df_reg[,2:4], na.rm = TRUE)

for(ol in unique(df_reg$OL)){
  for(d in unique(df_reg$dir)){
    print(df_reg %>%  
            filter( OL == ol, dir == d) %>% 
            ggplot() +
            geom_boxplot(aes(y = avgMSE, 
                             x = interaction(dist, covInit, sep = "."), 
                             color = penalty)) +
            scale_x_discrete(guide = guide_axis(angle = 90)) +
            ylim(min(df_reg$avgMSE),100)+
            ggtitle(paste0( ol, ", ", d)) +
            theme(legend.position = "bottom", 
                  panel.background = element_blank(),
                  strip.text = element_text(size = 10),
                  strip.background = element_rect(fill = "white"))+
            facet_grid(vars(lambda), vars(as.numeric(MissPct))))
  }
}

```

## Within the bigN variance 

```{r, fig.height=6,warning=FALSE}

df_var <- df_reg %>% 
  group_by(lambda, dir, dist, covInit, penalty, OL, MissPct, bigN) %>%
  summarise(OIVar = var(OI), minmaxRange = max(OI) - min(OI))
```


```{r, fig.height=6,warning=FALSE}
for(ol in unique(df_reg$OL)){
  for(d in unique(df_reg$dir)){
    for(dis in unique(df_reg$dist)){
      print( df_var %>% filter(OL == ol, dir == d, dist == dis) %>%
               ggplot() +
               geom_point(aes(y = OIVar, x = factor(as.numeric(MissPct)),
                              color = interaction(covInit,penalty, sep = ".")))+
               scale_x_discrete(guide = guide_axis(angle = 90)) +
               ylim(min(df_var$OIVar), max(df_var$OIVar))+
               ggtitle(paste(ol, ", ",d, ", ", dis))+
               theme(legend.position = "bottom", 
                     panel.background = element_blank(),
                     strip.text = element_text(size = 10),
                     strip.background = element_rect(fill = "white"))+
               facet_grid(vars(lambda), vars(as.numeric(bigN))))
      
    }
  }
}

```


```{r, fig.height=6,warning=FALSE}
for(ol in unique(df_reg$OL)){
  for(d in unique(df_reg$dir)){
    for(dis in unique(df_reg$dist)){
      print( df_var %>% filter(OL == ol, dir == d, dist == dis) %>%
               ggplot() +
               geom_point(aes(y = minmaxRange, x = factor(as.numeric(MissPct)),
                              color = interaction(covInit,penalty, sep = ".")))+
               scale_x_discrete(guide = guide_axis(angle = 90)) +
               #ylim(min(df_var$OIVar), max(df_var$OIVar))+
               ggtitle(paste(ol, ", ",d, ", ", dis))+
               theme(legend.position = "bottom", 
                     panel.background = element_blank(),
                     strip.text = element_text(size = 10),
                     strip.background = element_rect(fill = "white"))+
               facet_grid(vars(lambda), vars(as.numeric(bigN))))
      
    }
  }
}

```

```{r, fig.width=10, fig.height=6}

g <- df_reg %>% 
  group_by(alpha, lambda, dist,OL, dir, penalty, MissPct,covInit) %>% 
  dplyr::summarise(meanOI = mean(OI),
                   maxOI = max(OI),
                   minOI = min(OI),
                   sdOI = sd(OI),
                   meanmseavg = mean(avgMSE, na.rm=TRUE),
                   maxmseavg = max(avgMSE, na.rm=TRUE),
                   minmseavg = min(avgMSE, na.rm=TRUE),
                   sdmseavg = sd(avgMSE, na.rm=TRUE))
for(d in unique(g$dir)){
  for(ol in unique(g$OL)){
    #for(pen in unique(g$penalty)){
    print(g %>% filter(dir == d, OL == ol) %>% 
            ggplot(aes(x = interaction(covInit,lambda,sep = "/"), y = as.factor(as.numeric(MissPct)), fill = meanOI))+
            geom_tile() +
            scale_x_discrete(guide = guide_axis(angle = 90))+
            scale_fill_gradientn(colors = hcl.colors(20, "RdYlGn"), limits = c(0,1)) +#scale_fill_viridis_c(limits = c(0, 1) ) +  # Color scale
            labs(title = paste("meanOI ", d, " ",ol),
                 x = "dist X lambda", 
                 y = "alpha") +
            theme(legend.position = "bottom", 
                  panel.background = element_blank())+
            facet_grid(vars(penalty), vars(dist)))
    #}
  }
}




```

```{r, fig.width=15, fig.height=9}
p <- list()
cd <- 100
for(d in unique(g$dir)){
  for(ol in unique(g$OL)){
    for(pen in unique(g$penalty)){
      if(nrow(g %>% filter(dir == d, OL == ol, penalty == pen) ) > 0){
        p[[1]] <- g %>% filter(dir == d, OL == ol, penalty == pen) %>% 
          ggplot(aes(x = lambda, y = as.factor(as.numeric(MissPct)), fill = maxOI))+
          geom_tile(color = "black") +scale_x_discrete(guide = guide_axis(angle = 45))+
          scale_fill_gradientn(colors = hcl.colors(cd, "RdYlGn"), limits = c(0,1)) +
          labs(title = paste("maxOI ", d, " ",ol," ", pen),x = "dist X lambda", y = "alpha") +
          theme(legend.position = "bottom",panel.background = element_blank()) +
          facet_grid(vars(covInit), vars(dist))
        #facet_wrap(~dist)
        
        p[[2]] <- g %>% filter(dir == d, OL == ol, penalty == pen) %>% 
          ggplot(aes(x = lambda, y = as.factor(as.numeric(MissPct)), fill = minOI))+
          geom_tile(color = "black") +scale_x_discrete(guide = guide_axis(angle = 45))+
          scale_fill_gradientn(colors = hcl.colors(cd, "RdYlGn"), limits = c(0,1)) +
          labs(title = paste("minOI ", d, " ",ol," ", pen), x = "dist X lambda",y = "alpha") +
          theme(legend.position = "bottom",  panel.background = element_blank())+          
          facet_grid(vars(covInit), vars(dist))
        #facet_wrap(~dist)
        
        p[[3]] <- g %>% filter(dir == d, OL == ol, penalty == pen) %>% 
          ggplot(aes(x = lambda, y = as.factor(as.numeric(MissPct)), fill = meanOI))+
          geom_tile(color = "black") +scale_x_discrete(guide = guide_axis(angle = 45))+
          scale_fill_gradientn(colors = hcl.colors(cd, "RdYlGn"), limits = c(0,1)) +
          labs(title = paste("meanOI ", d, " ",ol," ", pen), x = "dist X lambda", y = "alpha") +
          theme(legend.position = "bottom",  panel.background = element_blank())+
          facet_grid(vars(covInit), vars(dist))
        #facet_wrap(~dist)
        
        p[[4]] <- g %>% filter(dir == d, OL == ol, penalty == pen) %>% 
          ggplot(aes(x = lambda, y = as.factor(as.numeric(MissPct)), fill = sdOI))+
          geom_tile(color = "black") +scale_x_discrete(guide = guide_axis(angle = 45))+
          scale_fill_gradientn(colors = hcl.colors(cd, "RdYlGn"), limits = c(min(g$sdOI),max(g$sdOI))) +
          labs(title = paste("sdOI ", d, " ",ol," ", pen), x = "dist X lambda", y = "alpha") +
          theme(legend.position = "bottom", panel.background = element_blank())+
          facet_grid(vars(covInit), vars(dist))
        #facet_wrap(~dist)
        pt <- ggpubr::ggarrange(plotlist = p)
        print(pt)
      }
      
    }
  }
}

```

## Plot MSE vs OI

```{r, fig.height=9, fig.width=20, warning=FALSE}
for(mp in unique(df_reg$MissPct)){
  print(df_reg %>% filter(MissPct == mp) %>%
          ggplot() +
          geom_point(aes(x = avgMSE, y = OI,color = factor(bigN))) +
          xlim(0, 100)+ ylim(0,1)+theme(legend.position = "bottom", panel.background = element_blank())+
          facet_grid(vars(dist), vars(OL,Nsim)))
}



```
## Find the best OI for the given paramter combinations parameter combination 

The number of Good OI is maximum

```{r}

## group_by the different factors and find the ones with the nightest number of goodOI
df_goodOI <- df_reg %>%
  group_by(OL, dist, lambda, MissPct, goodOI) %>%
  summarise(count = n(),prop = n()/220) %>%
  filter(goodOI == TRUE)

for(ol in unique(df_reg$OL)){
  #for(mp  in unique(df_reg$MissPct)){
  for(d in unique(df_reg$dist)){
    print(df_goodOI %>%
            filter(OL == ol,  dist == d) %>%
            ggplot(aes(x = factor(as.numeric(MissPct)), y = lambda, fill = count))+
            geom_tile() + scale_fill_gradient(limits = c( min(df_goodOI$count), max(df_goodOI$count))) + ggtitle(paste(ol, ",",d)))
    # }
  }
}

MaxgoodOI <- df_goodOI %>%
  group_by(OL, dist,MissPct) %>%
  slice_max(count, n = 1, with_ties = FALSE) %>%
  ungroup()

MingoodOI <- df_goodOI %>%
  group_by(OL, dist,MissPct) %>%
  slice_min(count, n = 1, with_ties = FALSE) %>%
  ungroup()
```


