---
title: "Untitled"
output: pdf_document
date: "2025-12-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mcp)
library(changepoint)
library(strucchange)
library(readxl)
library(RColorBrewer)
library(imputeTS)
library(fs)
library(glmnet)
#library(NGC)
library(igraph)
library(influential)
library(simts)
library(tseries)


nodeImpfunc <- function(nw){
  
  colnames <-  c("Section","Indegree","Outdegree","Betweenness",
                 "NeighConnect_in","NeighConnect_out", 
                 "H_Index_in","H_Index_out","Coll_inf_in","Coll_ing_out",
                 "ivi_in","ivi_out","ivi_all","Closeness","Eigen","City") #"Closeness","EigenCentrality",
  Node_imp <- data.frame(matrix(ncol =length(colnames), nrow = 0))
  
  
  for (i in 1:(Nbrk+1)) {
    nw[[i]] <- igraph::simplify(nw[[i]],  remove.multiple = FALSE )
    plot.igraph(igraph::simplify(nw[[i]]),directed = T,
                main = paste("subsection: ", i),
                edge.arrow.size = .2,
                vertex.label = V(nw[[i]])$names,
                vertex.size = 5,
                vertex.color = c("lightblue"),
                vertex.frame.color = "blue",
                vertex.label.size=0.001)
    
    ## gathering some ndoe importance measures from all the nodes
    Node_imp <- rbind(Node_imp, 
                      cbind(i,
                            igraph::degree(nw[[i]], mode = "in"),
                            igraph::degree(nw[[i]], mode = "out"),
                            round(igraph::betweenness(nw[[i]],normalized = TRUE ),2),
                            round(neighborhood.connectivity(nw[[i]], mode = "in"),2),
                            round(neighborhood.connectivity(nw[[i]], mode = "out"),2),
                            h_index(nw[[i]], mode= "in"),
                            h_index(nw[[i]], mode= "out"),
                            collective.influence(nw[[i]],mode = "in"),
                            collective.influence(nw[[i]],mode = "out"),
                            
                            ### Calculating the integrated value of influence from a graph
                            round(ivi(nw[[i]], directed = TRUE, mode = "in"),2),
                            round(ivi(nw[[i]], directed = TRUE, mode = "out"),2),
                            round(ivi(nw[[i]], directed = TRUE, mode = "all"),2),
                            igraph::closeness(nw[[i]], mode = "out"),
                            igraph::eigen_centrality(nw[[i]], directed = TRUE)$vector,
                            V(nw[[i]])$names
                      )
    )
    
  }
  colnames(Node_imp) <- colnames
  return(Node_imp)
}

LassoVar <- function(df_ip, d, Nbrk, retFit = FALSE){
  #edgeIx <- as.data.frame(matrix(nrow = 0, ncol = 4))
  if(retFit ==TRUE){
    grphs <- list()
    fits <- list()
  }
  for (m in 1:(Nbrk+1)) {
    print(paste0("Subsection number ,", m))
    k <- df_ip[[m]] 
    cityNames <- colnames(k)
    k <- t(k)
    if(any(is.na(k))){
      print("k has missing values")
    }
    fit1 = NGC::ngc(k, d)
    #summary(fit1)
    #edge <- which(fit1$estMat != 0, arr.ind = T)
    #edgeIx <- rbind(edgeIx, cbind(m, (edge)))
    
    if(retFit == TRUE){
      V(fit1$ring)$names <- cityNames
      grphs[[m]] <- fit1$ring
      fits[[m]] <- fit1
      
    }
    
  }
  
  ## assigning the city names back to the numbered locations
  #edgeIx <- as.data.frame(edgeIx)
  #colnames(edgeIx) <- c("group","to", "from","lag")
  #cityNames <- as.data.frame(cbind(cityNames, 1:Nval))
  #colnames(cityNames) <- c("cityNames","Id")
  #cityNames$Id <- as.integer(cityNames$Id)
  #grphdf <- left_join(edgeIx, cityNames, by = join_by( to == Id))
  #grphdf <- left_join(grphdf, cityNames, by = join_by(from == Id))
  
  #grphdf <- grphdf[,c(1,4,5,6)]
  #colnames(grphdf) <- c("group","lag","to","from")
  
  #if(retFit == TRUE){
  #  return(list(grphdf, grphs))
  #}
  return(list(grphs, fits))
}
```



## Trying out the change point detection method above ols-cusum : First 24 time series with lowest rate of missing values
```{r}
dat <- read_excel(paste0("C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Code/Combined_aggregated_OHA_normalized_2026-04-10.xlsx"),
                  sheet = "COVID",
                  guess_max = 10000)

df <- dat  %>% 
  subset(select = c(Sample_Date,LogCopiesPerL,LogCopiesPerDayPerPerson_NormtoFlowPopRec, Location, County, Site))
#df$Sample_Date <- lubridate::as_date(df$Sample_Date,format ="%m/%d/%y")
epiweek <- epiweek(df$Sample_Date)#epitools::as.week(df$Date, format  = "%m/%d/%y")
df$epiweek <- epiweek#as.numeric(epiweek$week)
#df$year <- year(as.Date(df$Date, format = "%m/%d/%y"))
df$year <- epiyear(df$Sample_Date)#year(as.Date(df$Date, format = "%m/%d/%y"))


df$epimonth <- month(df$Sample_Date)#month(as.Date(df$SDate, format = "%m/%d/%y"))
df$year <- year(df$Sample_Date)#year(as.Date(df$Date, format = "%m/%d/%y"))

df <- df %>%
  group_by(Location, year, epiweek) %>%
  dplyr::summarise(meanlogcopies =  mean(LogCopiesPerL, na.rm = TRUE),
                   Date = first(Sample_Date)) %>%
  ungroup() %>%
  group_by(year,epiweek)%>%
  dplyr::mutate(Date = first(Date)) %>%
  pivot_wider(names_from = Location, values_from = c(meanlogcopies, -Date) ) %>%
  ungroup() %>%
  arrange(year, epiweek)


df <- df[19:282,]
```

```{r}
## Find locations that have more than 50% missing values.

## Find the counties for each lcoation
df_county <- na.omit(distinct(data.frame(loc =make.names(dat$Location), county = dat$County)))

nas <- data.frame(names= colnames(df),
                  val = as.numeric(colSums(is.na(df))/dim(df)[1])*100)
summary(nas$val[4:length(nas$val)])
hist(nas$val[4:length(nas$val)], breaks = 70)

## nas by date
nas_date <- data.frame(week = 1:(dim(df)),
                       val = as.numeric(rowSums(!is.na(df[,-c(1:3)]))))
nas_date %>% ggplot()+geom_point(aes(x = week, y = val))+geom_line(aes(x = week, y = val), color = "gray40")
## removing locations that have more than 50% missing values
pctThrs <- 40
df <- df %>% subset(select = which(nas[,2] < pctThrs))
colnames(df) <- make.names(colnames(df))
## Remvoing st.Helens , Siletz and Siletz tribe ,Ontario, Ontario Prison, Redmond

df <- df %>% subset(select = -c(St..Helens,
                                Silverton,
                                #Ontario,
                                #Ontario.Prison,
                                Siletz
                                #Warm.Springs.SSL
                                #Port.Orford
))

## removing 2022 epiweek 53 
#df <- df[!(df$year %in% c( "2021","2024") & df$epiweek == "53"),]
nas$names <- make.names(nas$names)

```

## Plotting the locations to look at missing data

```{r, fig.width=8, fig.height=5}
df_tmp <-df
newColnames <- left_join(data.frame(loc = colnames(df_tmp)),nas, by = join_by(loc == names ) )
colnames(df_tmp) <- paste(newColnames$loc, round(newColnames$val, 2), sep = "_")
AvgValue <- rowMeans(df_tmp[,4:dim(df_tmp)[2]], na.rm = TRUE)
#df_tmp$Date_0 <- mdy(df_tmp$Date_0)
locNames <- colnames(df_tmp)[4:length(colnames(df_tmp))]
df_plt <- df_tmp %>%
  subset(select = -c(year_0, epiweek_0)) %>%
  pivot_longer(-c(Date_0))

#df_plt$Date_0 <-mdy(df_plt$Date_0)
df_plt$year <- year(df_plt$Date_0)
df_plt$month <- lubridate::month(df_plt$Date_0, label =TRUE)
Avg <- data.frame(AvgValue)
Avg$Date_0 <- df_tmp$Date_0
#pdf("MissingdataPlots.pdf")
for(i in seq(1,length(locNames),by =6)){
  df_c <- df_plt[df_plt$name %in% locNames[i:(i+3)],]
  print(ggplot()+
          geom_line(data = Avg, aes(x = Date_0, y = AvgValue), linetype = 2)+
          geom_line(data= df_c, aes(x = Date_0, y = value, color = name)) + 
          theme(legend.position="bottom",axis.text.x = element_text(angle = 45,  hjust=1, size=6 ))+
          ylab("log copies")+xlab("Date sampled")+ scale_x_date(date_breaks = "3 month", date_labels = "%b/%y")+
          facet_wrap(~name))
}
#dev.off()
x <- 0
for(i in 1:50){
  x <- choose(50, i)+x
}
x <- x/2

i <- 3
start <- (i-1)*10000 +1
end <- i*10000

```



```{r, fig.width=8, fig.height=6}
## Find locations that have more than 50% missing values.
Nval <- dim(df)[2]-3#27
Nbrk <- 6
nas <- data.frame(names= colnames(df),
                  val = as.numeric(colSums(is.na(df))/dim(df)[1])*100)
nas <- nas[-c(1,2,3),]
df_samp <- df[, -c(1,2,3)]
ww_samp <- df[, nas$names[sort(nas$val, index.return=TRUE)$ix[1:Nval]]]
ww_samp <- as.matrix(ww_samp)
op_bp <- list()
col <-  data.frame(loc = colnames(ww_samp))
col <- left_join(col, df_county,by = join_by(loc == loc ))

bp_nat <- data.frame(matrix(ncol = 2, nrow = 0, 0))

## Getting average value measured over the state
avgVal <- rowMeans(ww_samp, na.rm = TRUE)

ww_ip <- data.frame(matrix(ncol = ncol(ww_samp), nrow =nrow(ww_samp), 0))

for(i in 1:dim(ww_samp)[2]){
  ### OLS CUSUM changepoint det with missing data
  
  ww_ip[,i] <- na_kalman(ww_samp[,i],model = "auto.arima" )
  
 # bpIp <- data.frame(y = ww_ip[,i],
  #                   y_lag1 = stats::lag(ww_ip[,i], k=1),#c(ww_ip[-1,i], NA),
  #                   y_lag2 = stats::lag(ww_ip[,i], k=2)) %>%  #c(ww_ip[-c(1:2),i], NA,NA)) %>%
   # drop_na()
  bpIp <- data.frame(y = ww_ip[,i],
                     t = 1:length(ww_ip[,i]))
                     #y_lag1 = c(lag(ww_ip[,i])))#%>%
                     #y_lag2 = lag(ww_ip[-c(1:2),i])) %>%
    #drop_na()
  
  op_efp <- breakpoints(y ~ t,h =dim(ww_samp)[2], data = bpIp )#efp(y ~ y_lag1 + y_lag2  , data = bpIp, type = "OLS-CUSUM")
  plot(op_efp)
  
  ## Finding breakpoints without any lag considerations
  op_bp[[i]] <- breakpoints(breakpoints(y ~ t, #y_lag1 + y_lag2, 
                                        h = dim(ww_samp)[2], 
                                        data = bpIp), 
                            breaks = Nbrk)
  #print(confint(breakpoints(y ~ 1, h =dim(ww_samp)[2], data = bpIp, breaks = Nbrk)))
  ## finding breakpoints with lag consideration
  bp_nat <- rbind(bp_nat, cbind(col[i,1],col[i,2], c(1,op_bp[[i]]$breakpoints, dim(ww_samp)[1])))
  
}

## finding the changepoint in average data
# bpIpavg <- data.frame(y = avgVal,
#                      y_lag1 = c(avgVal[-1], NA),
#                      y_lag2 = c(avgVal[-c(1,2)], NA,NA)) %>%
#     drop_na()
# #   ## Finding breakpoints without any lag considerations
# op_bpavg <- breakpoints(breakpoints(y ~ y_lag1 + y_lag2, h =dim(ww_samp)[2], data = bpIpavg), breaks = Nbrk)
#bp_nat <- rbind(bp_nat, cbind("Average","value",c(1,op_bpavg$breakpoints ,dim(ww_samp)[1])))

colnames(ww_ip) <- colnames(ww_samp)
colnames(bp_nat) <- c("Location", "County","Breakpoint")
bp_nat$Breakpoint <- as.numeric(bp_nat$Breakpoint)


## Adding information about the breakpoint numbering
bp_nat$brkpt <- rep(0:(Nbrk+1), times = Nval)

#bp_nat <- bp_nat %>% group_by(brkpt) %>%
#  arrange(Breakpoint)

highest_rows <- bp_nat %>%
  filter(!(Breakpoint == 1) & !(Breakpoint ==dim(df)[1])) %>%
  group_by(brkpt) %>%
  slice_max(Breakpoint) 
# Select lowest row within each group
lowest_rows <- bp_nat %>%
    filter(!(Breakpoint == 1) & !(Breakpoint ==dim(df)[1])) %>%
  group_by(brkpt) %>%
  slice_min(Breakpoint) 
# To combine results, you can use `bind_rows`:
combined_results <- bind_rows(highest_rows, lowest_rows)

bp_nat$Location <- factor(bp_nat$Location, levels = bp_nat$Location[bp_nat$brkpt == 2])

bp_nat %>% ggplot() +
  geom_point(aes(y = interaction(Location, County), x = Breakpoint, group = Location)) +
  geom_line(aes(y = interaction(Location, County), x = Breakpoint, group = Location)) +
  geom_vline(data=highest_rows, aes(xintercept = Breakpoint), color = "darkblue", linetype = 2)+
    geom_vline(data=lowest_rows, aes(xintercept = Breakpoint), color = "darkred", linetype = 2)+
  scale_x_continuous(guide = guide_axis(angle = 45), limits = c(0,dim(ww_samp)[1])) + 
  ggtitle("Breakpoint distribution for locations") + 
  ylab("Locations") + xlab("Breakpoints") +
  theme_minimal()

bp_nat %>% ggplot() +
  geom_point(data =  bp_nat ,aes(y = interaction(Location), x = Breakpoint, group = Location))+#, color = factor(brkpt))) +
  geom_line(aes(y = interaction(Location), x = Breakpoint, group = Location), alpha =1) +
  #geom_vline(data=highest_rows, aes(xintercept = Breakpoint), color = "darkblue", linetype = 2)+
  #  geom_vline(data=lowest_rows, aes(xintercept = Breakpoint), color = "darkred", linetype = 2)+
  scale_x_continuous(guide = guide_axis(angle = 45), limits = c(0,dim(ww_samp)[1])) + 
  ggtitle("Breakpoint distribution for locations") + labs(color = "Breakpoint number") +   guides(color = guide_legend(nrow = 1))+
  ylab("Locations") + xlab("Breakpoints") + theme(legend.position = "bottom")
  theme_minimal()
#ggsave("brkpts.pdf")
```


```{r}
Tv <- dim(df)[1]
h <- dim(df)[2]-3
m <- Nbrk

## total segments
G1 <- Tv*(Tv+1)/2

## Considering the size of sgements

G2 <- (h-1)*Tv -(h-2)*(h-1)/2

## Final reduced segments to consider
G3 <- Tv*(h-1)-m*h*(h-1)-(h-1)^2-h*(h-1)/2


```


### Ploting the output from the changepoint method

```{r}
#pdf("AllBrkPts.pdf")
for (i in 1:dim(ww_samp)[2]) {
  print(ggplot() +
          geom_line(aes(x = 1:(dim(ww_ip)[1]), 
                        y = ww_ip[,i] ), color = "darkorange")+
          geom_line(aes(x = 1:(dim(ww_samp)[1]), 
                        y = ww_samp[,i])) +
          geom_vline(xintercept = op_bp[[i]]$breakpoints, 
                     color = "blue", 
                     linetype = "dashed") +
          theme_minimal() +
          ggtitle(col[i,1]))
  #ggsave(paste0("unicp",i,".jpeg"))
}
#dev.off()
```


## Combine all the breakpoints for the different time series data.

```{r}

d <- 2
bp <- data.frame(matrix(nrow = 0, ncol =4))
for(i in 1:length(op_bp)){
  tmp <- c(1,op_bp[[i]]$breakpoints,dim(ww_ip)[1])
  bp <- rbind(bp, cbind(rep(i, length(tmp)),tmp, df$Date[tmp], rep(col$loc[i], length(tmp))))
}

colnames(bp) <- c("TS","BkPtS", "Date", "Location")
bp$BkPtS <- as.numeric(bp$BkPtS)
bp <- bp %>% 
  group_by(TS) %>% 
  mutate(BkPtE = as.numeric(lead(BkPtS, 1, default = NA))) %>%
  filter(!is.na(BkPtE)) %>%
  mutate(range = paste0(BkPtS,"-",BkPtE)) %>%
  ungroup()%>%
  mutate(xRangeL =round(rep(seq(from = min(rowMeans(ww_ip, na.rm = TRUE)), 
                                  to = max(rowMeans(ww_ip, na.rm = TRUE)), 
                                length.out= length(unique(bp$TS))), 
                            each =Nbrk+1), 2) ) %>%
  mutate(xRangeH = rep(c(unique(xRangeL)[-1], 5.5) , each = Nbrk+1))%>%
  mutate(id = rep(1:(Nbrk+1), times = Nval)) %>%
  ungroup()

## find the minimum and maximum value for each changepoint window. 
#ww_samp <- cbind(ww_samp,df$Date)
ggplot()+
  geom_rect(aes(xmin = as.numeric(bp$BkPtS), xmax = as.numeric(bp$BkPtE), 
                ymin = bp$xRangeL, ymax = bp$xRangeH,
                fill = as.factor(bp$id)), alpha = 1) +
  geom_line(aes(y = rowMeans(ww_ip, na.rm = TRUE), x = as.numeric(1:dim(ww_ip)[1])))+
  geom_text(aes(x = -45, y =as.numeric(unique(bp$xRangeL)), label = col$loc), 
            size = 3, vjust = 0, hjust = 0, color = "blue4")+
  scale_fill_brewer(palette="Dark2")+
  xlab("Sample week")+ ylab("Average mean log copies.")+
  theme_minimal() + 
  theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Mean value of all cities")
#ggsave("CPperCity.pdf")

```


```{r}
## Separate out all the time windows based on their start and end change points
## Imputing data and creating equal length time windows depending on stationarity of the data.

rng <- bp %>% group_by(id) %>%
  summarise(minV = min(BkPtS),
            maxV = max(BkPtE))%>%
  mutate(minDate  = df$Date[minV],
         maxDate  = df$Date[maxV])

TSsec <- list()

for (i in 1:Nval) {
  g <- list()
  for(j in 1:(Nbrk+1)){
    bp_ss <- bp[bp$TS ==i,]
    strt <- bp_ss[bp_ss$id==j,]$BkPtS
    end <- bp_ss[bp_ss$id==j,]$BkPtE
    t = ww_ip[strt:end,i]
    rngstrt <- rng[j,]$minV   
    rngend <- rng[j,]$maxV
    ## Front padding
    fp <- strt - rngstrt
    if(fp > 0){
      t <- c(rep(NA, fp), t) 
    }
    ## End padding for the data
    ep <- rngend - end
    if(ep >0){
      t <- c(t, rep(NA,ep))
    }
    # Example 5:  Perform imputation with KalmanSmooth and user created model. This imputes the missing data
    ## eventually need to replace this with multiple imputation
    g[[j]] <- na_kalman(t) 
  }
  TSsec[i] <- list(g)
}

df_split <- list()
for(i in 1:length(TSsec[[i]])){
  df_split[[i]] <- as.matrix(sapply(TSsec,"[[",i)) 
  colnames(df_split[[i]]) <- col$loc
}
StatDat <- list()

## Data frame for saving output from dickey fuller test
adfOp <- data.frame(matrix(ncol = 1+1+2+2, nrow = 0, 0))


## check if individual sections are stationary
for(i in 1:length(df_split)){
  print(paste0("Subsection,", i))
  dd <- df_split[[i]]
  cn <- colnames(dd)
  diffedDat <- matrix(ncol = ncol(dd), nrow = nrow(dd)-1,0)
  for(j in 1:dim(dd)[2]){
    diffedDat[,j] <- diff(dd[,j], lag =1)#diff(diff(dd[,j]))#diff(dd[,j],  differences = 2)
    #acf(diffedDat[,j], lag.max = length(diffedDat[,j]), 
    #    xlab = "lag #", ylab = 'ACF',
    #   main=paste0("Subsection, ", i, " Location, ",cn[j]))
    ## Running dickey fuller test on the original data 
    origTst <- adf.test(dd[,j])
    ## Running dickey fuller on differenced data
    diffTst <- adf.test(diffedDat[,j])
    
    adfOp <- rbind(adfOp, c(i,cn[j],origTst$statistic[[1]], origTst$p.value, diffTst$statistic[[1]], diffTst$p.value ))
  }
  colnames(diffedDat) <- cn
  StatDat[[i]] <- diffedDat
}
colnames(adfOp) <- c("Subsection","Timeseries", "origStat","origPval","diffStat","diffpVal")
## If not then take difference and check pacf to see lag.
## If the above is OK, run VAR using LASSO
op <- LassoVar(df_ip = StatDat,d = d,Nbrk = Nbrk, retFit = TRUE)


```


```{r}
## Create maps using the LASSO penalty
G <- op[[1]]
nodeImp <- nodeImpfunc(G)

## find the max values for different node importance measures
maxImp <- nodeImp %>%
  group_by(Section) %>%
  summarise(maxOutdegree = max(Outdegree),
            #maxOutdegCity = City[which(Outdegree == max(Outdegree))],
            maxIndegree = max(Indegree),
           # maxIndegCity = City[which(Indegree == max(Indegree))],
            maxBetweenness = max(Betweenness),
            maxBetCity = City[which(Betweenness == max(Betweenness))]
            )

## creating network based on lat lon of the locations
grphDat <- readRDS("GraphData.rds")
g <- grphDat$WWgrph
l <- data.frame(names = make.names(V(g)$name),
                lat = as.numeric(V(g)$lat),
                lon = as.numeric(V(g)$lon))
## adding missing cities
l <- data.frame(rbind(as.matrix(l),
                      rbind(c("Rock.Creek",-122.8808,45.5554),
                            c("Dallas",-123.3170,44.9193),
                            c("Sunriver",-121.4334,43.8694))))
nameVal <- data.frame(names = make.names(V(G[[2]])$names))
layout <- left_join(nameVal, l, join_by(names == names))
## Setting labels for the nodes that have highest outdegree and indegree with different color code
```

```{r}

lvl <- 1
var <- c("Outdegree","Indegree","Closeness","Eigen")
#pdf("SegmentPlots.pdf")
for(v in var){
  gbg <- nodeImp %>% 
    group_by(Section) %>%
    subset(select = c(Section, get(v), City))%>%
    mutate(min_rank = dense_rank(as.numeric(get(v))), 
           max_rank = dense_rank(-as.numeric(get(v)))) %>%
    mutate(label1 = ifelse( max_rank <= lvl, City, "")) %>%
    mutate(label2 = ifelse( min_rank <= lvl, City, "")) %>%#min_rank <= 1 |
    mutate(color1 = case_when(max_rank <= lvl ~ "green4")) %>%
    mutate(color2 = case_when(min_rank <= lvl ~ "red"))
  
  for(i in 1:(Nbrk+1)){
    V(G[[i]])$label1 = gbg$label1[gbg$Section == i]
    V(G[[i]])$color1 = gbg$color1[gbg$Section == i]
    #jpeg(paste0(v,i,".jpg"), width = 350, height = 350)
    #  par(mar=c(0,0,0,0)+.8)
     par(mar=c(0.8,0,0.8,0))
    plot.igraph(igraph::simplify(G[[i]]),directed = T,
                main = paste(rng$minDate[i],"-", rng$maxDate[i]," Node measure",v),
                edge.arrow.size = 0.3,
                edge.width = 0.5,
                edge.color = "gray30",
                edge.alpha =0.5,
                layout = cbind(as.numeric(layout$lat),
                               as.numeric(layout$lon)),
                vertex.label = NA,
                vertex.size = 5,
                vertex.color =V(G[[i]])$color1,
                 vertex.label.dist=1,
                vertex.frame.color = NULL,
                vertex.label.size=0.001)
    
  }
}
#dev.off()
```



## fitting the changepoint method on average data and then lasso on the entire dataset using the average chnagepoints



```{r}
## finding the changepoint in average data
bpIpavg <- data.frame(y = avgVal, t =1:length(avgVal))
  #                   y_lag1 = c(avgVal[-1], NA),
  #                   y_lag2 = c(avgVal[-c(1,2)], NA,NA)) %>%
  #  drop_na()
## Finding breakpoints without any lag considerations
op_bpavg <- breakpoints(breakpoints(y ~ t, h =dim(ww_samp)[2], data = bpIpavg), breaks = Nbrk)
#bp_nat <- rbind(bp_nat, cbind("Average","value",c(1,op_bpavg$breakpoints ,dim(ww_samp)[1])))
b <- c(1,as.numeric(op_bpavg$breakpoints), length(avgVal))
avgSplt <- list()

for(i in 1:(length(b)-1)){
  avgSplt[[i]] <- apply(ww_ip[b[i]:b[i+1],], 2, diff)
}

op <- LassoVar(df_ip = avgSplt ,d = d,Nbrk = Nbrk, retFit = TRUE)

ggplot()+geom_line(aes(x = 1:length(avgVal), y = avgVal))+
  geom_vline(aes(xintercept = b), color = "darkblue", linetype = 2)+
  theme_minimal()

ww_ip %>%
  mutate(seq = 1:dim(ww_ip)[1]) %>%
  pivot_longer(-c(seq)) %>%
  ggplot() + 
  geom_line(aes(x = seq, y = value, color = name),show.legend = FALSE)+
  geom_line(data = data.frame(seq = 1:length(avgVal), avg = avgVal ), aes(x = seq, y = avg))+
  geom_vline(data = data.frame(b = b), aes(xintercept = b), color = "darkblue", linetype = 2)+
  theme_minimal()
op <- LassoVar(df_ip = avgSplt,d = d,Nbrk = Nbrk, retFit = TRUE)


```


## Creating ego networks for each node at different time chunks

plot ngc

```{r}
#' Plot DAG of network or ring graph showing Granger causality
#' param fit object of class ngc
#' param ngc.type type of plot to create
plot.ngc <- function(
    fit, #object of class ngc
    ngc.type = "dag", #"dag" or "granger"
    sparsify = FALSE #whether to remove covariates with no edges in the high-dimensional case
  ){
    if (class(fit) != "ngc")
    {
      stop("Class of argument must be ngc")
    }
    p <- fit$p
    d <- fit$d
    if (ngc.type == "dag" & p > 20)
    {
      cat("Warning: plot.ngc is not designed for plotting networks of more than 20 covariates.")
      if (sparsify)
      {
        cat("plot.ngc will remove covariates with no edges in order to plot the network.")
      }
    }
    covNames <- fit$covNames
    group <- fit$group
    if (ngc.type == "granger")
    {
      plot_ring(fit$ring, p, d)
    }
    else
    {
      plot_network(fit$dag, p, d, group, fit$fitMethod == "lasso", sparsify)
    }
    if (!is.null(covNames))
    {
      legend(d+1.5, p, paste(1:p, covNames, sep = " - "), cex = labelCex, ncol = p%/%10 + 1, title = "Legend")
    }
  }

plot_ring <- function(g, p, d)
{
  if (is.null(E(g)$weight))
  {
    edgeThickness = 0
  }
  else
  {
    edgeThickness = E(g)$weight^2/mean(E(g)$weight^2)
  }
  #control maximum and minimum thickness
  edgeThickness <- ifelse(edgeThickness > 0.2, edgeThickness, 0.2)
  edgeThickness <- ifelse(edgeThickness < 5, edgeThickness, 5)
  labelCex <- max(min(10/p, 1), 0.3)
  arrowSize <- 0.5*labelCex
  plot(simplify(g), layout = layout_in_circle(g),  vertex.label = V(g)$names,
       edge.arrow.size = arrowSize, vertex.shape = "none", edge.width = edgeThickness)
}


plot_network <- function(g, p, d, group =  NULL, signed = TRUE, sparsify = FALSE, title = NULL)
{
  edgeTails <- tail_of(g, E(g))
  edgeHeads <- head_of(g, E(g))
  if (sparsify)
  {
    nodes <- as.numeric(unique(c(edgeHeads%%p, edgeTails%%p)))
    nodes[nodes==0] <- p
    nodes <- sort(nodes)
    toRemove <- (1:p)[-nodes] + rep(seq(0, p*d, p), each = p - length(nodes))
    g <- delete_vertices(g, toRemove)
    p <- length(nodes)
    vertexLabels <- rep(nodes, d+1)
  }
  else
  {
    vertexLabels <- rep(1:p, d+1)
  }
  xcoords = rep(1:(d+1), each=p)
  ycoords = rep(p:1, d+1) 
  layout_matrix = matrix(c(xcoords, ycoords), ncol=2)
  groupList <- NULL
  if (!is.null(group))
  {
    groupList <- lapply(unique(group),function(x){which(group==x)})
  }
  par(mar=c(2.5, 2.5, 2.5, 2.5))
  if (signed)
  {
    edgeColor = ifelse(E(g)$weight > 0, "blue", "red")
  }
  else
  {
    edgeColor = NULL
  }
  if (is.null(E(g)$weight))
  {
    edgeThickness = 0
  }
  else
  {
    edgeThickness <- E(g)$weight^2/mean(E(g)$weight^2)
  }
  #control maximum and minimum thickness
  edgeThickness <- ifelse(edgeThickness > 0.2, edgeThickness, 0.2)
  edgeThickness <- ifelse(edgeThickness < 5, edgeThickness, 5)
  labelCex <- max(min(10/p, 1), 0.3)
  arrowSize <- 0.5*labelCex
  #curve edges that are more than 1 lag
  edgeCurvature <- (edgeTails <= p*(d-1))*0.25
  edgeCurvature <- edgeCurvature*(-1)^((head_of(g, E(g)) %% p) < (edgeTails %% p))
  aRatio <- ((d+3)/p)/2
  plot(g, asp = aRatio, layout = layout_matrix, main = title,
       mark.groups = groupList, mark.border = NA,
       vertex.label.cex = labelCex,
       vertex.label = vertexLabels, vertex.shape = "none",
       edge.color = edgeColor, edge.width = edgeThickness,
       edge.arrow.size = arrowSize, edge.curved = edgeCurvature,
       rescale = FALSE, xlim = c(0, d+2), ylim = c(0, p))
  text(0, -0.25*labelCex, "Lag", cex = labelCex)
  lagStep <- ifelse(d < 10, 1, 5)
  for (i in seq(lagStep, d, lagStep))
  {
    text(i, -0.25*labelCex, d-i+1, cex = labelCex)
  }
}
```

```{r, fig.width=8, fig.height=8}
for(i in 1:length(op[[2]])){
  V(op[[2]][[i]]$ring)$names <- cn
  plot.ngc(op[[2]][[i]] , "granger")
}

```



```{r}
subGrph <- list()
cmnty <- NA#data.frame(matrix(nrow=0, ncol = (Nbrk+1)))
for(i in 1:(Nbrk+1)){
  C <- igraph::simplify(G[[i]], remove.multiple = FALSE, remove.loops = TRUE)
  cmnty <- cbind(cmnty,c(cluster_edge_betweenness(C)$member))
  
  plot.igraph(C, vertex.color = cmnty[,i])
  sub <- ego(C, mode = "out")
  subGrph[[i]] = lapply(sub, function(x) induced_subgraph(C, x))
  # for(j in 1:length(subGrph[[i]])){
  #   plot.igraph(subGrph[[i]][[j]])
  # }
  
}


```



  ggtitle("Breakpoint distribution for locations") + labs(color = "Breakpoint number") +   guides(color = guide_legend(nrow = 1))+
  ylab("Locations") + xlab("Breakpoints") + theme(legend.position = "bottom")
  theme_minimal()
#ggsave("brkpts.pdf")
```
