---
title: "CP_VAR_Simulations"
output: pdf_document
date: "2024-11-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mcp)
library(changepoint)
library(strucchange)
library(readxl)
library(RColorBrewer)
library(imputeTS)
library(tseries)
library(tsDyn)
library(vars)
library(astsa)
```


## Creating a dataset of timeseries with shifted change points.

Simulation code based on: https://lindeloev.github.io/mcp/articles/packages.html

```{r}
# Simulate
set.seed(42)  # I always use 42; no fiddling
## Length of time series
nTS <-  150
## Number of time series
N <- 4
## Number of change points for each time series
nc <- 3
## Set an offset for for change point in time series. the change point idx keeps increasing for consecutive time series.
ofst <- 8
## Set offset at 20, 55, 75
StOfst <- c(20,45,30,55)

df = data.frame(
  x = 1:nTS
)
k <- 0
for (i in 1:N) {
  df[[paste0("y",i)]] = c(rnorm(StOfst[1]+k*ofst, 4),
                          rnorm(StOfst[2], 0),
                          rnorm(StOfst[3], 4),
                          rnorm(StOfst[4]-k*ofst, 0))
  k <- k+1
}
# Plot it
#plot(df)
#abline(v = c(20,65,95), col="red")
df_mat <- as.matrix(df[,-1])
df <- df %>%
  pivot_longer(!x)
df %>%
  ggplot(aes(x = x, y = value))+
  geom_point()+
  geom_vline(xintercept = c(20, 65, 95), color = "red")+
  geom_vline(xintercept = c(20+ofst, 65+ofst, 95+ofst), color = "blue", linetype = "dashed")+
  geom_vline(xintercept = c(20+ofst*2, 65+ofst*2, 95+ofst*2), color = "green", linetype = "dashed")+
  geom_vline(xintercept = c(20+ofst*3, 65+ofst*3, 95+ofst*3), color = "yellow4", linetype = "dashed")+
  theme_minimal()+
  facet_wrap(~name)

```

## Fit different models to the wastewater data. See which model works the best and use the changepoint method that works the best for that model.


## Now trying out different types of changepoint detection algorithms

### Trying the change point package using cpt.mean i.e. mean shift model
```{r}
cpt.mean(t(df_mat), method ="PELT", Q = 4)
```


### Using efp package

```{r}
op_efp <- efp(df_mat[,1] ~1, type = "OLS-CUSUM")
plot(op_efp)

bp_str <-breakpoints(df_mat[,1] ~ 1)
breakpoints(bp_str, breaks = 3)
breakpoints(bp_str, breaks = 4)
plot(bp_str)

```


```{r}
model = list(
  value ~ 1,          # intercept + slope
  1 + (1|name) ~ x
  # joined slope, varying by id
)
#ex = mcp_example("varying")
fit = mcp(model, df)
plot(fit, facet_by = "name")

```

## Creating missingness in the data and fitting the change point models used above.

```{r}
## creating a dataframe for missing data
df_miss <- df_mat

## Number of missing data in time series
n_miss <- 10

for(i in 1:N){
  ## set random locations for the missing data.
  n_miss_rand <- sample(x = 1:nTS, size = n_miss)
  
  ## Setting the indices to NA for missing data
  df_miss[n_miss_rand,i] <- NA
  
  ### OLS CUSUM changepoint det with missing data
  op_efp <- efp(df_miss[,i] ~1, type = "OLS-CUSUM")
  plot(op_efp)
  
  bp_str <-breakpoints(df_miss[,i] ~ 1)
  print(breakpoints(bp_str, breaks = 3))
  plot(bp_str)
}

```


## Change point -> VAR -> Network simulations


## Simulating VAR data

$$
y_{1t} = c1 + \pi_{11}^1y_{1,t-1} + \pi_{12}^1y_{2,t-1} +\pi_{13}^1y_{3,t-1} +\pi_{14}^1y_{4,t-1} \\

y_{2t} = c2 + \pi_{21}^1y_{1,t-1} + \pi_{22}^1y_{2,t-1} +\pi_{23}^1y_{3,t-1} +\pi_{24}^1y_{4,t-1} \\

y_{3t} = c3 + \pi_{31}^1y_{1,t-1} + \pi_{32}^1y_{2,t-1} +\pi_{33}^1y_{3,t-1} +\pi_{34}^1y_{4,t-1} \\

y_{4t} = c4 + \pi_{41}^1y_{1,t-1} + \pi_{42}^1y_{2,t-1} +\pi_{43}^1y_{3,t-1} +\pi_{44}^1y_{4,t-1} \\
$$

lag p = 1 number of time series = 4 section = 1
Starting with No initial values Same mean values of 1 for all the time series.
Dependency charts for section 1

$$
\begin{bmatrix} 
  & p_1 & p_2 & p_3 & p_4\\ 
  p_1 & 0 & 1 & 1 & 0  \\ 
  p_2 & 0 & 0 & 1 & 0  \\ 
  p_3 & 0 & 0 & 0 & 1  \\ 
  p_4 & 1 & 1 & 0 & 0\\ 
\end{bmatrix}
$$

lag p = 1 number of time series = 4 section = 2

Here we can use the previous lag values as starting values.
Change the mean value to 2 to all the ts. Dependency chart for section 2

$$

\begin{bmatrix} 
  & p_1 & p_2 & p_3 & p_4\\ 
  p_1 & 0 & 1 & 0 & 0  \\ 
  p_2 & 0 & 0 & 1 & 0  \\ 
  p_3 & 1 & 0 & 0 & 1  \\ 
  p_4 & 1 & 1 & 0 & 0 
\end{bmatrix}

$$

lag p = 1 number of time series = 4 section = 3

Here we can use the previous lag values as starting values.
Change the mean value to 4 to all the ts. Dependency chart for section 3

$$
\begin{bmatrix} 
  & p_1 & p_2 & p_3 & p_4\\ 
  p_1 & 0 & 0 & 0 & 1  \\ 
  p_2 & 1 & 0 & 1 & 0  \\ 
  p_3 & 1 & 0 & 0 & 1  \\ 
  p_4 & 0 & 1 & 0 & 0 
\end{bmatrix}
$$

```{r}
## Section 1
mu.vec1 = c(1,1,1,1)
pi1 = matrix(c(0.001, 0.5, 0.5, 0.001,
               0.001, 0.001, 0.5, 0.001,
               0.001, 0.001, 0.001, 0.8,
               0.5, 0.9, 0.001, 0.001),4,4, byrow = TRUE)
c.vec1 = as.vector((diag(4)-pi1)%*%mu.vec1)
B1<-cbind(c.vec1, pi1)
var1 <- VAR.sim(B=B1, n=200, include="const", 
                lag =1)
## Section 2
mu.vec2 = c(5,5,5,5)
pi2 = matrix(c(0.001, 0.001, 0.001, 0.001,
               0.001, 0.001, 0.7, 0.001,
               0.5, 0.001, 0.001, 0.8,
               0.5, 0.9, 0.001, 0.001),4,4, byrow = TRUE)
c.vec2 = as.vector((diag(4)-pi2)%*%mu.vec2)
B2<-cbind(c.vec2, pi2)
var2 <- VAR.sim(B = B2, n = 200, include = "const", 
                lag = 1, 
                starting = matrix(var1[200,], 1,4))
## Section 3
mu.vec3 = c(2,2,2,2)
pi3 = matrix(c(0.001, 0.001, 0.001, 0.4,
               0.6, 0.001, 0.7, 0.001,
               0.7, 0.001, 0.001, 0.8,
               0.001, 0.9, 0.001, 0.001),4,4, byrow = TRUE)
c.vec3 = as.vector((diag(4)-pi3)%*%mu.vec3)
B3<-cbind(c.vec3, pi3)
var3 <- VAR.sim(B = B3, n = 200, include="const", 
                lag = 1, 
                starting = matrix(var2[200,], 1,4))
#cov.mat = matrix(c(1,0.5,0.5,1),2,2)
var <- rbind(var1, var2, var3)
ts.plot(var, type= "l", col=c(1,2,3,4))
#ts.plot(var[,c(1,2)], type= "l", col=c(1,2))
#op <- VAR(var, p = 1, type = "const")
#summary(op)
# grangertest(y = var[,1], x = var[,2])
# grangertest(y = var[,2], x = var[,1])
# grangertest(y = var[,3], x = var[,4])
# grangertest(y = var[,4], x = var[,3])
# grangertest(y = var[,4], x = var[,2])
```

## Univariate changepoint detection

```{r}
#op_efp <- efp(var[,1] ~ 1, type = "OLS-CUSUM")
#plot(op_efp)
bp_str1 <-breakpoints(var[,1] ~ 1)
plot(bp_str1)
bp1 <- breakpoints(bp_str1, breaks = 3)

bp_str2 <-breakpoints(var[,2] ~ 1)
plot(bp_str2)
bp2 <- breakpoints(bp_str2, breaks = 3)

bp_str3 <-breakpoints(var[,3] ~ 1)
plot(bp_str3)
bp3 <- breakpoints(bp_str3, breaks = 3)

bp_str4 <-breakpoints(var[,4] ~ 1)
plot(bp_str4)
bp4 <- breakpoints(bp_str4, breaks = 3)
summary(bp1)
```


```{r}
#https://www.rdocumentation.org/packages/tsDyn/versions/11.0.4.1/topics/VAR.sim
# B1<-matrix(c(0.7, 0.2, 0.3, 0.2, 0.7, 0.3), ncol = 3)
# var1 <- VAR.sim(B=B1, n=100, include="none", lag =1)
# ts.plot(var1, type="l", col=c(1,2,3))
# 
pi1 = matrix(c(0.2,0.1,0.1,0.7),2,2)
mu.vec = c(1,5)
c.vec = as.vector((diag(2)-pi1)%*%mu.vec)
cov.mat = matrix(c(1,0.5,0.5,1),2,2)
B2<-cbind(c.vec, pi1) #rbind(c(0.2, 0.2, -0.7),
                       #      c(0.7, 0.2, 1.3))
#varcov<-matrix(c(1,0.2, 0.3, 1),2,2)
var <- VAR.sim(B=B2, n=300, include="const", lag =1)#, varcov = cov.mat)
ts.plot(var, type= "l", col=c(1,2))

op <- VAR(var, p = 1, type = "const")
summary(op)

grangertest(var[,1], var[,2])
grangertest(var[,2], var[,1])

```

```{r}
# pi1 = matrix(c(0.7,0.2,0.2,0.7),2,2)
# mu.vec = c(1,5)
# c.vec = as.vector((diag(2)-pi1)%*%mu.vec)
# cov.mat = matrix(c(1,0.5,0.5,1),2,2)
# var1.mod = list(const=c.vec,ar=pi1,Sigma=cov.mat)
# set.seed(301)
# y.var = simulate.VAR(var1.mod,n=250,
#                     y0=t(as.matrix(mu.vec)))
# dimnames(y.var) = list(NULL,c("y1","y2"))
```



