---
title: "Finding Communities and Correlations"
output: html_document
date: "2023-05-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#library(spdep)
library(igraph)
library(sf)
library(lubridate)
library(chron)
library(readxl)
library(CASCORE)
library(gridExtra)
```

## Reading the saved rds data and current covid data

```{r}

totalDat <- readRDS("GraphData.rds")

cases <- totalDat$cases

vaccine <- totalDat$vaccine

hwyGrph <- totalDat$HighwayGrph

dirEdges <- totalDat$directEdges

dirGrph <- totalDat$directGrph

WWpop <- totalDat$WWpop

WWgrph <- totalDat$WWgrph

ct_cntr <- totalDat$cityCenter

rm(totalDat)


```

## Defined functions

```{r}
source("HelperFuncs.R")


```


## Running various Community detection algorithms from the iGraph package

```{r}
## community detection methods in  igraph:
mem_edge <- cluster_edge_betweenness(WWgrph, weights = 1/(E(WWgrph)$distance),directed = FALSE)
png("edgebet.png", 600,500)
plot_graph(WWgrph, membership(mem_edge), NA)
dev.off()

mem_fg <- cluster_fast_greedy(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_fg), "Fast greedy")

mem_im <- cluster_infomap(WWgrph, e.weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_im), "Info Map")

mem_lp <- cluster_label_prop(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_lp), "Label propogation")

mem_le <- cluster_leading_eigen(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_le), "Leading Eigen")

mem_l <- cluster_leiden(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_l), "Leiden")

mem_o <- cluster_optimal(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_o), "Optimal")

mem_wt <- cluster_walktrap(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_wt), "Walktrap")
```

```{r}

## SBM method
n = length(unique(membership(mem_edge)))
thresh = 0.005
maxIter = 50
g <- WWgrph
V(g)$name <- as.character(1:length(V(g)))

# mem_sbm <- lazySBM(g, as.numeric(n), "simple", thresh, maxIter)
# plot_graph(g, mem_sbm[[1]][[1]], "SBM")
# 
# ## DCSBM
# mem_dc <- lazySBM(g, as.numeric(n), "DC", thresh, maxIter)
# plot_graph(g, mem_dc[[1]][[1]], "DCSBM")

## Regularized Spectral  clustering 
mem_spec <- RegSpectralClust(g, n, FALSE)
png("spectral.png", 600,500)
plot_graph(g, mem_spec, NA)
dev.off()

plot_graph(WWgrph, membership(mem_edge), NA)
plot_graph(g, mem_spec, NA)

```

```{r}
## importing wastewater data/ this is the data from 5/19

# covid <- read_csv("C:/Users/gauph/Box/Preliminary Results Coronavirus Sewer Surveillance/ddPCR results/Covid/R output data/5.19.23/Combined_all_sample_data_aggregated_byfilter_2023-05-19.csv")
# 
# covid <- covid[covid$SampleType == "Influent",]
# covid$Date <- as.dates(covid$Date)
# 
# covid$epiweek <- epiweek(covid$Date)
# covid$epiyear <- epiyear(covid$Date)
# covid$ym <- format(as.Date(covid$Date), "%Y-%m")
# ## subsampling OHA data only.
# covid <- covid[covid$Study == "OHA",]
# 
# covid_my <- covid %>%
#   dplyr::group_by(ym, Location) %>%
#   dplyr::summarize(meanLogCopies = mean(LogCopiesPerL, na.rm = TRUE), 
#                    county = first(na.omit(County)))
# 
# df <- covid %>%
#     ungroup() %>%
#     mutate(RV = as.numeric(paste0(epiyear,".",epiweek)))%>%
#     mutate(Wave = case_when(
#            between(RV, 2020.36,2021.09 )~"Pre-Alpha",
#            between(RV,2021.09, 2021.26 )~ "Alpha",
#            between(RV,2021.26,2021.44 )~ "Delta",
#            between(RV,2021.48, 2022.13 )~ "Omicron",
#            between(RV,2022.14, 2022.31 )~ "OmicronBA.2"
#            ))
# 
# 
# ## Aggregating based on wave
# covid_wv <- df %>%
#   dplyr::group_by(Location, Wave) %>%
#   dplyr::summarize(mlc = mean(LogCopiesPerL, na.rm = TRUE),
#                    county = first(na.omit(County))) %>%
#   filter(!is.na(Wave))
# 
# 
# ## merging data for waves into the graph object as attributes
# V(WWgrph)$prealpha <- unlist((covid_wv %>% filter(Wave == "Pre-Alpha"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Pre-Alpha"))$Location),3])
# 
# V(WWgrph)$alpha <- unlist((covid_wv %>% filter(Wave == "Alpha"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Alpha"))$Location),3])
#  
# V(WWgrph)$delta <- unlist((covid_wv %>% filter(Wave == "Delta"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Delta"))$Location),3])
# 
# V(WWgrph)$Omicron <- unlist((covid_wv %>% filter(Wave == "Omicron"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Omicron"))$Location),3])
# 
# V(WWgrph)$OmicronBA <- unlist((covid_wv %>% filter(Wave == "OmicronBA.2"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "OmicronBA.2"))$Location),3])
# 
# #V(WWgrph)$pop <- WWpop$Population[match(V(WWgrph)$name,  WWpop$Location)]
# 
# #V(WWgrph)$county <- covid_wv$county[]
# 
# 
# cov <- as.data.frame(cbind(V(WWgrph)$name,V(WWgrph)$prealpha,
#                            V(WWgrph)$alpha,V(WWgrph)$delta,
#                            V(WWgrph)$Omicron,V(WWgrph)$OmicronBA,
#                            V(WWgrph)$pop))
# 
# colnames(cov) <- c("name","prealpha","alpha","delta","Omicron","OmicronBA")#,"pop")
# ## Reguarized spectral clustering with covariates.
# ## removeing nodes that have consistent NA values
# ## I am not able to remove some fo the value because the stupid edge covariates are set to NULL.
# ## setting the edge covariates to 0 instead for now.
# E(WWgrph)$stsn <- 0
# E(WWgrph)$wchStn <- 0
# todel <-  c("Springfield", "Yachats","Toledo","Boardman","Depoe Bay","Condon")
# 
# ## Using CASCORE package.
# g <- delete_vertices(WWgrph, todel)
# V(g)$city <- V(g)$name
# V(g)$name <- as.character(1:length(V(g)))
adj_m <- as_adjacency_matrix(WWgrph, sparse = FALSE)

## Using Spectral Covariate clustering for the different waves
## Look into the alphan argument. 
# for(a in seq(5, 40, by=5)){
# 
#   mem_specCov <- CASC(adj_m, as.numeric(V(WWgrph)$delta), K = k,  itermax  = 1000, startn = 50, alphan = a)
#   plot_graph(WWgrph, mem_specCov, "Spectral with covariates")
# 
# }

op <- CASC(adj_m, as.numeric(V(WWgrph)$delta), K = n,  
           itermax  = 1000, startn = 50, alphan = 5)
png("spectralCov.png", 600,500)
plot_graph(WWgrph, op, NA)
dev.off()

# mem_specCov <- merge(as.data.frame(cbind(name = cov$name)),
#                      as.data.frame(cbind(membership = mem_specCov,
#                                          name = cov[-match(todel, cov$name),1])),
#                      by ="name", all.x = TRUE)

## Regularized Spectral  clustering 
mem_spec <- RegSpectralClust(WWgrph, n, FALSE)
png("spectral.png", 600,500)
plot_graph(WWgrph, mem_spec, NA)
dev.off()

mem_edge <- cluster_edge_betweenness(WWgrph, weights = 1/(E(WWgrph)$distance),directed = FALSE)
png("edgebet.png", 600,500)
plot_graph(WWgrph, membership(mem_edge), NA)
dev.off()


plot_graph(WWgrph, mem_spec, "Spectral")
plot_graph(WWgrph, membership(mem_edge), "Edge")
plot_graph(WWgrph, op, "SpecCov")


```




## Plotting boxplots for covid levels in each group for each of the methods above. 

```{r, fig.height=14, warning=FALSE}

## combining the output

op <- as.data.frame(cbind(Edge_betweenness = membership(mem_edge), 
                          Fast_greedy = membership(mem_fg), 
                          Info_map = membership(mem_im), 
                          Leiden = membership(mem_l), 
                          Leading_eigen = membership(mem_le), 
                          label_propogation = membership(mem_lp), 
                          Optimal = membership(mem_o), 
                          #SBM = mem_sbm[[1]][[1]], 
                          #DCSBM = mem_dc[[1]][[1]], 
                          Spectral = mem_spec, 
                          SpectralCov = op))
BOXPLOTS <- function(o, covVal, g, num, k){
  
  o$val <- covVal #<- merge(x = o, y = covVal, by = "City", all.o = TRUE)
  o  <- pivot_longer(o,!val, names_to = "Algorithm", values_to = "Membership" )
  o$Membership <- as.factor(o$Membership)
  o <- split(o, f = o$Algorithm)
  p <- list()
  aov_op <- list()
  # The palette with black:
  #cbPalette <- c( "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
  
  cbPalette <- c(rep("#0072B2", k))

  
  for(i in 1:num){ ## We have 10 algorithms 
    #print(i)
    p[[o[[i]]$Algorithm[1]]] <- ggplot(data = o[[i]] %>% filter(!is.na(Membership))) +
      geom_boxplot(aes(x = Membership, y = val, fill = Membership)) + 
      labs(title = as.character(o[[i]]$Algorithm[1])) +
      theme_minimal()+
      #(aes( y = val, group = as.factor(Membership), fill = as.factor(Membership)))+
      theme(legend.position = "none")+  scale_fill_manual(values=cbPalette)
    
    aov_op[[o[[i]]$Algorithm[1]]] <- tryCatch(o[[i]] %>% anova_test(val ~ Membership), 
                                              error=function(err) NA)#o[[i]] %>% anova_test(val ~ Membership)
  }
  #names(p) <- c()
  return(list(p, aov_op))
}

## plotting delta values
#delV <-  as.data.frame(cbind(V(WWgrph)$name, V(WWgrph)$delta))

```


```{r}

## Creating boxplots for the 38 communities
op<- as.data.frame(cbind(Edge_betweenness = membership(mem_edge),
           Spectral_Clustering  = mem_spec,
           SpectralWCovariates = op))
p  <- BOXPLOTS(op,as.numeric(V(g)$delta), g, 3, n)
aov <- p[[2]]
p <- p[[1]]

plt <- grid.arrange(p$Edge_betweenness,  p$Spectral_Clustering, p$SpectralWCovariates, ncol =1)

ggsave("boxplt.png", plt)



```


## Comparing the outputs using adjusted rand index.

```{r}
## Comparing edge betweenness and spectral w/o covariates
compare(op$Edge_betweenness, 
        op$Spectral_Clustering, 
        method = "adjusted.rand")

## Comparing edge betweenness and spectral w covariates
compare(op$Edge_betweenness, 
        op$SpectralWCovariates, 
        method = "adjusted.rand")

## comparing between spectral w and w/o covariates

compare(op$Spectral_Clustering, 
        op$SpectralWCovariates, 
        method = "adjusted.rand")


```
## Creating graph without losing the edges.


```{r}
V(g)$name <- V(g)$city
edges <- as.matrix(as_edgelist(g), ncols = 2)
for(v in todel){
  nbr <- as_ids(neighbors(WWgrph, v)) 
  nbr <- nbr[!(nbr %in% todel)]
  edges <- rbind(edges, as.matrix(expand.grid(nbr,nbr), ncol = 2))
}

nG <- simplify(graph_from_edgelist(edges, directed = FALSE))

plot(nG, vertex.label = NA)
V(nG)
```


## Running Cov assisted spectral algorithm for county level data. 


```{r}

## Combining cases for different waves.
county_cases <- read.csv("../Data/us-counties.csv")
county_cases <- county_cases[county_cases$state == "Oregon",]
county_cases$Date <- county_cases$date

county_cases$epiweek <- epiweek(county_cases$Date)
county_cases$epiyear <- epiyear(county_cases$Date)
county_cases$ym <- format(as.Date(county_cases$Date), "%Y-%m")
## subsampling OHA data only.
#county_cases <- county_cases[county_cases$Study == "OHA",]

county_cases_my <- county_cases %>%
  dplyr::group_by(ym, county) %>%
  dplyr::summarize(meanCases = mean(cases, na.rm = TRUE))

df <- county_cases %>%
    ungroup() %>%
    mutate(RV = as.numeric(paste0(epiyear,".",epiweek)))%>%
    mutate(Wave = case_when(
           between(RV, 2020.36,2021.09 )~"Pre-Alpha",
           between(RV,2021.09, 2021.26 )~ "Alpha",
           between(RV,2021.26,2021.44 )~ "Delta",
           between(RV,2021.48, 2022.13 )~ "Omicron",
           between(RV,2022.14, 2022.31 )~ "OmicronBA.2"
           ))


## Aggregating based on wave
county_cases_wv <- df %>%
  dplyr::group_by(county, Wave) %>%
  dplyr::summarize(mlc = mean(cases, na.rm = TRUE)) %>%
  filter(!is.na(Wave))


## merging data for waves into the graph object as attributes
V(WWgrph)$Cases_prealpha <- unlist((county_cases_wv %>% filter(Wave == "Pre-Alpha"))[match(V(WWgrph)$name , (county_cases_wv %>% filter(Wave == "Pre-Alpha"))$county),3])

V(WWgrph)$Cases_alpha <- unlist((county_cases_wv %>% filter(Wave == "Alpha"))[match(V(WWgrph)$name , (county_cases_wv %>% filter(Wave == "Alpha"))$county),3])
 
V(WWgrph)$Cases_delta <- unlist((county_cases_wv %>% filter(Wave == "Delta"))[match(V(WWgrph)$name , (county_cases_wv %>% filter(Wave == "Delta"))$county),3])

V(WWgrph)$Cases_Omicron <- unlist((county_cases_wv %>% filter(Wave == "Omicron"))[match(V(WWgrph)$name , (county_cases_wv %>% filter(Wave == "Omicron"))$county),3])

V(WWgrph)$cases_OmicronBA <- unlist((county_cases_wv %>% filter(Wave == "OmicronBA.2"))[match(V(WWgrph)$name , (county_cases_wv %>% filter(Wave == "OmicronBA.2"))$county),3])

#V(WWgrph)$pop <- WWpop$Population[match(V(WWgrph)$name, WWpop$county)]

covCases <- as.data.frame(cbind(V(WWgrph)$Casesname,V(WWgrph)$Casesprealpha,
                           V(WWgrph)$Casesalpha,V(WWgrph)$Casesdelta,
                           V(WWgrph)$CasesOmicron,V(WWgrph)$CasesOmicronBA))



```







## Spatial data analsysis


## Calculating Morans I at different lags (distances)
```{r}
library(geosphere)
library(spdep)
library(ape)

distMat <- distm(cbind(V(WWgrph)$lat, V(WWgrph)$lon))/1000
d <- seq(10, 500, by=10)
op <- data.frame(matrix(nrow = length(d), ncol = 5))
colnames(op) <- c("obs", "exp", "sd", "pVal","dist")
j = 1

for(i in d){
  distMat.bin <- (distMat >0 & distMat <= i)
  v <- Moran.I(V(WWgrph)$delta, distMat.bin, na.rm = TRUE)
  op[j,1] = v$observed
  op[j,2] = v$expected
  op[j,3] = v$sd
  op[j,4] = v$p.value
  op[j,5] = i
  j = j+1
  
}

ggplot(op) + 
  geom_point(aes(x = dist, y = obs, color = pVal<0.05))

```
## finding local morans I for each location

```{r}

grphnb <- nb2listw(knn2nb(knearneigh(ct_cntr, k = 5)))

op <- as.data.frame(localmoran(V(WWgrph)$delta , 
                               grphnb, 
                               na.action = na.exclude, 
                               zero.policy = TRUE))

ggplot()+
  geom_sf(data = fin, aes(geometry = geometry), color = "black", alpha =0.3)+
  geom_sf(data = ct_sbst, aes(geometry = shape, fill = as.numeric(op$Ii), color = as.numeric(op$Ii)))



```



## Looking at the nationwide wastewater surveilance data.

```{r}
cdc <- read.csv("../Data/NWSS_Public_SARS-CoV-2_Wastewater_Metric_Data.csv")

cdc <- cdc %>% 
  select(wwtp_jurisdiction, county_names, county_fips) %>%
  distinct() %>%
  separate_rows(county_fips, sep = ",")


cnty_fips <- as.data.frame(cbind(unique(cdc$county_fips), 1))

colnames(cnty_fips) <- c("fips", "values")
library(usmap)

plot_usmap(data = cnty_fips)

centroids <- tigris::counties(resolution = "20m") %>%
  st_centroid

centroids <- centroids[centroids$GEOID %in% cnty_fips$fips,] 

centroids <- as.data.frame(cbind(lat = as.numeric(centroids$INTPTLAT), lon = as.numeric(centroids$INTPTLON)))

trndsfrmed <- usmap_transform(centroids)

plot_usmap("states") +
  geom_point(data = trndsfrmed[-222,],
             aes(x=x,y=y),
             color= "darkblue",
             size = 1)

ggsave("CDCmap.png")
```

