---
title: "Data Exploration"
author: "Gauri Phatak"
date: "2023-04-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) 
library(readxl)
library(ggplot2) 
library(reshape2) 
library(grid) 
library(chron) 
library(stringr) 
library(plyr) 
library(dplyr) 
library(schoolmath) 
library(boxr) 
library(openxlsx) 
library(lubridate)
library(logr)
library(utils)
library(zoo)
library(janitor)
library(sf)
library(foreach)
library(igraph)
library(geosphere)
library(CASCORE)
```
# Exploring Different datasets used for this project:

We will mainly look at county level or city level data depending on the grnularity of the avaiable datasets.

## Wastewater data:

## Traffic Data

Reading traffic data:

```{r}
trf20 <- read_excel("../Data/TVT_2020.xlsx", sheet = "2020")
trf21 <- read_excel("../Data/TVT_2021.xlsx", sheet = "2021")

```

Reading the TCDS data : Permanent Automatic Traffic Recorder Volume.

combining the volume data for volume per week for year 2020, 2021 and 2022.

```{r, warning=FALSE}
## Listing all the files in the data folder
allFiles <- list.files("../Data/TCDS/")

df <- data.frame(matrix(ncol = 31, nrow = 0))
colnames(df) <- c("location","start_date","end_date","interval",
                  "h01","h02","h03","h04","h05","h06","h07","h08",
                  "h09","h10","h11","h12","h13","h14","h15","h16",
                  "h17","h18","h19","h20","h21","h22","h23","h24",
                  "type","total")

for(f in allFiles){
  if(grepl("VolumeCount", f)){
   # print(f)
    trf <- read_excel(paste0("../Data/TCDS/", f), skip = 6) %>%
      clean_names()
   # print(colnames(trf))
    trf$start_date <- as.Date(trf$start_date, origin = "1899-12-30")
    trf$end_date <- as.Date(trf$end_date , origin = "1899-12-30")
    trf$location <- na.locf(trf$location)
    trf$WY <-  format(trf$start_date, "%W/%Y")
    
    df <- rbind(df, trf)
  }
}

df <- df %>%
  group_by(location, WY) %>%
  dplyr::summarise(across(where(is.numeric), sum))

```

```{r}

trfLoc <- readxl::read_xlsx("../Data/TCDS/tcds_list.xlsx",sheet = "tcds_list",  skip = 13)

trfShp <- trfLoc %>% 
  dplyr::select(Longitude,Latitude) %>%
  st_as_sf(coords = c('Longitude', 'Latitude'), 
           na.fail = FALSE) %>%
  st_set_crs(4326) %>%
  st_transform(crs= 32736)

```

```{r}

##Loading city data
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/OSDLDataExtract/data.gdb"
#rgdal::ogrListLayers(hwpath)
ct <- st_read(hwpath, layer = "City_Limits__2016_")


## Loading highway data
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/HighwayDat/data.gdb"
hwd <- st_read(hwpath, layer="Highway_Network__2015_")
hwd <- st_zm(hwd)
id <- unique(hwd$st_hwy_idx)
fin <- c(1,1)
for (i in id) {
  val <- hwd[hwd$st_hwy_idx == i,]
  val <- st_cast(st_union(st_combine(val), by_feature = FALSE), "MULTILINESTRING")
  fin <- rbind(fin, cbind(i,val))
}


fin <- as.data.frame(fin[-1,])
colnames(fin) <- c("hwy_id","geometry")
fin <- st_as_sf(fin)
st_crs(fin) <- st_crs(ct)

##Loading city data
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/OSDLDataExtract/data.gdb"
#rgdal::ogrListLayers(hwpath)
ct <- st_read(hwpath, layer = "City_Limits__2016_")

```


```{r}

trfShp <- st_transform(trfShp, st_crs(hwd))
trfShp$LocID <-  trfLoc$`Loc ID`
#st_crs(trfShp) <- st_crs(hwd)

# ggplot() +
#   geom_sf(data = fin, aes(geometry = geometry), color = "black")+
#       geom_sf(data = ct, aes(geometry = shape), color = "green")+
#   geom_sf(data = trfShp, aes(geometry = geometry), color = "red")


```

Which sections of the highway do the ATR intersect.

Map the highway traffic volume by Health regions, county etc. compare that with the waste water data for that region over time.

```{r}

#intr <- st_intersects(st_buffer(trfShp, 500), fin)
intr <- st_nearest_feature(trfShp, fin)
intrPts <- foreach(i = intr, .combine='rbind') %do% {if(!is.na(i)){fin[i,]}}
trfShp <- trfShp[-223,]
#Find the nearest points on the highways where the traffic monitors can be placed.# 
intrPts <- st_nearest_points(trfShp, intrPts, pairwise = TRUE) %>% 
  st_cast("POINT")

intrPts <-  intrPts[seq(2, length(intrPts), 2)] %>%
  st_as_sf()

```

```{r}

ggplot() +
  geom_sf(data = fin, aes(geometry = geometry), color = "darkgray")+
      geom_sf(data = ct, aes(geometry = shape), color = "darkred")
  #geom_sf(data = intrPts, aes(geometry = x), color = "red")



```

Remove the cities that have AT in approach.

```{r, warning=FALSE}

## remove the AT from Approach
##trfLoc_sbst <- trfLoc[!(trfLoc$Approach == "AT"),]

## Remove the points that intersect with cities
##trfCts <- trfShp[-unlist(st_intersects(ct, trfShp)),]


#gbg <- hwd[hwd$st_hwy_idx == "001",]
#int <- st_difference(gbg,st_union(st_geometry(st_intersection(ct, gbg))))

#int <- st_union(int, by_feature = TRUE)

# sortedV <- int %>% 
#      group_by(city_name) %>%
#      dplyr::summarise(m = median(beg_mp_no)) %>%
#      arrange(m)
## Get coordinates for the centroid of the cities.

city_cntr <- ct %>% 
  st_as_sf() %>% 
  st_centroid() %>% 
  st_cast("POINT") %>% 
  st_transform(4326) %>% 
  st_coordinates()

distMat <- distm(city_cntr)
colnames(distMat) <- ct$city_name
rownames(distMat) <- ct$city_name

edges <- data.frame(matrix(ncol = 6, nrow=0))
colnames(edges) <- c("from","to","hwy_id", "NumStations", "Stations","dist")


for(hwy_id in id) {
  sbst <- hwd[hwd$st_hwy_idx == hwy_id,]
  if(length(st_union(st_geometry(st_intersection(ct, sbst)))) != 0 ) {
  #print(paste0("1",hwy_id))
  
  int1 <- st_intersection(sbst, ct)
  sortedV <- int1 %>% 
    group_by(city_name) %>%
    dplyr::summarise(m = median(beg_mp_no)) %>%
    arrange(m)
  #  print(paste0("2",hwy_id))
  ## in this we are getting rid of all the stations that are contained isnide the city. What happens if we remove those 
  int <- st_difference(sbst,st_union(st_geometry(st_intersection(ct, sbst))))
  int <- st_union(int, by_feature = TRUE)
  nearestHwy <- st_is_within_distance(trfShp, int, 60)#st_intersects(st_buffer(trfShp, 40), int)
  
  ### Code for when we dont remove the stations that are inside the city.
  #sbst <- st_union(sbst, by_feature = TRUE)
  #nearestHwy <- st_is_within_distance(trfShp, sbst, 60)
  
  sbstOverlap <- as.data.frame(nearestHwy)
  
  if(nrow(sbstOverlap) == 0){
    
    sortedV$city_nameConn <- c(sortedV$city_name[-1], 0)
    sortedCT <- as.matrix(cbind(sortedV$city_name, sortedV$city_nameConn), ncol =2 )#[1: length(sortedV$city_name)-1,]
    #print(hwy_id)
    #print(sortedCT)
    dist <- c()
  for (j in 1:(dim(sortedV)[1])) {
    #print(paste0(sortedCT[j,1], sortedCT[j,2], " size", j))
    if(sortedCT[j,2] != 0){
            dist <- c(dist, distMat[sortedCT[j,1], sortedCT[j,2]] )
    }
  }
    dist <- c(dist, 0)
    #sortedV <- sortedV[-length(sortedV$city_name), ]
    
    tmpdf <- as.data.frame(cbind(sortedV$city_name,
                         sortedV$city_nameConn,
                         rep(hwy_id,length(sortedV$city_name)),
                         0,0,dist))[1:length(sortedV$city_name)-1,]
    colnames(tmpdf) <- c("from","to","hwy_id", "NumStations", "Stations", "dist")
    
    edges <- rbind(edges,tmpdf)
    #print(length(edges$from))
    next
  }
  
  ## Area where the hwy data intersects with the buffered station data
  
  ## Below is when we remove the stations inside cities
  hwyInt <- int[sbstOverlap$col.id, ]
  
  ## For when we include stations inside the citites we use the code below.
  #hwyInt <- sbst[sbstOverlap$col.id, ]
  
  hwyInt <- cbind(sbstOverlap$row.id, hwyInt$beg_mp_no,  "Station" )
  sortedV <- cbind(sortedV$city_name, sortedV$m, "City")
  
  tot <- as.data.frame(rbind(sortedV, hwyInt))
  tot$V2 <- as.numeric(tot$V2)
  tot <- tot[order(tot$V2),]
   # print(paste0("4",hwy_id))

  
  stations <- list()
  to <- "NULLCITY"
  #  print(paste0("5",hwy_id))

  for (i in 1:length(tot$V1)) {
    if(tot[i, 3] == "City"){
      from <- to 
      to <- tot[i,1]
      #print(list(from, to,hwy_id,length(unique(unlist(stations))),list(unique(unlist(stations)))))
      #sortedCT <- as.matrix(cbind(sortedV$city_name, sortedV$city_nameConn), ncol =2 )#[1: length(sortedV$city_name)-1,]
    #print(hwy_id)
    #print(sortedCT)
      dist = 0 
      if(from  != "NULLCITY"){
              dist <- distMat[to, from]
      }
      
      edges[nrow(edges)+1, ] <- list(from, to, 
                                     hwy_id,
                                     length(unique(unlist(stations))),
                                     list(unique(unlist(stations))),
                                     dist)
      numStations <- 0
      stations <- list()
    } else{
      stations <- append(stations, tot[i,1])
    }
  }
  #print(paste0("completed hwy id", hwy_id))
  }
  #sortedV$city_nameConn <- c(sortedV$city_name[-1], 0)
  
  #edges <- rbind(edges,cbind(sortedV$city_name, sortedV$city_nameConn, #rep(hwy_id,length(sortedV$city_name)))[1:length(sortedV$city_name)-1,])
}

edges <- edges[edges$from != "NULLCITY",]

## Maping the detected stations

det <- trfShp[c(unique(unlist(edges$Stations))),]
det <- det[!is.na(det$LocID), ]

## find the nearest feature between the non-overlapping part and the stations.
#nearestHwy <- st_is_within_distance(trfShp, int, 50)#st_intersects(st_buffer(trfShp, 40), int)
#sbstOverlap <- as.data.frame(nearestHwy)

ggplot() +
  geom_sf(data = hwd, aes(geometry = shape), color = "black")+
  geom_sf(data = ct, aes(geometry = shape), color = "blue")+
#    geom_sf(data = gbg, aes(geometry = shape), color = "blue") +
#  geom_sf(data = int, aes(geometry = shape), color = "red") +
  #geom_sf(data = trfShp, aes(geometry = geometry), color = "purple")+
  #geom_sf(data = det, aes(geometry= geometry), color = "green")+
  theme_minimal()


```

## Creating a histogram of howmany cities have stations between them.

```{r, fig.width=7, fig.height=7}

## Get coordinates for the centroid of the cities.
#city_cntr <- st_coordinates(st_centroid(ct))

hwy_grph <- graph_from_data_frame(d = edges,vertices = ct$city_name, directed = FALSE)
edges$NumStations <- as.numeric(edges$NumStations)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, 
            vertex.size = 1, 
            vertex.color = "black",
            #edge.color = edges$NumStations+1, 
            edge.width = 2, 
            layout = city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, 
            vertex.size = 1, 
            vertex.color = "black",
            edge.color = edges$NumStations, 
            edge.width = 2, 
            layout = city_cntr)

hist(edges$NumStations, xlab = "Number of stations between cities.")
table(edges$NumStations)
```

## Reducing the cities to just wastewater cities

```{r, fig.width=7, fig.height=7, warning=FALSE}
WD <- "C:\\Users\\gauph\\Box\\Preliminary Results Coronavirus Sewer Surveillance\\Data files\\covid data files\\TestingSandbox\\RScripts"
dat <- readRDS(paste(WD, "\\..\\COVID_Data_ROutput\\ProcessedCOVIDDataInfo.rds", sep= ""))
df <- do.call(rbind.data.frame, sapply(dat, '[', 3))
df$Date <- as.Date(as.integer(df$Date), origin = "1970-01-01")
## cities present in ct and wastewater data
ct_sbst <- ct$city_name[ct$city_name %in% unique(df$Location)]

df_sbst <- df[df$Location %in% ct_sbst, ]

## keeping all the edges from above. Checking if this would add more edges to the data
saveDirEdges <-  data.frame(matrix(ncol = 2, nrow = 0))
colnames(saveDirEdges) <- c("to","from")

dirEdges <-  data.frame(matrix(ncol = 5, nrow = 0))
colnames(dirEdges) <- c("to","from","stsn","wchStn", "distance")


for (i in 1:length(ct_sbst)) {
  
  trav <- list()
  path <- shortest_paths(hwy_grph, ct_sbst[i], 
                         ct_sbst, output = "both" , 
                         weights = round(as.numeric(E(hwy_grph)$dist)))
  
  for(j in 1:length(ct_sbst)){
    curPath <- names(unlist(path$vpath[[j]]))
    totStations <- c(E(subgraph.edges(hwy_grph, as.integer(path$epath[[j]])))$NumStations,0)
    wchStations <- c(E(subgraph.edges(hwy_grph, as.integer(path$epath[[j]])))$Stations,0)
    dist <- c(E(subgraph.edges(hwy_grph, as.integer(path$epath[[j]])))$dist,0)
    subPath <- curPath[curPath %in% ct_sbst]
    
    l = 1
    if(length(curPath) > 1){
    for(k in 1:(length(subPath)-1)){
      start = subPath[k]
      end = subPath[k+1]
      numStn = 0
      wchStn <- list()
      subdist <- 0
      while(curPath[l] != end){
        numStn <- numStn + as.numeric(totStations[l])
        wchStn <- c(wchStn, wchStations[l])
        subdist <- subdist+as.numeric(dist[l])
         l = l+1
        # print(l)
      }
      dirEdges <- rbind(dirEdges, cbind(start, end, numStn, list(unlist(wchStn)), round(subdist, 2)))
    }
    }
    
    #if(length(subPath) > 1){
    #  saveDirEdges <- rbind(saveDirEdges, cbind(subPath[1:length(subPath)-1], subPath[2:length(subPath)]))
    #}
  }
}

colnames(dirEdges) <- c("to","from","stsn","wchStn", "distance")
dirEdges$distance <- as.numeric(dirEdges$distance)

```

```{r}
## Creating edges from the paths that we generate using shortest path algorithm. 
## Coloring based on the weight of the edge i.e. the number of nodes between the two nodes of interest.
hist(as.numeric(dirEdges$stsn))
DirectGrph <- graph_from_data_frame(d = dirEdges, vertices = ct$city_name, directed = FALSE)
incl <- V(DirectGrph)$name %in% ct_sbst
V(DirectGrph)$included <- ifelse(incl == TRUE, "#009E73", "#E69F00")
DirectGrph <- igraph::simplify(DirectGrph,
                       remove.multiple = TRUE,
                       remove.loops = TRUE, 
                       edge.attr.comb = list(distance = "min")
                       )

V(DirectGrph)$lat <- city_cntr[,1]
V(DirectGrph)$lon <- city_cntr[,2]

png("DirectPlot.png", 600,500)
plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1.5,
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = "#999999",
            edge.width = 1, layout = cbind(V(DirectGrph)$lat, V(DirectGrph)$lon))
dev.off()

plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1.5,
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = edges$NumStations,
            edge.width = 1, layout = city_cntr)


ggplot() +
  geom_sf(data = hwd, aes(geometry = shape), color = "#999999")+
  geom_sf(data = ct, aes(geometry = shape), fill = "#E69F00", color = "#E69F00")+
#    geom_sf(data = gbg, aes(geometry = shape), color = "blue") +
  geom_sf(data = ct[V(DirectGrph)$name %in% ct_sbst,], aes(geometry = shape), fill = "#009E73", color = "#009E73") +
  #geom_sf(data = trfShp, aes(geometry = geometry), color = "purple")+
  #geom_sf(data = det, aes(geometry= geometry), color = "green")+
  theme_minimal()

ggsave("citiesplot.png")

png("Highwayplot.png", 600,500)
plot.igraph(hwy_grph, vertex.label = NA, 
            vertex.size = 1.5, 
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = "#999999", 
            edge.width = 1, 
            layout = city_cntr)
dev.off()

```

## Looking at the non-permanent data

```{r}
getwd()
trfLocNP <- readxl::read_xlsx("../Data/TCDS/tcds_list_Nonperm.xlsx",sheet = "tcds_list_Nonperm",  skip = 13)

length(unique(trfLoc$`Loc ID`))

trfShpNP <- trfLocNP %>% 
  dplyr::select(Longitude,Latitude) %>%
  st_as_sf(coords = c('Longitude', 'Latitude'), 
           na.fail = FALSE) %>%
  st_set_crs(4326) %>%
  st_transform(crs= 32736)

trfShpNP <- st_transform(trfShpNP, st_crs(hwd))
trfShpNP$LocID <-  trfLocNP$`Loc ID`

#intrNP<- st_intersects(st_buffer(trfShpNP, 100), fin)
intrNP <- st_nearest_feature(trfShpNP, fin)
intrPtsNP <- foreach(i = intrNP, .combine='rbind') %do% {if(!is.na(i)){fin[i,]}}

#Find the nearest points on the highways where the traffic monitors can be placed.# 
intrPtsNP <- st_nearest_points(trfShpNP, intrPtsNP, pairwise = TRUE) %>% 
  st_cast("POINT")

intrPtsNP <-  intrPtsNP[seq(2, length(intrPtsNP), 2)] %>%
  st_as_sf()

ggplot() +
  geom_sf(data = fin, aes(geometry = geometry), color = "black")+
      geom_sf(data = ct, aes(geometry = shape), color = "green")+
  geom_sf(data = intrPts, aes(geometry = x), color = "red")

ggplot() +
  geom_sf(data = hwd, aes(geometry = shape), color = "black")+
  geom_sf(data = ct, aes(geometry = shape), color = "blue")+
#    geom_sf(data = gbg, aes(geometry = shape), color = "blue") +
#  geom_sf(data = int, aes(geometry = shape), color = "red") +
  geom_sf(data = trfShpNP, aes(geometry = geometry), color = "purple")


```

## Highway Spatial network data

*Need to bring the spatial networks code into this RMD*

##Public health data:

### Cases

```{r}
cases <- read.csv("../Data/United_States_COVID-19_Community_Levels_by_County.csv")
cases <- cases[cases$state == "Oregon",]

county_cases <- read.csv("../Data/us-counties.csv")
county_cases <- county_cases[county_cases$state == "Oregon",]
vaccine <- read.csv("../Data/COVID-19_Vaccinations_in_the_United_States_County.csv")

#cityDemo <- read_excel("../Data/City_data_2020")


```

### Deaths

### Vaccines

## Public Policy data

## Demographic data

## Using the direct graph data and performing community detection 

```{r, warning=FALSE}


WWgrph <- igraph::delete.vertices(DirectGrph, degree(DirectGrph) == 0)
plot(WWgrph,layout = cbind(V(WWgrph)$lat, V(WWgrph)$lon), vertex.size = 8, vertex.label = NA, main = "Original graph")

## community detection methods in  igraph:
mem_edge <- cluster_edge_betweenness(WWgrph, weights = 1/(E(WWgrph)$distance),directed = FALSE)
plot_graph(WWgrph, membership(mem_edge), "Edge betweeness")

mem_fg <- cluster_fast_greedy(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_fg), "Fast greedy")

mem_im <- cluster_infomap(WWgrph, e.weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_im), "Info Map")

mem_lp <- cluster_label_prop(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_lp), "Label propogation")

mem_le <- cluster_leading_eigen(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_le), "Leading Eigen")

mem_l <- cluster_leiden(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_l), "Leiden")

mem_o <- cluster_optimal(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_o), "Optimal")

mem_wt <- cluster_walktrap(WWgrph, weights =  1/(E(WWgrph)$distance))
plot_graph(WWgrph, membership(mem_wt), "Walktrap")

## SBM method
n = 7
thresh = 0.005
maxIter = 50
g <- WWgrph
V(g)$name <- as.character(1:length(V(g)))

op <- lazySBM(g, as.numeric(n), "simple", thresh, maxIter)
plot_graph(g, op[[1]][[1]], "SBM")

## DCSBM
op <- lazySBM(g, as.numeric(n), "DC", thresh, maxIter)
plot_graph(g, op[[1]][[1]], "DCSBM")

## Regularized Spectral  clustering 
op <- RegSpectralClust(g, n)
plot_graph(g, op, "Spectral")

## importing wastewater data/

covid <- read_csv("C:/Users/gauph/Box/Preliminary Results Coronavirus Sewer Surveillance/ddPCR results/Covid/R output data/5.19.23/Combined_all_sample_data_aggregated_byfilter_2023-05-19.csv")

covid <- covid[covid$SampleType == "Influent",]
covid$Date <- as.dates(covid$Date)

covid$epiweek <- epiweek(covid$Date)
covid$epiyear <- epiyear(covid$Date)
covid$ym <- format(as.Date(covid$Date), "%Y-%m")
## subsampling OHA data only.
covid <- covid[covid$Study == "OHA",]

covid_my <- covid %>%
  dplyr::group_by(ym, Location) %>%
  dplyr::summarize(meanLogCopies = mean(LogCopiesPerL, na.rm = TRUE))

#### Read in the population estimates for the different cities. 
boxPath <- "C:/Users/gauph/Box/"
wwtp_pop <- read_excel(paste0(boxPath,"Coronavirus Sewer Surveillance/Samples/WWTP_population.xlsx"), sheet = "wwtp_population", col_names = T)
colnames(wwtp_pop)[which(names(wwtp_pop) == "City")] <- "Location"


```



```{r}

df <- covid %>%
    ungroup() %>%
    mutate(RV = as.numeric(paste0(epiyear,".",epiweek)))%>%
    mutate(Wave = case_when(
           between(RV, 2020.36,2021.09 )~"Pre-Alpha",
           between(RV,2021.09, 2021.26 )~ "Alpha",
           between(RV,2021.26,2021.44 )~ "Delta",
           between(RV,2021.48, 2022.13 )~ "Omicron",
           between(RV,2022.14, 2022.31 )~ "OmicronBA.2"
           ))


## Aggregating based on wave
covid_wv <- df %>%
  dplyr::group_by(Location, Wave) %>%
  dplyr::summarize(mlc = mean(LogCopiesPerL, na.rm = TRUE)) %>%
  filter(!is.na(Wave))


## merging data for waves into the graph object as attributes
V(WWgrph)$prealpha <- unlist((covid_wv %>% filter(Wave == "Pre-Alpha"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Pre-Alpha"))$Location),3])

V(WWgrph)$alpha <- unlist((covid_wv %>% filter(Wave == "Alpha"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Alpha"))$Location),3])
 
V(WWgrph)$delta <- unlist((covid_wv %>% filter(Wave == "Delta"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Delta"))$Location),3])

V(WWgrph)$Omicron <- unlist((covid_wv %>% filter(Wave == "Omicron"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "Omicron"))$Location),3])

V(WWgrph)$OmicronBA <- unlist((covid_wv %>% filter(Wave == "OmicronBA.2"))[match(V(WWgrph)$name , (covid_wv %>% filter(Wave == "OmicronBA.2"))$Location),3])

cov <- as.data.frame(cbind(V(WWgrph)$name,V(WWgrph)$prealpha, V(WWgrph)$alpha,V(WWgrph)$delta,V(WWgrph)$Omicron, V(WWgrph)$OmicronBA))

## Reguarized spectral clustering with covariates.

## removeing nodes that have consistent NA values
## I am not able to remove some fo the value because the stupid edge covariates are set to NULL.
## setting the edge covariates to 0 instead for now.
E(WWgrph)$stsn <- 0
E(WWgrph)$wchStn <- 0
todel <-  c("Springfield", "Yachats","Toledo","Boardman","Depoe Bay","Condon")

## Using CASCORE package.
adj_m <- as_adjacency_matrix(delete_vertices(WWgrph, todel),
                             sparse = FALSE)

## Using Spectral Covariate clustering for the different waves
## Look into the alphan argument. 
op <- CASC(adj_m, as.numeric(cov[-match(todel, cov$V1),4]),K = 5, alphan = 5)

plot_graph(delete_vertices(WWgrph, todel), op, "Spectral with covariates")

```

## Saving the processed data as RDS

```{r}

saveRDS(list(cases = cases, vaccine = vaccine, HighwayGrph = hwy_grph, directEdges  = dirEdges, directGrph = DirectGrph, WWpop = wwtp_pop, WWgrph = WWgrph, cityCenter = city_cntr), "GraphData.rds")


```



