---
title: "MapNetworkCode"
author: "Gauri Phatak"
date: "2023-01-22"
output: pdf_document
---

```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=8, warning=FALSE)
library(tidyverse)
library(dplyr)
library(sf)
library(mapview)
library(sp)
library(usmap)
require(rgdal)
require(ggplot2)
library(raster)
library(igraph)
library(GGally)
library(ggnet)
#library(network)
#library(sna)
#library(ggplot2)
library(geosphere)
library(lubridate)
library(gganimate)
library(gifski)
library(png)
```

## Downloading the relevant data for city network and highway network.

```{r, warning=FALSE}
##Loading city data 20
citylim = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/OSDLDataExtract/data.gdb"
#rgdal::ogrListLayers(citylim)
ct <- st_read(citylim, layer = "City_Limits__2016_")
ct <- st_transform(ct, 2994)

## Adding sunriver shapefile
sunriver <- st_read("C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Data/SunriverShapefile/Sunriver.shp")
sunriver<-  st_transform(sunriver, crs = 2994)
sunriver <- rename(sunriver, city_name = id)
sunriver$city_name[1] <- "Sunriver"
sunriver <- rename(sunriver, shape = geometry)
sunriver <- st_cast(sunriver, "MULTIPOLYGON")

## adding rock creek shapefile
Rockcreek <- st_read("C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Data/RockcreekShapefile/Rockcreek.shp")
Rockcreek <-  st_transform(Rockcreek, crs = 2994)
Rockcreek <- rename(Rockcreek, city_name = id)
Rockcreek$city_name[1] <- "Rock Creek"
Rockcreek <- rename(Rockcreek, shape = geometry)
Rockcreek <- st_cast(Rockcreek, "MULTIPOLYGON")

ct <- bind_rows(ct, sunriver,Rockcreek)

## Loading highway data
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/HighwayDat/data.gdb"
hwd <- st_read(hwpath, layer="Highway_Network__2015_")
hwd <- st_transform(hwd, 2994)
hwd <- st_zm(hwd)
id <- unique(hwd$st_hwy_idx)
```


## Creating the city network using highway and city limits data

```{r, warning=FALSE}

edges <- data.frame(matrix(ncol = 3, nrow=0))
colnames(edges) <- c("to","from","hwy_id")


for(hwy_id in id) {
  sbst <- hwd[hwd$st_hwy_idx == hwy_id,]
  int <- st_intersection(sbst, ct)
  sortedV <- int %>% 
    group_by(city_name) %>%
    dplyr::summarise(m = median(beg_mp_no)) %>%
    arrange(m)
  
  sortedV$city_nameConn <- c(sortedV$city_name[-1], 0)
  edges <- rbind(edges,cbind(sortedV$city_name, sortedV$city_nameConn, rep(hwy_id,length(sortedV$city_name)))[1:length(sortedV$city_name)-1,])
}


```
creating a network with whole highways as one geometry. This will be used in the highway intersections network as well.

```{r, warning=FALSE}

fin <- c(1,1)
for (i in id) {
  val <- hwd[hwd$st_hwy_idx == i,]
  val <- st_cast(st_union(st_combine(val), by_feature = FALSE), "MULTILINESTRING")
  fin <- rbind(fin, cbind(i,val))
}


fin <- as.data.frame(fin[-1,])
colnames(fin) <- c("hwy_id","geometry")
fin <- st_as_sf(fin)
st_crs(fin) <- st_crs(ct)

```

Creating bipartite network of nearest cities to highways . 

```{r, fig.width=20, fig.height=20}

int <- st_intersection(hwd, ct)
int <- int[, c("st_hwy_idx","beg_mp_no","city_name")]
int <- int[order(unlist(int$st_hwy_idx)),]
sortedV <- int %>% 
    group_by(city_name, st_hwy_idx) %>%
    dplyr::summarize(across(matches("beg_mp_no"), mean),
                     across(matches("shape"), st_combine)) %>%
    ungroup()%>%
    arrange(st_hwy_idx, beg_mp_no)

sortedV <- st_centroid(sortedV)


nearest <- st_nearest_feature(ct, hwd)
## find the nodes with no connecting highways
cntdCts <- ct$city_name[!(ct$city_name %in% unique(sortedV$city_name))]

#find the highways closest to the cities
nearest <- data.frame(nearest)
nearest$city_names <- ct$city_name
prsnt <- nearest$city_names %in% cntdCts
nearest <- nearest[prsnt,]
ct_unCntd <- ct[prsnt,]
ct_unCntd$hwy_id <- nearest$nearest

## Creating a bipartite network using the data
# names <- c(ct_unCntd$city_name, unique(ct_unCntd$hwy_id))
# types <- c(rep(0, length(ct_unCntd$city_name)), rep(1, length(unique(ct_unCntd$hwy_id))))
# names(types) <- names
# biEdges <- pivot_longer(data.frame(cbind(ct_unCntd$city_name, 
#                                          ct_unCntd$hwy_id)), 
#                         cols = everything())
# g <- make_bipartite_graph(types, c(biEdges$value))
# 
# LO = layout_as_bipartite(g)
# LO = LO[,c(2,1)]
# 
# g %>%
#   plot(vertex.size = 1,layout = LO)
#create data frame with 0 rows and 5 columns
df <- data.frame(matrix(ncol = 3, nrow = 0))

for(i in 1:length(nearest$nearest)){
  df <- rbind(df, cbind(hwd[nearest$nearest[i],], nearest$city_names[i]))
}

df <- df[,c("nearest.city_names.i.","st_hwy_idx","beg_mp_no","shape")]
df <- st_centroid(df)

colnames(df) <- c("city_name","st_hwy_idx","beg_mp_no","shape")

finalGrph <- rbind(df, sortedV)

edges <- data.frame(matrix(ncol = 3, nrow=0))

for (hwy_id in id) {
  sbst <- finalGrph[finalGrph$st_hwy_idx == hwy_id,]
  sbst <- sbst[order(sbst$beg_mp_no),]
  city_nameConn <- c(sbst$city_name[-1], 0)
  edges <- rbind(edges,cbind(sbst$city_name, 
                                        city_nameConn, 
                                        rep(hwy_id, 
                                            length(sbst$city_name)))[1: length(sbst$city_name)-1,])
}
colnames(edges) <- c("to","from","hwy_id")

finalGrph <- finalGrph %>% 
    group_by(city_name) %>%
    dplyr::summarize(across(matches("shape"), st_combine)) %>%
    ungroup()

finalGrph <- st_coordinates(st_centroid(finalGrph))

# 
# ## find the nearest points between the cities and the highways
# nearestPts <- st_nearest_points(ct_unCntd, df, pairwise = TRUE)
# 
# nearestPts <- st_as_sf(nearestPts)
# st_crs(nearestPts) <- st_crs(fin)
# nearestLine <- nearestPts
# 
# nearestPts <- st_cast(nearestPts,"POINT")
# 
# nearestPts <- nearestPts[seq(2,104, 2),]
# 
# nearestPts$city <- df$nearest.city_names.i.
# nearestPts$hwy <- df$hwy_id
# ggplot()+
#   geom_sf(data = fin, aes(geometry = geometry) )+
#   geom_sf(data = ct, aes(geometry = shape), color = "green") +
#   geom_sf(data = nearestPts, aes(geometry = x), color = "purple", size = 1.5)+
#   geom_sf(data=nearestLine, aes(geometry = x), color = "red")

## Get coordinates for the centroid of the cities.
city_cntr <- st_coordinates(st_centroid(ct))

hwy_grph <- graph_from_data_frame(d = edges,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.size = 1, edge.color = edges$hwy_id, edge.width = 3, layout = city_cntr)

```


Adding the points to the network of cities.


```{r}


## Get coordinates for the centroid of the cities.
city_cntr <- st_coordinates(st_centroid(ct))

hwy_grph <- graph_from_data_frame(d = edges,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 3, edge.color = edges$V3, edge.width = 3, layout = city_cntr)

```


## Creating highway intersections data.

Using tmp$cnt variable that counts the number of points where the highways intersect. 
The depth value for the clustering tree d set to 16000 gives the best possible clustering based on cuts. 

```{r, warning=FALSE, fig.width=8, fig.height=8}


# Plotting the final combined data.
int <- st_intersection(fin)

mulpt <- st_collection_extract(int, "POINT")
#cent_pt <- st_centroid(mulpt)
pt <- st_cast(mulpt, "POINT")
st_crs(mulpt) <- st_crs(fin)

crsVal <- st_crs(fin)
## FIND THE CENTROID OF EACH ENTRY IN MULPT
#cent <- st_centroid(mulpt)
## Use the clustering function on points where there are multiple intersections in the same highways
gbg <- pt %>% group_by(origins) %>% 
  dplyr::summarise(cnt = n()) %>% 
  as.data.frame() %>% 
  arrange(desc(cnt))
cent <- c(1,1)

gbg <- st_as_sf(gbg)

for (i in 1:length(gbg$origins)) {
  tmp  <- gbg[i,]
  pt_coords <- tmp %>%
      st_cast("POINT") %>%
      st_transform(4326) %>%
      st_coordinates() %>%
    as.data.frame()
  
  if(tmp$cnt >= 11){
    
    mdist <- distm(pt_coords)
    
    # cluster all points using a hierarchical clustering approach
    hc <- hclust(as.dist(mdist), method="complete")
    
    # define the distance threshold, in this case 40 m
    d=16000
    k = 2
    
    # define clusters based on a tree "height" cutoff "d" and add them to the SpDataFrame
    pt_coords <- tmp %>%
      st_cast("POINT")
    st_crs(pt_coords) <- st_crs(hwd)
    pt_coords$clust <- cutree(hc, h=d)
    #print(paste0(tmp$origins, "  ", max(pt_coords$clust)))
    for (j in 1:max(pt_coords$clust)) {
      val <- pt_coords[pt_coords$clust == j , ]
      #val <- st_as_sf(val, coords = c("X","Y"), crs = 4326)
      val <- st_combine(val)
      val <- st_centroid(val)
      cent <- rbind(cent, cbind(i,val))
    }
  }
  else {
      #val <- st_as_sf(pt_coords, coords = c("X","Y"), crs = 4326)
      #val <- st_combine(val)
      #val <- st_centroid(val)
      #cent <- rbind(cent, cbind(i,val))
    val <- tmp %>%
      st_cast("POINT") %>%
      st_combine() %>%
      st_centroid()
    #st_crs(tmp) <- st_crs(cent)
    cent <- rbind(cent, cbind(i, val))
   # print(paste0(tmp$origins, "  ", "< 11"))

  }
}

cent <- as.data.frame(cent[-1,])
colnames(cent) <- c("id","geometry")
cent <- st_as_sf(cent, crs = crsVal)
#cent %>% st_set_crs(4326)
#fin %>% st_set_crs(4326)
#st_crs(fin) <- st_set_crs(hwd)

ggplot()+
#  geom_sf(data = mulpt, aes(geometry = geometry), color = "blue", size =3)+
  geom_sf(data = cent, aes(geometry = geometry), color = "red", size =1)+
  #geom_sf(data = centOld, aes(geometry = geometry), color = "green", size =1)+
  geom_sf(data = hwd, aes(geometry = shape), color = "black")
ggsave("HighwayOrig.pdf")
#centOld <- cent
```

Need to figure out what that lone red point is in the corner. 


Converting the points derived in cent variable above to create the highway network. 


## Creating network using st_buffer and using centroid


```{r}

library(mapview)
library(units)

ct_cent <- st_centroid(ct)

ct_buf10 <- st_buffer(ct_cent, dist = 10000)
ct_buf20 <- st_buffer(ct_cent, dist = 20000)
ct_buf30 <- st_buffer(ct_cent, dist = 30000)



## find which highways intersect with the buffers
#int10 <- st_intersects(ct_buf10, fin)
#int20 <- st_intersects(ct_buf20, fin)
#int30 <- st_intersects(ct_buf30, fin)

```

```{r}
## Creating a network that has multiple layers of connectivity.
## Get coordinates for the centroid of the cities.

city_cntr <- ct %>% 
  st_as_sf() %>% 
  st_centroid() %>% 
  st_cast("POINT") %>% 
  st_transform(4326) %>% 
  st_coordinates()

distMat <- distm(city_cntr)
colnames(distMat) <- ct$city_name
rownames(distMat) <- ct$city_name

#city_cntr <- cbind(city_cntr, ct$city_name)

findEdges <- function(geom, hwd, id, type){
  edges <- data.frame(matrix(ncol = 4, nrow=0))
  
  for(hwy_id in id) {
    dist<- c()
    sbst <- hwd[hwd$st_hwy_idx == hwy_id,]
    int <- st_intersection(sbst, geom)
    sortedV <- int %>% 
      group_by(city_name) %>%
      dplyr::summarise(m = median(beg_mp_no)) %>%
      arrange(m)
    #Subset of cities in the data
    #ct$city_name[ct$city_name %in% unique(int$city_name)]
    sortedV$city_nameConn <- c(sortedV$city_name[-1], 0)
    
    sortedCT <- as.matrix(cbind(sortedV$city_name, sortedV$city_nameConn), ncol =2 )#[1: length(sortedV$city_name)-1,]
    #print(hwy_id)
    #print(sortedCT)
    
    for (i in 1:dim(sortedV)[1]-1) {
      dist <- c(dist, distMat[sortedCT[i,1], sortedCT[i,2]])
    }
    ##Cannot use the milepost numbers as distance metric... it's different for different highways
    #dist <- c(sortedV$m[-1],0) - sortedV$m
    edges <- rbind(edges,cbind(sortedV$city_name, sortedV$city_nameConn,
                               rep(hwy_id,length(sortedV$city_name)),
                               dist)[1:length(sortedV$city_name)-1,])
  }
  edges <- cbind(edges, type)
  colnames(edges) <- c("to","from","hwy_id","distance","type")
  return(edges)
}

edges10 <- findEdges(ct_buf10, hwd, id, "10")
edges20 <- findEdges(ct_buf20, hwd, id,"20")
edges30 <- findEdges(ct_buf30, hwd, id,"30")


```

```{r, fig.width=6, fig.height=6}
ggplot()+
  geom_sf(data = hwd, aes(geometry = shape))+
  geom_sf(data = ct, aes(geometry = shape))+
    geom_sf(data = ct_buf30, aes(geometry = shape), color = "green")+
  geom_sf(data = ct_buf20, aes(geometry = shape), color = "blue")+
  geom_sf(data = ct_buf10, aes(geometry = shape), color = "red")

## Highway graph for circle around data of 10 kms
hwy_grph <- graph_from_data_frame(d = edges10,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.color  = NULL,edge.color = edges10$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 20 kms
hwy_grph <- graph_from_data_frame(d = edges20,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.frame.color  = NULL, edge.color = edges20$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 30 kms
hwy_grph <- graph_from_data_frame(d = edges30,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.color  = NULL,edge.color = edges30$hwy_id, edge.width = 1, layout = city_cntr)


```



## Creating network using st_buffer but using convex hull of the cities.

```{r}

ct_hull <- st_convex_hull(ct)
ct_hull_buff10 <- st_buffer(ct_hull, dist  = 10000)
ct_hull_buff20 <- st_buffer(ct_hull, dist  = 20000)
ct_hull_buff30 <- st_buffer(ct_hull, dist  = 30000)
ct_hull_buff40 <- st_buffer(ct_hull, dist  = 40000)
ct_hull_buff50 <- st_buffer(ct_hull, dist  = 50000)


## find which highways intersect with the convex hull buffers
#int_hull10 <- st_intersects(ct_hull_buff10, fin)
#int_hull20 <- st_intersects(ct_hull_buff20, fin)
#int_hull30 <- st_intersects(ct_hull_buff30, fin)
```

```{r, warning=FALSE}

#Using the find edges function to find the edges between the different convex hulls
edges_hull10 <- findEdges(ct_hull_buff10, hwd, id, "10")
edges_hull20 <- findEdges(ct_hull_buff20, hwd, id, "20")
edges_hull30 <- findEdges(ct_hull_buff30, hwd, id, "30")
edges_hull40 <- findEdges(ct_hull_buff40, hwd, id, "40")
edges_hull50 <- findEdges(ct_hull_buff50, hwd, id, "50")

```

```{r, fig.width=6, fig.height=6}
##Visualizaing the data

ggplot()+
  geom_sf(data = hwd, aes(geometry = shape))+
  geom_sf(data = ct_hull_buff50, aes(geometry = shape), color = "pink4") +
  geom_sf(data = ct_hull_buff40, aes(geometry = shape), color = "yellow") +
  geom_sf(data = ct_hull_buff30, aes(geometry = shape), color = "green") +
  geom_sf(data = ct_hull_buff20, aes(geometry = shape), color = "blue") +
  geom_sf(data = ct_hull_buff10, aes(geometry = shape), color = "red") +
    geom_sf(data = ct_hull, aes(geometry = shape), color = "purple")


## Highway graph for circle around data of 10 kms
hwy_grph <- graph_from_data_frame(d = edges_hull10,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull10$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 20 kms
hwy_grph <- graph_from_data_frame(d = edges_hull20,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull20$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 30 kms
hwy_grph <- graph_from_data_frame(d = edges_hull30,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull30$hwy_id, edge.width = 1, layout = city_cntr)

## Highway graph for circle around data of 40 kms
hwy_grph <- graph_from_data_frame(d = edges_hull40,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull40$hwy_id, edge.width = 1, layout = city_cntr)

## Highway graph for circle around data of 50 kms
hwy_grph <- graph_from_data_frame(d = edges_hull50,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull50$hwy_id, edge.width = 1, layout = city_cntr)
```


## finding edges for convex hulls that intersect with each other

```{r, fig.width = 6, fig.height=6}
ggplot()+
  geom_sf(data = hwd, aes(geometry = shape))+
  geom_sf(data = ct_hull_buff50, aes(geometry = shape), color = "pink4")+
  geom_sf(data = ct_hull_buff40, aes(geometry = shape), color = "yellow")+
  geom_sf(data = ct_hull_buff30, aes(geometry = shape), color = "green")+
  geom_sf(data = ct_hull_buff20, aes(geometry = shape), color = "blue")+
  geom_sf(data = ct_hull_buff10, aes(geometry = shape), color = "red")+
    geom_sf(data = ct_hull, aes(geometry = shape), color = "purple")

hull_edges <- st_intersects(ct_hull, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1,vertex.frame.width  = 0, edge.color = "black", layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff10, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1,vertex.frame.width  = 0,edge.color = "black", layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff20, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0,edge.color = "black",layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff30, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0 ,edge.color = "black",layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff40, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0 ,edge.color = "black",layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff50, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0 ,edge.color = "black",layout = city_cntr)


```


# Combining the three networks and color code them.


```{r, fig.width=8, fig.height=8}

options(dplyr.summarise.inform = FALSE)
edgesfull <- rbind(edges_hull10, edges_hull20, edges_hull30, edges_hull40, edges_hull50)
hwy_grph <- graph_from_data_frame(d = edgesfull ,vertices = ct$city_name, directed = FALSE)

plot.igraph(hwy_grph,vertex.label = NA, vertex.size = 1, edge.color = factor(edgesfull$type),
            edge.width = 1, layout = city_cntr)


common5 <- edgesfull %>% group_by(to,from, hwy_id) %>% dplyr::summarise( n = n(), .group = "keep") %>% ungroup()
common5$n <- as.factor(common5$n)
ecols <- c("red", "blue","green","yellow","pink4")[common5$n]
common5$ecols <- ecols
hwy_grph <- graph_from_data_frame(d = common5 ,vertices = ct$city_name, directed = FALSE)

plot.igraph(hwy_grph,vertex.label = NA, vertex.size = 1, edge.color = ecols,
            edge.width = 1, layout = city_cntr)
mults <- simplify_and_colorize(hwy_grph)#which_multiple(hwy_grph)
plot.igraph(mults, vertex.label = NA, vertex.size = 1, 
            edge.width = 1, layout = city_cntr)
#legend("bottomright", legend = levels(common3$n),pch =16, col = ecols)

```


```{r, fig.width=8, fig.height=8}

hwy_grph <- graph_from_data_frame(d = edgesfull ,vertices = ct$city_name, directed = FALSE)

mults <- simplify_and_colorize(hwy_grph)#which_multiple(hwy_grph)
pdf(file= "HighWayGraph5.pdf")
par(mar=c(0,0.2,0,0.2)+.55)
plot.igraph(mults, vertex.label = NA, vertex.size = 1, 
            edge.width = 1, layout = city_cntr)
dev.off()
```


## COVID publically avaiable data.

## COVID waste water data.

```{r}

WD <- paste0(fs::path_home(), "/Box/Preliminary Results Coronavirus Sewer Surveillance/ddPCR results/Covid/R output data/7.11.25/Combined_all_data_2025-07-11.xlsx")
  #"C:\\Users\\gauph\\Box\\Preliminary Results Coronavirus Sewer Surveillance\\Data files\\covid data files\\TestingSandbox\\RScripts"
dat <- readxl::read_excel(WD,sheet = "COVID", guess_max = 10000)
#dat <- readRDS(paste(WD, "\\..\\COVID_Data_ROutput\\ProcessedCOVIDDataInfo.rds", sep= ""))
#df <- do.call(rbind.data.frame, sapply(dat, '[', 3))
#df$Date <- as.Date(as.integer(df$Date), origin = "1970-01-01")
## cities present in ct and wastewater data
ct_sbst <- ct$city_name[ct$city_name %in% unique(dat$Location)]

## Which locations are not there in the ct database
no_ct_dat <-  unique(dat$Location)[!(unique(dat$Location) %in% ct_sbst)]
no_ct_dat

df_sbst <- dat[dat$Location %in% ct_sbst, ]

```


## Using the subset data for descriptive analysis

```{r, fig.width=7, fig.height =7}
#Coloring based on the cities considered for measurement. 
## Using the 30 km hull - roadway intersection network to create the visualizations.

## Highway graph for circle around data of 30 kms
hwy_grph <- graph_from_data_frame(d = edges_hull50,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
#plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.color = "black", edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

incl <- V(hwy_grph)$name %in% ct_sbst
V(hwy_grph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
E(hwy_grph)$weight <- edges_hull50$distance
#hwy_grph<- simplify(hwy_grph)

plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.color = V(hwy_grph)$included, vertex.frame.color = V(hwy_grph)$included, edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

```
original city from the 
start at some arbitrary city. find all the paths to red cities.

for each path check if the path goes through a red city.
  if it does, save the list and path to the closest red city.
  
## Creating graph from full edges

```{r, fig.width=7, fig.height =7}
#Coloring based on the cities considered for measurement. 
## Using the 30 km hull - roadway intersection network to create the visualizations.

## Highway graph for circle around data of 30 kms
#common5 <- edgesfull %>% group_by(to,from, hwy_id) %>% dplyr::summarise( n = n(), .group = "keep") %>% ungroup()
#common5$n <- as.factor(common5$n)
#ecols <- c("red", "blue","green","yellow","pink4")[common5$n]
#common5$ecols <- ecols
hwy_grph <- graph_from_data_frame(d = edgesfull ,vertices = ct$city_name, directed = FALSE)
#coords <- layout_(hwy_grph, city_cntr)
#plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.color = "black", edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

incl <- V(hwy_grph)$name %in% ct_sbst
V(hwy_grph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
E(hwy_grph)$weight <- edgesfull$distance
#hwy_grph<- simplify(hwy_grph)

plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.color = V(hwy_grph)$included, vertex.frame.color = V(hwy_grph)$included, edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

```

```{r, fig.height=6, fig.height=6}
#hwy_grph <- simplify(hwy_grph)
#savePath = list()
#saveDirEdges <-  data.frame(matrix(ncol = 3, nrow = 0))
#colnames(saveDirEdges) <- c("to","from", "length")

# for (i in 1:length(ct_sbst)) {
#   trav <- list()
#   path <- shortest_paths(hwy_grph, ct_sbst[i], 
#                          ct_sbst, output = "both" , 
#                          weights = round(as.numeric(E(hwy_grph)$distance)))
#   for( j in 1:48){
#     if(sum(names(unlist(path$vpath[[j]])) %in% ct_sbst) == 2){
#       curPath <- names(path$vpath[[j]])
#       savePath <- append(savePath, list(curPath))
#       saveDirEdges[nrow(saveDirEdges)+1, ] <- list(curPath[1] ,curPath[length(curPath)], length(curPath))
#     }
#   }
# }

## Creating edges from the paths that we generate using shortest path algorithm. 
## Coloring based on the weight of the edge i.e. the number of nodes between the two nodes of interest.

# DirectGrph <- graph_from_data_frame(d = saveDirEdges, vertices = ct$city_name, directed = FALSE)
# V(DirectGrph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
# DirectGrph <- simplify(DirectGrph)
# plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1,
#             vertex.color = V(DirectGrph)$included,
#             vertex.frame.color = V(DirectGrph)$included,
#             edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

## keeping all the edges from above. Checking if this would add more edges to the data
saveDirEdges <-  data.frame(matrix(ncol = 2, nrow = 0))
colnames(saveDirEdges) <- c("to","from")

for (i in 1:length(ct_sbst)) {
  
  trav <- list()
  path <- shortest_paths(hwy_grph, ct_sbst[i], 
                         ct_sbst, output = "both" , 
                         weights = round(as.numeric(E(hwy_grph)$distance)))
  
  for(j in 1:length(ct_sbst)){
    curPath <- names(unlist(path$vpath[[j]]))
    subPath <- curPath[curPath %in% ct_sbst]
    if(length(subPath) > 1){
      saveDirEdges <- rbind(saveDirEdges, cbind(subPath[1:length(subPath)-1], subPath[2:length(subPath)]))
    }
  }
}

## Creating edges from the paths that we generate using shortest path algorithm. 
## Coloring based on the weight of the edge i.e. the number of nodes between the two nodes of interest.

DirectGrph <- graph_from_data_frame(d = saveDirEdges, vertices = ct$city_name, directed = FALSE)
V(DirectGrph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = "darkgrey", edge.width = 1, layout = city_cntr)
DirectGrph <- simplify(DirectGrph)
plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = "darkgrey", edge.width = 1, layout = city_cntr)
## Save the graph for use
saveRDS(DirectGrph, "ShortestPathGrph5.rds")
```

## Creating a geographical database of different variables for the cities under consideration

```{r}

## Locations under consideration
ct_names <- unique(dat$Location)
ct_names <- ct_names[!is.na(ct_names)]

### Add code to remove other Locations that are not of interest.
####****************#######
####*
geo_df <- data.frame(matrix(0, nrow = 0, ncol = length(ct_names)))
colnames(geo_df) <- ct_names

## Setting the variables of interest as the row names 
## Variables of interest added here. Tracking two lists. One of full name and 2nd of variable name for easier coding.
## Named list

names <- c("Rural/Urban/Suburban", "Number of primary schools",
           "Number of 2ndry schools","Number of highschools", 
           "Number of Colleges/Universities","Number of tourists per year",
           "Geographical distinctions","One of 9 different regions",
           "Prone to a particular natural disaster","Number of rivers ",
           "Coastal region?")

## Variables name
geo_df_rowNames <- c() 

```

From Spatial dataset website:

Levee data:
https://spatialdata.oregonexplorer.info/geoportal/details;id=c448ffe2e1dc4ca78506e64d83285a76

Tsunami protection data:
https://spatialdata.oregonexplorer.info/geoportal/details;id=67ed182d110d4100adbbdd99bf4b2e92

Pacific Northwest Quantitative Wildfire Risk Assessment (Oregon Data) - 2018
https://spatialdata.oregonexplorer.info/geoportal/details;id=d437b41e36254af4a97ceda3a0392632

Communities at Risk: Hazard Rating
https://spatialdata.oregonexplorer.info/geoportal/details;id=8f9280aaa51844408e79dfe471dcbce8

Communities at Risk: Hazard: Elevation
https://spatialdata.oregonexplorer.info/geoportal/details;id=450e30809aef4c1aad3f6e74d2ecbd43

Oregon Conservation Strategy Ecoregions - 2016
https://spatialdata.oregonexplorer.info/geoportal/details;id=3c7862c4ae664993ad1531907b1e413e

Water rights:
https://geohub.oregon.gov/maps/21ac9a9431a14be4804badbec0cdf529/about

state park boundaries:
https://geohub.oregon.gov/maps/c1d937bae66e41068721f4474a8811a6

Exterprise Zones:
https://geohub.oregon.gov/datasets/oregon-geo::enterprise-zones-2024/about

Structural fire districts
https://geohub.oregon.gov/datasets/6e98f7ca2bb4424d9c6372f74cd47ecf_68/explore?location=44.034180%2C-120.785050%2C7.41

Watershed council boundaries:
https://geohub.oregon.gov/datasets/83f9e6d8966c45cc969a236f6baa2a0a_0/explore?location=44.054641%2C-120.574533%2C7.45

Landslide Information database:
https://geohub.oregon.gov/maps/2052a56a76c54c1ab261edb04a5d05bb/about

Soil and water conservatin zone:
https://geohub.oregon.gov/datasets/cfbd557debe54ce0956646fde6b68705_0/explore?location=44.054663%2C-120.515050%2C7.45

Hazardous material storage sites:
https://geohub.oregon.gov/datasets/f9d7eb16f6374e5f934a07acb1adaebf_0/explore?location=44.044037%2C-120.612500%2C6.47

Oregon wetland database:
https://geohub.oregon.gov/maps/c2f5f74b4e6a4d4f86b4e2bd9f6fe872/about

Electric transmission lines:
https://geohub.oregon.gov/datasets/765796b44c0d4bff8356a5e752cb68cf_0/explore?location=43.973849%2C-120.542187%2C7.27

National forest boundaries:
https://geohub.oregon.gov/datasets/b479e4bd7d70439a87e0230c99bddce5_0/explore?location=34.117737%2C-107.853800%2C4.02

Acute care hospitals in Oregon:
https://geohub.oregon.gov/datasets/3f55dc8837fd438a991c0e1e6ba98731_0/explore?location=44.372219%2C-120.305121%2C7.28

Law enforcement facilities:
https://geohub.oregon.gov/datasets/f6c921f7183e4f32b39a45f8c7c5610c_0/explore?location=44.029996%2C-120.773600%2C7.44

Oregon Ecoregions:
https://geohub.oregon.gov/datasets/c03cb0885c8c41219f9810c8a45b38e1_0/explore?location=44.053681%2C-120.514713%2C7.45

Building footprints:
https://geohub.oregon.gov/datasets/d8f8d8317615462698a1d811caa3a43a_0/explore?location=44.519547%2C-123.295485%2C11.07

Rail tracks:
https://geohub.oregon.gov/datasets/49ab3092bff64bbfab7b048c8608bb55_143/explore?location=43.978286%2C-120.584850%2C7.38

Census tracts:
https://geohub.oregon.gov/datasets/d589210147204f0286289d1636aa86ed_0/explore?location=44.083694%2C-120.583402%2C7.43

Dam facilities:
https://geohub.oregon.gov/datasets/bc0fa0f7c58a46fba44648f914f6b5b6_0/explore?location=44.362451%2C-120.605794%2C7.23

Urban boundaries:
https://geohub.oregon.gov/datasets/a020f978338647b59b9bb19590c82497_0/explore?location=44.053832%2C-120.728027%2C7.47



```{r}
## Inspecting leevee data
getwd()
df <- st_read("../Data/EstuarineLeveeProtectedLandsOCMP2011/EstuarineLeveeProtectedLandsOCMP2011.shp")

ggplot() + 
  geom_sf(data = df, size = 1.5, color = "black", fill = "cyan1") + 
  ggtitle("Leevee data") + 
  coord_sf()

```



```{r, fig.height=10, fig.width=14}
library(lubridate)
library(RColorBrewer)
library(ggiraph)
library(plotly)

df_OHA <- df[df$Study == "OHA",]
#df_OHA <- df_OHA[df_OHA$QualCall == "Negative",]

df_OHA <- df_OHA[!(is.na(df_OHA$Location)),]

df_OHA <- df_OHA[df_OHA$Location %in% ct_sbst,]

df_OHA <- df_OHA[df_OHA$CopiesPerul > 0 , ]

df_OHA <- df_OHA[!is.na(df_OHA$SampleType),]

df_OHA <- df_OHA[!(is.na(df_OHA$County)),]

gbg <- data.frame(table(df_OHA$Location, df_OHA$County))
gbg <- gbg[gbg$Freq > 0,]

## Removing gilliam county

df_OHA <- df_OHA[!(df_OHA$County == "Gilliam County"),]

#gbg <- df_OHA[df_OHA$Location == "Corvallis",]

# df_OHA <- df_OHA %>%
#   dplyr::mutate(year = lubridate::year(Date), 
#                 month = lubridate::month(Date), 
#                 day = lubridate::day(Date))

df_OHA <- df_OHA %>%
  dplyr::mutate(Month_Yr = format(as.Date(Date),"%Y-%m")) %>% 
  mutate(weekno = as.numeric(Date - min(Date, na.rm = TRUE)),
         weekno = (weekno %/% 7) +1) %>%
  group_by(weekno) %>% 
  arrange(desc(CopiesPerul)) %>%
    mutate(
        maxByVal = if_else(row_number() == 1, "1", "0")
    ) %>%
  arrange(weekno)%>%
  ungroup()

# aggr <- df_OHA %>% 
#   group_by(weekno, Location) %>%
#   arrange(weekno, desc(CopiesPerul)) %>%
#   summarise_at(vars("CopiesPerul"), max) %>%
#   mutate(maxByVal = if_else(CopiesPerul == max(CopiesPerul), Location, "0")) %>%
#   ungroup() 

aggr <- df_OHA %>%
  group_by(weekno, Location) %>%
  filter(CopiesPerul == max(CopiesPerul, na.rm = TRUE))


colors <-  c("cornflowerblue", "coral2","chocolate3", "chartreuse4","brown4",
                             "blue4","darkorchid", "orangered","gold1","cyan2",
                             "slateblue3","salmon4","darkolivegreen1", "aquamarine",
                             "firebrick2", "maroon2","dodgerblue","sienna3")

# p<- ggplot()+
#   geom_point(data =subset(aggr, CopiesPerul < 300) , aes(x = Date, y= CopiesPerul, group = Location), alpha =0.5)+
#   theme_minimal() +
#   theme(axis.line = element_line(colour = "black"),
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.border = element_blank(),
#     panel.background = element_blank(),
#     legend.position = "none") +
#   geom_point(data = subset(aggr, maxByVal == "1" & CopiesPerul < 300), aes(x = Date, y = CopiesPerul,color = County))+
#   scale_color_manual(values = colors)
# 
# ggplotly(p)

p<- ggplot()+
  geom_point(data =subset(aggr, CopiesPerul < 300) , aes(x = weekno, y= CopiesPerul, group = Location), color = "grey37",alpha =0.2)+
  theme_minimal() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.position = "none") + labs(x = "Week number stating from September 2nd 2020", y = "SARS-COV2 concentration in Copies per uL")+
  geom_point(data = subset(aggr, maxByVal == "1" & CopiesPerul < 300), aes(x = weekno, y = CopiesPerul,color = County))+
  scale_color_manual(values = colors)

ggplotly(p)

#   p <- ggplot()+
#   geom_point(data =aggr , aes(x = Date, y= CopiesPerul, color = factor(maxByVal), group = Location), alpha =0.5)+
#   theme_minimal() +
#   theme(axis.line = element_line(colour = "black"),
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.border = element_blank(),
#     panel.background = element_blank(),
#     legend.position = "none") +
#   geom_point_interactive(data = subset(aggr, maxByVal == "1"), aes(x = Date, y = CopiesPerul,color = County,  tooltip = Location))+
#   scale_color_manual(values = c("0"="orange",
#                                 "1"="steelblue"))
#   
#   
# print(girafe(ggobj = p))
#   
# 
# aggr %>% ungroup() %>%#subset(Location == "Albany")%>%
#   ggplot()+
#   geom_point(aes(x = Month_Yr, y = CopiesPerul))+
#     geom_line(aes(x = Month_Yr, y = CopiesPerul, group = Location))+
#   theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),strip.text = element_text(size=4, margin = margin()))+# element_text(angle = 90, vjust = 0.5, hjust=1))+
#   facet_wrap(~Location, scales = "free_y")

```

Creating visualization for counties/cities that never has the highest concentration or had highest concentration only a few times. Exploring correlation between demographic information and policy enactment with the observed concentration levels. Observing decline in cases or wastewater concentrations after a wave or post vaccination drives. 


Creating the visualization 
```{r}



```

Need to find the shortest paths between the must visit nodes using Dijkstras or Floyd or Bellman-Ford. Using the distances between the two cities as edge weights. 

Possibly:: https://stackoverflow.com/questions/74003506/good-algorithm-for-finding-shortest-path-for-specific-vertices
https://stackoverflow.com/questions/222413/find-the-shortest-path-in-a-graph-which-visits-certain-nodes

## Statistical questions to ask using this data.

Data:

* COVID waste water data.

* Highway Networks data. General roadways data is available, but not currently used.

* Census Demographics data.

* Publicly available COVID hospitalization and cases data.

* Possible County/City level COVID restrictions.

Possible questions:

* Are there communities in Oregon based on prevalence of COVID. Can the temporal nature of the data be used to determine communities using the flow of variants and traffic.

* Data imputation. 
  For e.g. 
      Salem stopped taking part in the waste water detection program mid 2021. 

      Can we predict the prevalence in the towns/cities nearby the ones participating in the waste water detection program.


