---
title: "MapNetworkCode"
author: "Gauri Phatak"
date: "2023-01-22"
output: pdf_document
---

```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=8, warning=FALSE)
library(tidyverse)
library(dplyr)
library(sf)
library(mapview)
library(sp)
library(usmap)
require(rgdal)
require(ggplot2)
library(raster)
library(igraph)
library(GGally)
library(ggnet)
#library(network)
#library(sna)
#library(ggplot2)
library(geosphere)
library(lubridate)
library(gganimate)
library(gifski)
library(png)
```

## Downloading the relevant data for city network and highway network.

```{r, warning=FALSE}
##Loading city limits data 
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/OSDLDataExtract/data.gdb"
ct <- st_read(hwpath, layer = "City_Limits__2016_")
ct <- st_transform(ct, 2994)

sunriver <- st_read("C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Data/SunriverShapefile/Sunriver.shp")
sunriver<-  st_transform(sunriver, crs = 2994)
sunriver <- rename(sunriver, city_name = id)
sunriver$city_name[1] <- "Sunriver"
sunriver <- rename(sunriver, shape = geometry)
sunriver <- st_cast(sunriver, "MULTIPOLYGON")

## adding rock creek shapefile
Rockcreek <- st_read("C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Data/RockcreekShapefile/Rockcreek.shp")
Rockcreek <-  st_transform(Rockcreek, crs = 2994)
Rockcreek <- rename(Rockcreek, city_name = id)
Rockcreek$city_name[1] <- "Rock Creek"
Rockcreek <- rename(Rockcreek, shape = geometry)
Rockcreek <- st_cast(Rockcreek, "MULTIPOLYGON")

## Adding warmsprings shapefile
WarmSprings <- st_read("C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/Sunbelt23/Data/WarmSpringsShapefile/WarmSprings.shp")
WarmSprings <-  st_transform(WarmSprings, crs = 2994)
WarmSprings <- rename(WarmSprings, city_name = id)
WarmSprings$city_name[1] <- "Warm Springs"
WarmSprings <- rename(WarmSprings, shape = geometry)
WarmSprings <- st_cast(WarmSprings, "MULTIPOLYGON")

ct <- bind_rows(ct, sunriver,Rockcreek, WarmSprings)

## Loading covid levels data
```

```{r}
WD <- paste0(getwd(),"/Combined_aggregated_OHA_normalized_2026-04-10.xlsx")
#"/Box/Preliminary Results Coronavirus Sewer Surveillance/ddPCR results/Covid/R output data/7.11.25/Combined_all_data_2025-07-11.xlsx")

dat <- readxl::read_excel(WD,sheet = "COVID", guess_max = 10000)

## removing KF S Suburban, Portland Tryon Creek, Ontario prison, Warm Spring SSL,
df <- dat %>% filter(!(Location %in%c("KF S Suburban", "Portland Tryon Creek", "Ontario-Prison", "Warm Springs-SSL", "Siletz Tribe") ))

## cities present in ct and wastewater data
ct_sbst <- ct$city_name[ct$city_name %in% unique(df$Location)]

unique_loc <- unique(df$Location)
unique_week <- table(df$week)
df <- df[!(is.na(df$Location)),]

gbg <- data.frame(table(df$Location, df$County))
gbg <- gbg[gbg$Freq > 0,]

## Removing gilliam county
df <- df[!(df$County == "Gilliam County"),]

## remove columns that we wont use
df <- df %>%
  dplyr::mutate(Date = lubridate::ymd(Sample_Date )) %>%
  dplyr::mutate(year = lubridate::year(Date), 
                month = lubridate::month(Date), 
                day = lubridate::day(Date))

df <- df %>%
  dplyr::mutate(Yr_Mth = format(as.Date(Date),"%Y-%m")) %>% 
  dplyr::mutate(weekno = as.numeric(Date - min(Date, na.rm = TRUE)),
         weekno = (weekno %/% 7) + 1) %>%
  group_by(weekno) %>% 
  arrange(desc(LogCopiesPerL)) %>%
  dplyr::mutate(
    maxByVal = if_else(row_number() == 1, "1", "0")
  ) %>%
  arrange(weekno)%>%
  ungroup()

df <- df %>% 
  dplyr::select(c(LogCopiesPerL ,Date,Location,MasterID,County,weekno,Yr_Mth,
           maxByVal,year,month,day )) %>%
  distinct()


aggr <- df %>%
  group_by(weekno,County, Location) %>%
  dplyr::summarise(meanLogCopiesPerL = mean(LogCopiesPerL, na.rm = TRUE),
                   across(everything() ,first)) %>% 
  dplyr::select(-c(LogCopiesPerL))

saveRDS(aggr, "aggr_04-10.rds")

## Loading highway data
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/HighwayDat/data.gdb"
hwd <- st_read(hwpath, layer="Highway_Network__2015_")
hwd <- st_transform(hwd, 2994)
hwd <- st_zm(hwd)
id <- unique(hwd$st_hwy_idx)
```


## Creating the city network using highway and city limits data

```{r, warning=FALSE}

edges <- data.frame(matrix(ncol = 3, nrow=0))
colnames(edges) <- c("to","from","hwy_id")


for(hwy_id in id) {
  sbst <- hwd[hwd$st_hwy_idx == hwy_id,]
  int <- st_intersection(sbst, ct)
  sortedV <- int %>% 
    group_by(city_name) %>%
    dplyr::summarise(m = median(beg_mp_no)) %>%
    arrange(m)
  
  sortedV$city_nameConn <- c(sortedV$city_name[-1], 0)
  edges <- rbind(edges,cbind(sortedV$city_name, sortedV$city_nameConn, rep(hwy_id,length(sortedV$city_name)))[1:length(sortedV$city_name)-1,])
}


```
creating a network with whole highways as one geometry. This will be used in the highway intersections network as well.

```{r, warning=FALSE}

fin <- c(1,1)
for (i in id) {
  val <- hwd[hwd$st_hwy_idx == i,]
  val <- st_cast(st_union(st_combine(val), by_feature = FALSE), "MULTILINESTRING")
  fin <- rbind(fin, cbind(i,val))
}


fin <- as.data.frame(fin[-1,])
colnames(fin) <- c("hwy_id","geometry")
fin <- st_as_sf(fin)
st_crs(fin) <- st_crs(ct)

```

Creating bipartite network of nearest cities to highways . 

```{r, fig.width=20, fig.height=20}

int <- st_intersection(hwd, ct)
int <- int[, c("st_hwy_idx","beg_mp_no","city_name")]
int <- int[order(unlist(int$st_hwy_idx)),]
sortedV <- int %>% 
    group_by(city_name, st_hwy_idx) %>%
    dplyr::summarize(across(matches("beg_mp_no"), mean),
                     across(matches("shape"), st_combine)) %>%
    ungroup()%>%
    arrange(st_hwy_idx, beg_mp_no)

sortedV <- st_centroid(sortedV)


nearest <- st_nearest_feature(ct, hwd)
## find the nodes with no connecting highways
cntdCts <- ct$city_name[!(ct$city_name %in% unique(sortedV$city_name))]

#find the highways closest to the cities
nearest <- data.frame(nearest)
nearest$city_names <- ct$city_name
prsnt <- nearest$city_names %in% cntdCts
nearest <- nearest[prsnt,]
ct_unCntd <- ct[prsnt,]
ct_unCntd$hwy_id <- nearest$nearest

## Creating a bipartite network using the data
#create data frame with 0 rows and 5 columns
df <- data.frame(matrix(ncol = 3, nrow = 0))

for(i in 1:length(nearest$nearest)){
  df <- rbind(df, cbind(hwd[nearest$nearest[i],], nearest$city_names[i]))
}

df <- df[,c("nearest.city_names.i.","st_hwy_idx","beg_mp_no","shape")]
df <- st_centroid(df)

colnames(df) <- c("city_name","st_hwy_idx","beg_mp_no","shape")

finalGrph <- rbind(df, sortedV)

edges <- data.frame(matrix(ncol = 3, nrow=0))

for (hwy_id in id) {
  sbst <- finalGrph[finalGrph$st_hwy_idx == hwy_id,]
  sbst <- sbst[order(sbst$beg_mp_no),]
  city_nameConn <- c(sbst$city_name[-1], 0)
  edges <- rbind(edges,cbind(sbst$city_name, 
                                        city_nameConn, 
                                        rep(hwy_id, 
                                            length(sbst$city_name)))[1: length(sbst$city_name)-1,])
}
colnames(edges) <- c("to","from","hwy_id")

finalGrph <- finalGrph %>% 
    group_by(city_name) %>%
    dplyr::summarize(across(matches("shape"), st_combine)) %>%
    ungroup()

finalGrph <- st_coordinates(st_centroid(finalGrph))

## Get coordinates for the centroid of the cities.
city_cntr <- st_coordinates(st_centroid(ct))

hwy_grph <- graph_from_data_frame(d = edges,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.size = 1, edge.color = edges$hwy_id, edge.width = 3, layout = city_cntr)

```


Adding the points to the network of cities.


```{r}
## Get coordinates for the centroid of the cities.
city_cntr <- st_coordinates(st_centroid(ct))
hwy_grph <- graph_from_data_frame(d = edges,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 3, edge.color = edges$V3, edge.width = 3, layout = city_cntr)

```


## Creating highway intersections data.

Using tmp$cnt variable that counts the number of points where the highways intersect. 
The depth value for the clustering tree d set to 16000 gives the best possible clustering based on cuts. 

```{r, warning=FALSE, fig.width=8, fig.height=8}


# Plotting the final combined data.
int <- st_intersection(fin)

mulpt <- st_collection_extract(int, "POINT")
pt <- st_cast(mulpt, "POINT")
st_crs(mulpt) <- st_crs(fin)

crsVal <- st_crs(fin)
## FIND THE CENTROID OF EACH ENTRY IN MULPT
## Use the clustering function on points where there are multiple intersections in the same highways
gbg <- pt %>% group_by(origins) %>% 
  dplyr::summarise(cnt = n()) %>% 
  as.data.frame() %>% 
  arrange(desc(cnt))
cent <- c(1,1)

gbg <- st_as_sf(gbg)

for (i in 1:length(gbg$origins)) {
  tmp  <- gbg[i,]
  pt_coords <- tmp %>%
      st_cast("POINT") %>%
      st_transform(4326) %>%
      st_coordinates() %>%
    as.data.frame()
  
  if(tmp$cnt >= 11){
    
    mdist <- distm(pt_coords)
    
    # cluster all points using a hierarchical clustering approach
    hc <- hclust(as.dist(mdist), method="complete")
    
    # define the distance threshold, in this case 40 m
    d=16000
    k = 2
    
    # define clusters based on a tree "height" cutoff "d" and add them to the SpDataFrame
    pt_coords <- tmp %>%
      st_cast("POINT")
    st_crs(pt_coords) <- st_crs(hwd)
    pt_coords$clust <- cutree(hc, h=d)
    for (j in 1:max(pt_coords$clust)) {
      val <- pt_coords[pt_coords$clust == j , ]
      val <- st_combine(val)
      val <- st_centroid(val)
      cent <- rbind(cent, cbind(i,val))
    }
  }
  else {
    val <- tmp %>%
      st_cast("POINT") %>%
      st_combine() %>%
      st_centroid()
    cent <- rbind(cent, cbind(i, val))
  }
}

cent <- as.data.frame(cent[-1,])
colnames(cent) <- c("id","geometry")
cent <- st_as_sf(cent, crs = crsVal)


ggplot()+
  geom_sf(data = ct, aes(geometry = shape), color = "red", size =1)+
  geom_sf(data = hwd, aes(geometry = shape), color = "black")


ggsave("HighwayOrig_WS_SR_RC.pdf")
```

Need to figure out what that lone red point is in the corner. 


Converting the points derived in cent variable above to create the highway network. 


## Creating network using st_buffer and using centroid


```{r}

library(mapview)
library(units)

ct_cent <- st_centroid(ct)

ct_buf10 <- st_buffer(ct_cent, dist = 10000)
ct_buf20 <- st_buffer(ct_cent, dist = 20000)
ct_buf30 <- st_buffer(ct_cent, dist = 30000)
```

```{r}
## Creating a network that has multiple layers of connectivity.
## Get coordinates for the centroid of the cities.

city_cntr <- ct %>% 
  st_as_sf() %>% 
  st_centroid() %>% 
  st_cast("POINT") %>% 
  st_transform(4326) %>% 
  st_coordinates()

distMat <- distm(city_cntr)
colnames(distMat) <- ct$city_name
rownames(distMat) <- ct$city_name

#city_cntr <- cbind(city_cntr, ct$city_name)

findEdges <- function(geom, hwd, id, type){
  edges <- data.frame(matrix(ncol = 4, nrow=0))
  
  for(hwy_id in id) {
    dist<- c()
    sbst <- hwd[hwd$st_hwy_idx == hwy_id,]
    int <- st_intersection(sbst, geom)
    sortedV <- int %>% 
      group_by(city_name) %>%
      dplyr::summarise(m = median(beg_mp_no)) %>%
      arrange(m)
    #Subset of cities in the data
    sortedV$city_nameConn <- c(sortedV$city_name[-1], 0)
    
    sortedCT <- as.matrix(cbind(sortedV$city_name, sortedV$city_nameConn), ncol =2 )

    for (i in 1:dim(sortedV)[1]-1) {
      dist <- c(dist, distMat[sortedCT[i,1], sortedCT[i,2]])
    }
    ##Cannot use the milepost numbers as distance metric... it's different for different highways
    edges <- rbind(edges,cbind(sortedV$city_name, sortedV$city_nameConn,
                               rep(hwy_id,length(sortedV$city_name)),
                               dist)[1:length(sortedV$city_name)-1,])
  }
  edges <- cbind(edges, type)
  colnames(edges) <- c("to","from","hwy_id","distance","type")
  return(edges)
}

edges10 <- findEdges(ct_buf10, hwd, id, "10")
edges20 <- findEdges(ct_buf20, hwd, id,"20")
edges30 <- findEdges(ct_buf30, hwd, id,"30")


```

```{r, fig.width=6, fig.height=6}
ggplot()+
  geom_sf(data = hwd, aes(geometry = shape))+
  geom_sf(data = ct, aes(geometry = shape))+
    geom_sf(data = ct_buf30, aes(geometry = shape), color = "green")+
  geom_sf(data = ct_buf20, aes(geometry = shape), color = "blue")+
  geom_sf(data = ct_buf10, aes(geometry = shape), color = "red")

## Highway graph for circle around data of 10 kms
hwy_grph <- graph_from_data_frame(d = edges10,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.color  = NULL,edge.color = edges10$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 20 kms
hwy_grph <- graph_from_data_frame(d = edges20,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.frame.color  = NULL, edge.color = edges20$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 30 kms
hwy_grph <- graph_from_data_frame(d = edges30,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.color  = NULL,edge.color = edges30$hwy_id, edge.width = 1, layout = city_cntr)


```



## Creating network using st_buffer but using convex hull of the cities.

```{r}

ct_hull <- st_convex_hull(ct)
ct_hull_buff10 <- st_buffer(ct_hull, dist  = 10000)
ct_hull_buff20 <- st_buffer(ct_hull, dist  = 20000)
ct_hull_buff30 <- st_buffer(ct_hull, dist  = 30000)
ct_hull_buff40 <- st_buffer(ct_hull, dist  = 40000)
ct_hull_buff50 <- st_buffer(ct_hull, dist  = 50000)

```

```{r, warning=FALSE}

#Using the find edges function to find the edges between the different convex hulls
edges_hull10 <- findEdges(ct_hull_buff10, hwd, id, "10")
edges_hull20 <- findEdges(ct_hull_buff20, hwd, id, "20")
edges_hull30 <- findEdges(ct_hull_buff30, hwd, id, "30")
edges_hull40 <- findEdges(ct_hull_buff40, hwd, id, "40")
edges_hull50 <- findEdges(ct_hull_buff50, hwd, id, "50")

```

```{r, fig.width=6, fig.height=6}
##Visualizaing the data

ggplot()+
  geom_sf(data = hwd, aes(geometry = shape))+
  geom_sf(data = ct_hull_buff50, aes(geometry = shape), color = "pink4") +
  geom_sf(data = ct_hull_buff40, aes(geometry = shape), color = "yellow") +
  geom_sf(data = ct_hull_buff30, aes(geometry = shape), color = "green") +
  geom_sf(data = ct_hull_buff20, aes(geometry = shape), color = "blue") +
  geom_sf(data = ct_hull_buff10, aes(geometry = shape), color = "red") +
  geom_sf(data = ct_hull, aes(geometry = shape), color = "purple")


## Highway graph for circle around data of 10 kms
hwy_grph <- graph_from_data_frame(d = edges_hull10,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull10$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 20 kms
hwy_grph <- graph_from_data_frame(d = edges_hull20,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull20$hwy_id, edge.width = 1, layout = city_cntr)


## Highway graph for circle around data of 30 kms
hwy_grph <- graph_from_data_frame(d = edges_hull30,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull30$hwy_id, edge.width = 1, layout = city_cntr)

## Highway graph for circle around data of 40 kms
hwy_grph <- graph_from_data_frame(d = edges_hull40,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull40$hwy_id, edge.width = 1, layout = city_cntr)

## Highway graph for circle around data of 50 kms
hwy_grph <- graph_from_data_frame(d = edges_hull50,vertices = ct$city_name, directed = FALSE)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, vertex.frame.width  = 0, vertex.color = "black",edge.color = edges_hull50$hwy_id, edge.width = 1, layout = city_cntr)
```


## finding edges for convex hulls that intersect with each other

```{r, fig.width = 6, fig.height=6}
ggplot()+
  geom_sf(data = hwd, aes(geometry = shape))+
  geom_sf(data = ct_hull_buff50, aes(geometry = shape), color = "pink4")+
  geom_sf(data = ct_hull_buff40, aes(geometry = shape), color = "yellow")+
  geom_sf(data = ct_hull_buff30, aes(geometry = shape), color = "green")+
  geom_sf(data = ct_hull_buff20, aes(geometry = shape), color = "blue")+
  geom_sf(data = ct_hull_buff10, aes(geometry = shape), color = "red")+
    geom_sf(data = ct_hull, aes(geometry = shape), color = "purple")

hull_edges <- st_intersects(ct_hull, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1,vertex.frame.width  = 0, edge.color = "black", layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff10, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1,vertex.frame.width  = 0,edge.color = "black", layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff20, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0,edge.color = "black",layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff30, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0 ,edge.color = "black",layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff40, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0 ,edge.color = "black",layout = city_cntr)

hull_edges <- st_intersects(ct_hull_buff50, sparse = FALSE)
hwy_grph <- graph_from_adjacency_matrix(hull_edges, mode = "undirected")
hwy_grph <- simplify(hwy_grph)
plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1, edge.width = 1, vertex.frame.width  = 0 ,edge.color = "black",layout = city_cntr)


```


# Combining the n networks and color code them.


```{r, fig.width=8, fig.height=8}

options(dplyr.summarise.inform = FALSE)
edgesfull <- rbind(edges_hull10, edges_hull20, edges_hull30)
hwy_grph <- graph_from_data_frame(d = edgesfull ,vertices = ct$city_name, directed = FALSE)

plot.igraph(hwy_grph,vertex.label = NA, vertex.size = 1, edge.color = factor(edgesfull$type),
            edge.width = 1, layout = city_cntr)


common5 <- edgesfull %>% group_by(to,from, hwy_id) %>% dplyr::summarise( n = n(), .group = "keep") %>% ungroup()
common5$n <- as.factor(common5$n)
ecols <- c("red", "blue","green","yellow","pink4")[common5$n]
common5$ecols <- ecols
hwy_grph <- graph_from_data_frame(d = common5 ,vertices = ct$city_name, directed = FALSE)

plot.igraph(hwy_grph,vertex.label = NA, vertex.size = 1, edge.color = ecols,
            edge.width = 1, layout = city_cntr)
mults <- simplify_and_colorize(hwy_grph)
plot.igraph(mults, vertex.label = NA, vertex.size = 1, 
            edge.width = 1, layout = city_cntr)

```


```{r, fig.width=8, fig.height=8}

hwy_grph <- graph_from_data_frame(d = edgesfull ,vertices = ct$city_name, directed = FALSE)

mults <- simplify_and_colorize(hwy_grph)
pdf(file= "HighWayGraph_30km_WS_SR_RC.pdf")
par(mar=c(0,0.2,0,0.2)+.55)
plot.igraph(mults, vertex.label = NA, vertex.size = 1, 
            edge.width = 1, layout = city_cntr)
dev.off()
```


## COVID publically avaiable data.

## COVID waste water data.

```{r}

#WD <- paste0(fs::path_home(), "/Box/Preliminary Results Coronavirus Sewer Surveillance/ddPCR results/Covid/R output data/7.11.25/Combined_all_data_2025-07-11.xlsx")
dat <- readRDS("aggr_10_7.rds")

## cities present in ct and wastewater data
ct_sbst <- ct$city_name[ct$city_name %in% unique(dat$Location)]

df_sbst <- dat[dat$Location %in% ct_sbst, ]

```


## Using the subset data for descriptive analysis
```{r, fig.width=7, fig.height =7}
#Coloring based on the cities considered for measurement. 
## Using the 50 km hull - roadway intersection network to create the visualizations.

## Highway graph for circle around data of 50 kms
hwy_grph <- graph_from_data_frame(d = edges_hull30,vertices = ct$city_name, directed = FALSE)

incl <- V(hwy_grph)$name %in% ct_sbst
V(hwy_grph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
E(hwy_grph)$weight <- edges_hull30$distance

plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.color = V(hwy_grph)$included, vertex.frame.color = V(hwy_grph)$included, edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

```

original city from the 
start at some arbitrary city. find all the paths to red cities.

for each path check if the path goes through a red city.
  if it does, save the list and path to the closest red city.
  
## Creating graph from full edges

```{r, fig.width=7, fig.height =7}
#Coloring based on the cities considered for measurement. 
## Using the 30 km hull - roadway intersection network to create the visualizations.

## Highway graph for circle around data of 30 kms
hwy_grph <- graph_from_data_frame(d = edgesfull ,vertices = ct$city_name, directed = FALSE)

incl <- V(hwy_grph)$name %in% ct_sbst
V(hwy_grph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
E(hwy_grph)$weight <- edgesfull$distance

plot.igraph(hwy_grph, vertex.label = NA, vertex.size = 1,vertex.color = V(hwy_grph)$included, vertex.frame.color = V(hwy_grph)$included, edge.color = "darkgrey", edge.width = 1, layout = city_cntr)

```

```{r, fig.height=6, fig.height=6}

## keeping all the edges from above. Checking if this would add more edges to the data
saveDirEdges <-  data.frame(matrix(ncol = 2, nrow = 0))
colnames(saveDirEdges) <- c("to","from")

for (i in 1:length(ct_sbst)) {
  
  trav <- list()
  path <- shortest_paths(hwy_grph, ct_sbst[i], 
                         ct_sbst, output = "both" , 
                         weights = round(as.numeric(E(hwy_grph)$distance)))
  
  for(j in 1:length(ct_sbst)){
    curPath <- names(unlist(path$vpath[[j]]))
    subPath <- curPath[curPath %in% ct_sbst]
    if(length(subPath) > 1){
      saveDirEdges <- rbind(saveDirEdges, cbind(subPath[1:length(subPath)-1], subPath[2:length(subPath)]))
    }
  }
}

## Creating edges from the paths that we generate using shortest path algorithm. 
## Coloring based on the weight of the edge i.e. the number of nodes between the two nodes of interest.

DirectGrph <- graph_from_data_frame(d = saveDirEdges, vertices = ct$city_name, directed = FALSE)
V(DirectGrph)$included <- ifelse(incl == TRUE, "orangered3", "grey37")
plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = "darkgrey", edge.width = 1, layout = city_cntr)
DirectGrph <- simplify(DirectGrph)
plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(DirectGrph)$included,
            vertex.frame.color = V(DirectGrph)$included,
            edge.color = "darkgrey", edge.width = 1, layout = city_cntr)
## Save the graph for use
saveRDS(DirectGrph, "ShortestPathGrph30Km_WS_SR_RC.rds")
```

```{r}
city_cntr <- ct %>% 
  st_as_sf() %>% 
  st_centroid() %>% 
  st_cast("POINT") %>% 
  st_transform(4326) %>% 
  st_coordinates()

O_attr <- as.data.frame(cbind(as.data.frame(vertex_attr(DirectGrph)), city_cntr))
saveRDS(O_attr,"O_attr_WS_SR_RC.rds")

plot.igraph(DirectGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(DirectGrph)$included, 
            vertex.frame.color = V(DirectGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = city_cntr)

```


```{r}
G_FullGrph <- delete_vertices(DirectGrph, V(DirectGrph)[included == "grey37"])
fg_attr <- O_attr[O_attr$included == "orangered3",]
fg_attr <- fg_attr[fg_attr$name %in% unique(aggr$Location), ]
plot.igraph(G_FullGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(G_FullGrph)$included, 
            vertex.frame.color = V(G_FullGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = city_cntr[V(DirectGrph)[included != "grey37"], ])
G_FullGrph <- induced_subgraph(G_FullGrph,vids = fg_attr$name)
plot.igraph(G_FullGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(G_FullGrph)$included, 
            vertex.frame.color = V(G_FullGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = city_cntr[O_attr$name %in% fg_attr$name, ])
```


```{r}

df <- as.data.frame(vertex_attr(G_FullGrph))

## joining the data and creating na's for where there is no data
# fg_attr <- left_join(fg_attr,aggr_102 %>% 
#                        dplyr::select(meanLogCopiesPerL, Location), 
#                      by = join_by(name == Location))

#G_FullGrph <- set_vertex_attr(G_FullGrph,name = "meanLogCopiesPerL", value = fg_attr$meanLogCopiesPerL )
G_FullGrph <- set_vertex_attr(G_FullGrph, name = "X", value = as.matrix(fg_attr$X ))
G_FullGrph <- set_vertex_attr(G_FullGrph, name = "Y", value = as.matrix(fg_attr$Y ))
saveRDS(G_FullGrph, "G_FullGrph30Km_WS_SR_RC.rds")

```

## Statistical questions to ask using this data.

Data:

* COVID waste water data.

* Highway Networks data. General roadways data is available, but not currently used.

* Census Demographics data.

* Publicly available COVID hospitalization and cases data.

* Possible County/City level COVID restrictions.

Possible questions:

* Are there communities in Oregon based on prevalence of COVID. Can the temporal nature of the data be used to determine communities using the flow of variants and traffic.

* Data imputation. 
  For e.g. 
      Salem stopped taking part in the waste water detection program mid 2021. 

      Can we predict the prevalence in the towns/cities nearby the ones participating in the waste water detection program.


