---
title: "Algorithm for Simultaneous Missing Data Imputation and Community Detection"
output: pdf_document
date: "2024-01-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("HelperFuncs.R")

```

## Type of missing data

Assumption: Missing at random. Lends itself to imputation problems

Handling continuous data for now.

## Multi layer Gibbs sampling

Outer posterior: Missing data handling

Inner posterior: Community detection

Simplifying assumptions: 

1. Single community : Only the inner layer is utilized
2. No missing data : Only the outer layer is utilized

Identify the distribution of missing data

Criterion for convergence of the Gibbs sampler.

Probability based community assignment

Distributions of communities.

Gives an idea of community assignment in relation to the missing data.

Probability and missing data values can give a reason for difficulty to place nodes. Gives a confidence for different possible imputed values of the missing data and the difficulty to place the nodes.

##### Steps to take:

* Start with known communities and full data.Different ways to generate data. Is there correlation between communities and the data/missing data.
- Come up with a different ways the data can be missing. Related to the community assignment 
* Multiple layer Gibbs sampler

TODO:

1. Understanding how multilayer Gibbs sampling works.

2. Create inner and outer layer based on ERGM model or Community detection. Two possible types of communities.
a. Communities are a categorical variable. Each node belongs to one community
b. Probability based communities. Can relate this to missing data. Give a confidence of community assignment based on different possible values of imputed data.

3. Two possibilities Likelihood based methods or Data imputation.


## Understadning method used by thesis* for missing data imputation.

a: Relies on combining FCS framework and network model.

b: Not many models available for imputing missing data in networks. Especially using ERGM model.

## MultiLayer Gibbs sampling:

1. Gibbs sampling for missing data:
a. Sample from Conditional distribution instead of joint distribution.


2. Adding a layer to Gibbs sampling for ERGM model.



### Starter code for multilevel imputation.

Tracking:

1. Missing data

2. Communities

a. ARI compared to priginal

b. ARI compared to previous iteration.



```{r}
SimNW <- function(pC,k,N,B){
  C = sample(1:k,N,replace = TRUE, prob = pC)
  coefs = c(prob2logit(B))
  
  ## Simulating the basis network with clusters
  g.sim <- NetworkSim(N,FALSE,B,C, NULL, coefs)
  return(g.sim)
}

AssgnCat <- function(g.sim, catName, pCat, cat){
  g.sim %v% catName <- NA
  j <- 1
  for (i in 1:k) {
    bk <- g.sim %v% catName
    bk[which(g.sim %v% 'Cluster' == i)] <- sample(cat,
                                                  length( which(g.sim %v% 'Cluster' == i)), 
                                                  prob = pCat[[i]],
                                                  replace = TRUE)
    g.sim %v% catName <- bk
  }
  g.sim %v% paste0(catName,"Orig") <- g.sim %v% catName
  g.sim <- asIgraph(g.sim)
  return(g.sim)
}

comdet <- function(g.sim, cat){
  # running regularized spectral clustering on the original network without any covariate information.
  origmem <- RegSpectralClust(g.sim, 3,regularize = TRUE)
  
  ## Covariate assisted spectral clustering 
  ## Since we are using categorical data we have to perform one hot encoding.
  X <- as.matrix(cat)
  Xdum <- as.matrix(data.frame(predict(dummyVars("~.", data = X ), newdata <- X)))
  origmemCov <- CovAssistedSpecClust(G = g.sim, Xdum, 3,
                                     Regularize =TRUE, alpha =NA,
                                     type ="non-assortative")
  return(data.frame(origmem = origmem, origmemCov = origmemCov))
}
# 

## Check correlation between the covariates and the community generated.
# 
# table(origmemCov, V(g.sim)$LOTR)
# 
# table(origmemCov, V(g.sim)$Cluster)
# 
# table(V(g.sim)$LOTR, V(g.sim)$Cluster)

# create missingness in simulated networks

## Missingness created randomly.
Mymode <- function(codes){
  names(which.max(table(codes)))
}


IterativeImpute <- function(g.sim,N,coms,niter, k,covMsng){
  ## Based on notes from 8th
  g <- g.sim
  vtxat <- as.data.frame(vertex.attributes(g))
  ## start with randomly assigned covariate values
  Midx <- list()#matrix(nrow = dim(covMsng)[1],ncol =1)
  for (i in 1:dim(covMsng)[1]) {
    Midx[[i]] <- sample(1:N,ceiling(covMsng$p[i] *N/100))
    ## setting random initial values to vertices 
    g <- set_vertex_attr(g, 
                         covMsng$name[i], 
                         index = c(Midx[[i]]), 
                         sample(unique(covMsng$cat[[i]]),
                                size  = length(Midx[[i]]),
                                replace = TRUE))
  }
  
  ## assigning random communitites to begin
  V(g)$com <- sample(1:k, size = N, replace = TRUE)
  op <- data.frame(matrix(nrow=0,ncol = 9))
  covARI <- data.frame(matrix(nrow = 0,ncol =1))
  prevComLst <- coms$origmemCov
  for (i in 1:niter){
    
    ## Run community detection 
    X <- as.matrix(vertex_attr(g, covMsng$name))#as.matrix(V(g)$LOTR)
    Xdum <- as.matrix(data.frame(predict(dummyVars("~.", data = X ),newdata <- X)))
    com <- CovAssistedSpecClust(G = g, Xdum, 3,
                                Regularize =TRUE, alpha =NA, 
                                type ="assortative",
                                kmeansIter = 1000)
    V(g)$com <- com
    
    ## Just use neighbors within cluster for imputation. If there is a tie deal with ties randomly.
    for(j in 1:length(Midx)){
      oldCov <- vertex_attr(g, name = covMsng$name[j])
      for (idx in Midx[[j]]) {
        b <- as.data.frame(vertex.attributes(g, index = neighbors(g,idx)))
        ## Number of neighbours wiht the same community assgnment as the missing node
        oldcom <- sum(b$com == V(g)$com[idx])/length(b$com)
        b <- b[b$com == V(g)$com[idx], ]
        g <- set_vertex_attr(g, covMsng$name[j], 
                             index = idx, 
                             Mymode(b[[covMsng$name[j]]]))
        ## Stopping rule: are all the neighbors in the same community
        status <- all(vertex_attr(g,index = neighbors(g,idx))$com == V(g)$com[idx])
        op <- rbind(op, cbind(i, 
                              idx, 
                              oldcom,
                              vertex_attr(g, name = covMsng$name[j],
                                          index = idx),
                              oldCov[idx],
                              vertex_attr(g.sim, name = covMsng$name[j],
                                          index = idx),
                              mclust::adjustedRandIndex(coms$origmemCov, 
                                                        V(g)$com),
                              mclust::adjustedRandIndex(prevComLst,
                                                        V(g)$com),
                              status))
        prevComLst <-  V(g)$com
      }
      v <- mclust::adjustedRandIndex(vertex_attr(g, name = covMsng$name[j],
                                                 index = Midx[[j]]),
                                     vertex_attr(g.sim, name = covMsng$name[j],
                                                 index = Midx[[j]]))
      covARI <- rbind(covARI, 
                      cbind(rep(v ,
                                times = length(Midx[[j]])))
      )
    }
    
  }
  colnames(op) <- c("iteration","MissingId","SameComm",
                    "ImputedLOTR","prevLOTR","AssignedLOTR",
                    "ARI","PrevARI","neighComStat")
  op$covARI <- covARI[,1]
  op$iteration <- as.numeric(op$iteration)
  op$MissingId <- as.numeric(op$MissingId)
  
  #op <- op[with(op,order(op[,2],op[,1])),]
  return(list(op, g))
}

plot_combinations <- function(g.sim, coms, p){
  plot.igraph( g.sim,
               edge.col = adjustcolor('black',alpha.f = 0.5),
               vertex.color = as.factor(V(g.sim)$LOTROrig),
               vertex.label = NA,
               vertex.size = 5,
               main = paste0("Imputed values :", as.character(round(mclust::adjustedRandIndex(V(g.sim)$LOTROrig,V(g.sim)$LOTR), 3)),
                             "Pcnt missing :", p))
  
  plot.igraph( g.sim,
               edge.col = adjustcolor('black',alpha.f = 0.5),
               vertex.color = as.factor(V(g.sim)$com),
               vertex.label = NA,
               vertex.size = 5,
               main = paste0("Final Community values :", as.character(round(mclust::adjustedRandIndex(V(g.sim)$Cluster,V(g.sim)$com),3)),
                             "Pcnt missing :",p))
  
  plot.igraph( g.sim,
               edge.col = adjustcolor('black',alpha.f = 0.5),
               vertex.color = V(g.sim)$Cluster,
               vertex.label = NA,
               vertex.size = 5,
               main=paste0("Original cluster assignment"," Pcnt missing :", p))
  plot.igraph( g.sim,
               edge.col = adjustcolor('black',alpha.f = 0.5),
               vertex.color = coms$origmem,
               vertex.label = NA,
               vertex.size = 5,
               main=paste0("Reg spectral clustering w/o cov ",
                           as.character(round(mclust::adjustedRandIndex(V(g.sim)$Cluster,coms$origmem),3)),
                           " Pcnt missing :", p))
  
}

## Loop
## Missingness based on mean imputation based on assigned communities.
## Update communities based on Spectral clustering with covariates algorithm.
## Future:
### Using nodecov for quantitative and nodefactor for categorical variables when I eventually use ERGM for model fitting.
```

## Categorical variables
### Highly defined cluster - same number of levels

```{r}
# network simulation with 3 groups 100 nodes and connectivity defined by B vector. Co-variates defined as below.
##Synthetic population parameters
## Going to use only undirected network
## Setting the required coefficient values
#### Example for within cluster probability is higher than between cluster.
niter= 100
k <- 3
N <- 100
## Almost equally defined clusters
pC = c(0.3,0.4,0.3)
## Highly defined clusters
B = c(0.7,0.02,0.7,0.03,0.02,0.7)
## Simulate network
g.sim <- SimNW(pC,k,N,B)
### Categorical variable correlated to the assigned clusters and same number of levels.
## Using LOTR books.
cat <- c("FOTR","TT","ROTK")
pCat <- list(c(0.6,0.2,0.2), # Cluster 1
             c(0.2,0.6,0.2), # Cluster 2
             c(0.2,0.2,0.6)) # Cluster 3

g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat)

coms <- comdet(g.sim, V(g.sim)$LOTR)

pctMsng <- c(1,5,7,10)


```


### Highly defined cluster - more levels
```{r}
### Categorical variable correlated to the assigned clusters and different number of levels.(binary variable where one is correlated to two clusters and 2nd is correlated to the last cluster. Or more than one level correlated with cluster)
### Categorical variable correlated to the assigned clusters and same number of levels.
## Using LOTR Universe books.
niter= 10
k <- 3
N <- 100
## Almost equally defined clusters
pC = c(0.3,0.4,0.3)
## Highly defined clusters
B = c(0.7,0.02,0.7,0.03,0.02,0.7)
## Simulate network
g.sim <- SimNW(pC,k,N,B)

## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pCat <- list(c(0.3,0.4,0.4,0.02,0.01,0.02,0.02,0.01,0.01), # Cluster 1
             c(0.01,0.02,0.01,0.2,0.3,0.4,0.02,0.01,0.01), # Cluster 2
             c(0.01,0.01,0.02,0.01,0.2,0.02,0.3,0.4,0.2)) # Cluster 3
g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat)

g <- data.frame(as.matrix(V(g.sim)$LOTR))
colnames(g) <- "cat"
vtx <- left_join(g,col, by = join_by(cat== cat))
#g.sim <- asIgraph(g.sim)
V(g.sim)$col <- vtx$catcol

## Regularized and cova assisted spectral clustering
coms <- comdet(g.sim, V(g.sim)$LOTR)

pctMsng <- c(5,7,10,20,30,40,50)
op <- data.frame(matrix(nrow=0,ncol = 9))
g.imp <- list()
i <-  1
for(p in pctMsng){
  covMsng <- data.frame(name = c("LOTR") ,
                        p = p,
                        cat = I(list(cat)))
  df <- IterativeImpute(g.sim, N, coms,niter,k,covMsng)
  g.imp[[i]] <- df[[2]]
  op <- rbind(op,df[[1]])
  i <- i+1
}
op$pcnt <- rep(pctMsng, times = niter*pctMsng)
opHD <- op
for(i in 1:length(pctMsng)){
  plot_combinations(g.imp[[i]], coms, pctMsng[i])
}
```



### Less defined clusters - sample number of levels
```{r}

```


## Less defined clusters - more levels
```{r}
### Categorical variable correlated to the assigned clusters and different number of levels.(binary variable where one is correlated to two clusters and 2nd is correlated to the last cluster. Or more than one level correlated with cluster)
### Categorical variable correlated to the assigned clusters and same number of levels.
## Using LOTR Universe books.
niter= 5
superiter <- 1
k <- 3
N <- 100
## Almost equally defined clusters
pC = c(0.3,0.4,0.3)
## Highly defined clusters
B = c(0.3,0.01,0.3,0.05,0.01,0.2)
## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pCat <- list(c(0.3,0.4,0.4,0.02,0.01,0.02,0.02,0.01,0.01), # Cluster 1
             c(0.01,0.02,0.01,0.2,0.3,0.4,0.02,0.01,0.01), # Cluster 2
             c(0.01,0.01,0.02,0.01,0.2,0.02,0.3,0.4,0.2)) # Cluster 3

c1 <- c("FOTR|TT|ROTK")
c2 <- c("Hob|Sil|UT")
c3 <- c("CoH|BL|FoG")
clusts <- c(c1,c2,c3)
opLD <- data.frame(matrix(nrow =0 , ncol = 15))

for(val in 1:superiter){
  ## Simulate network
  g.sim <- SimNW(pC,k,N,B, NULL)
  g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat,k)
  
  g <- data.frame(as.matrix(V(g.sim)$LOTR))
  colnames(g) <- "cat"
  vtx <- left_join(g,col, by = join_by(cat== cat))
  #g.sim <- asIgraph(g.sim)
  V(g.sim)$col <- vtx$catcol
  
  ## Regularized and cova assisted spectral clustering
  coms <- comdet(g.sim, V(g.sim)$LOTR)
  
  pctMsng <- c(5,7,10,20,30,40,50)
  op <- data.frame(matrix(nrow=0,ncol = 9))
  g.imp <- list()
  i <-  1
  for(p in pctMsng){
    covMsng <- data.frame(name = c("LOTR") ,
                          p = p,
                          cat = I(list(cat)))
    df <- IterativeImpute(g.sim, N, coms,niter,k,covMsng)
    g.imp[[i]] <- df[[2]]
    op <- rbind(op,df[[1]])
    i <- i+1
  }
  
  op$pcnt <- rep(pctMsng, times = niter*pctMsng)
  op$whichClust <- NA
  op$whichClust <- FALSE
  for(i in 1:dim(op)[1]){
    str <- c(op[i,4], op[i,6])
    op$sameClust[i] <- all(sapply(str, grepl, c1)) | all(sapply(str, grepl, c2)) | all(sapply(str, grepl, c3))
    
    if(as.numeric(which(str_detect(op$AssignedLOTR[i], clusts) == TRUE,arr.ind = TRUE)) == as.numeric(op$Cluster[i])){
      op$whichClust[i] <- TRUE
    }
    
  }
  
  op$superiter <- val
  opLD <- rbind(opLD,op)
  print(val)
  
}
# propCorClust <- opLD %>%
#     group_by(iteration, pcnt,superiter) %>%
#     dplyr::summarise(propImputed = sum(sameClust)/n(),
#                      propAssigned = sum(whichClust)/n())
for(i in 1:length(pctMsng)){
  plot_combinations(g.imp[[i]], coms, pctMsng[i])
}
op <- op[with(op,order(op[,2],op[,1],op[,11])),]

```


```{r}
## creating plots based on the grouped proportional correct cluster data

#TopLD <- opLD
#TpropCorClust <- propCorClust

TpropCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_bar(aes(x = propImputed, fill =as.factor(pcnt))) +
  ggtitle("Proportion of imputed values in the same category cluster")+
  facet_wrap(vars(color = as.factor(pcnt)), ncol =2, scales='free_y')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))

TpropCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_bar(aes(x = propAssigned, fill =as.factor(pcnt))) +
  ggtitle("Proportion of imputed values in the same category cluster")+
  facet_wrap(vars(color = as.factor(pcnt)), ncol =2, scales='free_y')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))


TpropCorClust$diff <- TpropCorClust$propAssigned - TpropCorClust$propImputed
TpropCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_histogram(aes(x = diff,fill =as.factor(pcnt))) +
  geom_vline(aes(xintercept = 0.0))+
  ggtitle("difference in proportions Assigned - Imputed")+
  facet_wrap(vars(as.factor(pcnt)), ncol =2, scales='free')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))

TpropCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_point(aes(x = propAssigned , y=propImputed, fill =as.factor(pcnt))) +
  ggtitle("Imputed vs Assigned proportion value")+
  facet_wrap(vars(color = as.factor(pcnt)), ncol =2, scales='free')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))

TpropCorClust %>%
  filter(iteration == 5) %>%
  group_by(pcnt) %>%
  dplyr::summarise(prop = sum(diff<0)/n())



```


## Uneven cluster i.e two large one small cluster size.

```{r}
### Categorical variable correlated to the assigned clusters and different number of levels.(binary variable where one is correlated to two clusters and 2nd is correlated to the last cluster. Or more than one level correlated with cluster)
### Categorical variable correlated to the assigned clusters and same number of levels.
## Using LOTR Universe books.
niter= 5
superiter <- 1
k <- 3
N <- 100
## cluster sizes
pC = c(0.1,0.5,0.4)
## cluster edge definition
B = c(0.3,0.1,0.2,0.05,0.1,0.2)
## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pCat <- list(c(0.3,0.4,0.4,0.02,0.01,0.02,0.02,0.01,0.01), # Cluster 1
             c(0.01,0.02,0.01,0.2,0.3,0.4,0.02,0.01,0.01), # Cluster 2
             c(0.01,0.01,0.02,0.01,0.2,0.02,0.3,0.4,0.2)) # Cluster 3

c1 <- c("FOTR|TT|ROTK")
c2 <- c("Hob|Sil|UT")
c3 <- c("CoH|BL|FoG")
clusts <- c(c1,c2,c3)
opLD <- data.frame(matrix(nrow =0 , ncol = 15))

for(val in 1:superiter){
  ## Simulate network
  g.sim <- SimNW(pC,k,N,B, formula = NULL)
  g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat,k)
  
  g <- data.frame(as.matrix(V(g.sim)$LOTR))
  colnames(g) <- "cat"
  vtx <- left_join(g,col, by = join_by(cat== cat))
  #g.sim <- asIgraph(g.sim)
  V(g.sim)$col <- vtx$catcol
  
  ## Regularized and cova assisted spectral clustering
  coms <- comdet(g.sim, V(g.sim)$LOTR)
  
  pctMsng <- c(5,7,10,20,30,40,50)
  op <- data.frame(matrix(nrow=0,ncol = 9))
  g.imp <- list()
  i <-  1
  for(p in pctMsng){
    covMsng <- data.frame(name = c("LOTR") ,
                          p = p,
                          cat = I(list(cat)))
    df <- IterativeImpute(g.sim, N, coms,niter,k,covMsng)
    g.imp[[i]] <- df[[2]]
    op <- rbind(op,df[[1]])
    i <- i+1
  }
  
  op$pcnt <- rep(pctMsng, times = niter*pctMsng)
  op$whichClust <- NA
  op$whichClust <- FALSE
  for(i in 1:dim(op)[1]){
    str <- c(op[i,4], op[i,6])
    op$sameClust[i] <- all(sapply(str, grepl, c1)) | all(sapply(str, grepl, c2)) | all(sapply(str, grepl, c3))
    
    if(as.numeric(which(str_detect(op$AssignedLOTR[i], clusts) == TRUE,arr.ind = TRUE)) == as.numeric(op$Cluster[i])){
      op$whichClust[i] <- TRUE
    }
  }
  op$superiter <- val
  opLD <- rbind(opLD,op)
  #print(val)
  
}

for(i in 1:length(pctMsng)){
  plot_combinations(g.imp[[i]], coms, pctMsng[i])
}
propCorClust <- opLD %>%
  group_by(iteration, pcnt,superiter) %>%
  dplyr::summarise(propImputed = sum(sameClust)/n(),
                   propAssigned = sum(whichClust)/n())



```



```{r}
## creating plots based on the grouped proportional correct cluster data

#TopLD <- opLD
#TpropCorClust <- propCorClust

propCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_bar(aes(x = propImputed, fill =as.factor(pcnt))) +
  ggtitle("Proportion of imputed values in the same category cluster")+
  facet_wrap(vars(color = as.factor(pcnt)), ncol =2, scales='free')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))
propCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_bar(aes(x = propAssigned, fill =as.factor(pcnt))) +
  ggtitle("Proportion of assigned values in the same category cluster")+
  facet_wrap(vars(color = as.factor(pcnt)), ncol =2, scales='free')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))


propCorClust$diff <- propCorClust$propAssigned - propCorClust$propImputed
propCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_histogram(aes(x = diff,fill =as.factor(pcnt))) +
  geom_vline(aes(xintercept = 0.0))+
  ggtitle("difference in proportions Assigned - Imputed")+
  facet_wrap(vars(as.factor(pcnt)), ncol =2, scales='free')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))

propCorClust %>%
  filter(iteration == 5) %>%
  ggplot()+
  geom_point(aes(x = propAssigned , y=propImputed, fill =as.factor(pcnt))) +
  ggtitle("Imputed vs Assigned proportion value")+
  facet_wrap(vars(color = as.factor(pcnt)), ncol =2, scales='free')+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.border=element_rect(fill=NA, colour="grey40"))

propCorClust %>%
  filter(iteration == 5) %>%
  group_by(pcnt) %>%
  dplyr::summarise(prop = sum(diff<0)/n())


```

```{r}

## Trying out nodemix 
## We have to create a network using both node and cluster assignment
## trying this out using the LOTR example
niter= 5
k <- 3
N <- 100
## Almost equally defined clusters
pC = c(0.3,0.4,0.3)
## Highly defined clusters
B = c(0.5,0.01,0.4,0.01,0.01,0.4)
## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pCat <- list(c(0.3,0.4,0.4,0.01,0.01,0.01,0.01,0.01,0.01), # Cluster 1
             c(0.01,0.01,0.01,0.2,0.3,0.4,0.01,0.01,0.01), # Cluster 2
             c(0.01,0.01,0.01,0.01,0.01,0.01,0.3,0.4,0.2)) # Cluster 3

c1 <- c("FOTR|TT|ROTK")
c2 <- c("Hob|Sil|UT")
c3 <- c("CoH|BL|FoG")
g.sim <- SimNW(pC,k,N,B, NULL)
g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat,k)

plot.igraph(g.sim,
            edge.col = adjustcolor('black',alpha.f = 0.5),
            vertex.color = 0,
            vertex.label = NA,
            vertex.size = 5)
g.sim <- intergraph::asNetwork(g.sim)
# fit <- ergm(g.sim ~ nodemix(c("Cluster"),levels = TRUE,levels2 = TRUE)+
#               nodemix(c("LOTR"),levels = TRUE,levels2 = TRUE))

#fit <- ergm(g.sim ~ nodemix("Cluster", levels=TRUE, levels2 = TRUE) + nodefactor(c("LOTR"), levels = TRUE): nodefactor(c("Cluster"), levels = TRUE))
# 
fit <- ergm(g.sim ~ nodemix("Cluster", levels = TRUE, levels2 =TRUE) + nodefactor(c("LOTR"), levels = TRUE):nodefactor(c("Cluster"), levels = TRUE))
#fit <- ergm(g.sim ~ nodefactor(c("Cluster"), levels=TRUE): nodefactor(c("LOTR"), levels=TRUE))
# fit <- ergm(g.sim ~ nodemix(c("LOTR")))
# 
# fit <- ergm(g.sim ~ nodemix("Cluster", levels=TRUE, levels2 = TRUE))
gbg <- data.frame(round(logit2prob(fit$coefficients), 3))
gbg <- data.frame(mix  = rownames(gbg),
                  probs = gbg[,1] ,
                  coefs = fit$coefficients)

# gbg <- gbg %>% 
#   separate_wider_delim(mix,delim = ".",
#                        names=c(NA,NA,"B1","B2"))
# 
# gbg <- gbg %>% 
#   separate_wider_delim(mix,delim = ":",
#                        names=c("Clust","Book")) %>%
#   separate(Clust, c(NA,NA,"Clust")) %>%
#   separate(Book, c(NA,NA,"Book"))

g.simf <- simulate(fit, nsim = 10)
for (i in 1:10) {
  g <- asIgraph(g.simf[[i]])
  par(mfrow=c(1,2))
  
  plot.igraph(g,
              edge.col = adjustcolor('black',alpha.f = 0.5),
              vertex.color = as.factor(V(g)$LOTR),
              vertex.label = NA,
              vertex.size = 5)
  plot.igraph(g,
              edge.col = adjustcolor('black',alpha.f = 0.5),
              vertex.color = as.factor(V(g)$Cluster),
              vertex.label = NA,
              vertex.size = 5)
}


summary(fit)

```

```{r}
## lets add a base edge probability
be <- 0.05
## probability of an edge based on a cluster
B = c(0.7,0.4,0.7,0.4,0.4,0.7)

cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
pCat <- c(0.4,0.4,0.4,0.05,0.05,0.05,0.05,0.05,0.05,
          0.05,0.05,0.05,0.4,0.4,0.4,0.05,0.05,0.05,
          0.05,0.05,0.05,0.05,0.05,0.05,0.4,0.4,0.4)# Cluster 3
#pCat <- rep(0.4, 3*length(cat))
pCat <- data.frame(cat =cat,clust = rep(c("1","2","3"), each = length(cat)), pCat  = pCat) 
pCat <- pCat[with(pCat, order(clust, cat)),]


#coefs <- prob2logit(c(B, pCat$pCat))
#coefs <- prob2logit(pCat$pCat)
coefs <- prob2logit(c(B,pCat$pCat))
nw <- network(100, directed = FALSE, density= 0)

idx <- sample(1:27,size=100, replace = TRUE, prob = pCat$pCat)

nw %v% "Cluster" <- pCat$clust[idx]#sample(c("1","2","3"), 100, replace = TRUE)
nw %v% "LOTR" <- pCat$cat[idx]#sample(cat, 100,replace= TRUE)
g <- asIgraph(nw)
par(mfrow=c(1,2))
plot.igraph(g,
            edge.col = adjustcolor('black',alpha.f = 0.5),
            vertex.color = as.factor(V(g)$LOTR),
            vertex.label = NA,
            vertex.size = 5)

plot.igraph(g,
            edge.col = adjustcolor('black',alpha.f = 0.5),
            vertex.color = as.factor(V(g)$Cluster),
            vertex.label = NA,
            vertex.size = 5)
g.simf <- simulate(nw ~ nodemix("Cluster", levels = TRUE, levels2 =TRUE)+nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE), 
                   #g.simf <- simulate(nw~ nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE), 
                   #g.simf <- simulate(nw~ edges+nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE), 
                   #g.simf <- simulate(nw~ edges+nodefactor(c("LOTR"), levels=TRUE)+ nodefactor(c("Cluster"), levels=TRUE),
                   #basis = nw,
                   nsim = 10,
                   coef = coefs)#prob2logit(c(be, rep(0.4,9), c(0.3,0.4,0.4))))
#control=control.simulate( MCMC.burnin=10000, MCMC.interval=100))
fit <- ergm(g.simf[[1]] ~ nodemix("Cluster", levels = TRUE, levels2 =TRUE)+nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE))
#fit <- ergm(g.simf[[1]] ~ nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE))
#fit <- ergm(g.simf[[1]] ~ edges+nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE))
#fit <- ergm(g.simf[[1]] ~ edges+nodefactor(c("LOTR"), levels=TRUE)+ nodefactor(c("Cluster"), levels=TRUE))
gbg <- data.frame(round(logit2prob(fit$coefficients), 3))
gbg <- data.frame(mix  = rownames(gbg),
                  probs = gbg[,1] ,
                  origCoefs  = coefs,
                  coefs = fit$coefficients)


for (i in 1:10) {
  g <- asIgraph(g.simf[[i]])
  par(mfrow=c(1,2))
  plot.igraph(g,
              edge.col = adjustcolor('black',alpha.f = 0.5),
              vertex.color = as.factor(V(g)$LOTR),
              vertex.label = NA,
              vertex.size = 5)
  
  plot.igraph(g,
              edge.col = adjustcolor('black',alpha.f = 0.5),
              vertex.color = as.factor(V(g)$Cluster),
              vertex.label = NA,
              vertex.size = 5)
}



```


```{r, warning=FALSE}

## Create a network with pre determined probabilities of categories and cluster assignment
## Fit an ERGM model to that network.
## Simulate networks based on that fit.

niter= 5
k <- 3
N <- 100
## Almost equally defined clusters
p = c(0.3,0.4,0.3)
## Highly defined clusters
B = c(0.6,0.05,0.6,0.05,0.05,0.6)
## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pC <- list(c(0.04,0.02,0.04,rep(-1.5,6)), # Cluster 1
           c(rep(-1.5,3),0.03,0.02,0.04,rep(-2.5,3)), # Cluster 2
           c(rep(-1.5,6),0.03,0.04,0.02)) # Cluster 3
c1 <- c("FOTR|TT|ROTK")
c2 <- c("Hob|Sil|UT")
c3 <- c("CoH|BL|FoG")
clusts <- c(c1,c2,c3)
cat <- sort(cat, decreasing = TRUE)
combi <- data.frame(rbind(t(combn(cat,2, simplify = TRUE)), cbind(cat,cat)))
combi$prob <- 0
for(i in 1:length(combi$cat)){
  if( which(str_detect(combi[i,1], clusts) == TRUE,arr.ind = TRUE) == which(str_detect(combi[i,2], clusts) == TRUE,arr.ind = TRUE)){
    if(combi[i,1] == combi[i,2]){
      combi$prob[i] = 0.6
    }
    else{
      combi$prob[i] = 0.3
    }
  }
  else{
    combi$prob[i] = 0.1
  }
}
colnames(combi) <- c("cat1","cat2","prob")
combi <- combi[with(combi, order(cat1, cat2)),]
pCat <- data.frame(cat =cat,clust = rep(c("1","2","3"), each = length(cat)), pCat  = unlist(pC)) 
pCat <- pCat[with(pCat, order(clust, cat)),]

C = sample(1:k,N,replace = TRUE, prob = p)
net <- network(N, directed = FALSE, density= 0 )

net %v% 'Cluster' <- C

for (i in 1:k) {
  bk <- net %v% "LOTR"
  bk[which(net %v% 'Cluster' == i)] <- sample(cat,
                                              length( which(net %v% 'Cluster' == i)), 
                                              prob =logit2prob(pC[[i]]),
                                              replace = TRUE)
  net %v% "LOTR" <- bk
}

############## plotting initial network
g <- asIgraph(net)
par(mfrow=c(1,3))
plot.igraph(g,
            edge.col = adjustcolor('black',alpha.f = 0.5),
            vertex.color = 0,
            vertex.label = NA,
            vertex.size = 5)
plot.igraph(g,
            edge.col = adjustcolor('black',alpha.f = 0.5),
            vertex.color = as.factor(V(g)$LOTR),
            vertex.label = NA,
            vertex.size = 5)
plot.igraph(g,
            edge.col = adjustcolor('black',alpha.f = 0.5),
            vertex.color = as.factor(V(g)$Cluster),
            vertex.label = NA,
            vertex.size = 5)

g.sim <- net#intergraph::asNetwork(g.sim)

g.simf <- simulate(g.sim ~ nodemix("Cluster", levels = TRUE, levels2 = TRUE) + nodemix(c("LOTR"), levels=TRUE, levels2 = TRUE),
                   nsim = 10,
                   coef = prob2logit(c(B, combi$prob)),
                   control=control.simulate( MCMC.burnin=10000, MCMC.interval=1000))

op <- logit2prob(summary(g.simf[[1]] ~ nodemix(c("Cluster"), levels=TRUE, levels2 = TRUE)+nodemix(c("LOTR"), levels=TRUE, levels2 = TRUE)))#nodefactor(c("LOTR"), levels=TRUE): nodefactor(c("Cluster"), levels=TRUE))

for (i in 1:10) {
  fit <- ergm(g.simf[[i]] ~ nodemix(c("Cluster"), levels=TRUE, levels2 = TRUE)+ nodemix(c("LOTR"), levels=TRUE, levels2 = TRUE))
  op <- cbind(op,logit2prob(fit$coefficients))
  g <- asIgraph(g.simf[[i]])
  par(mfrow=c(1,2))
  plot.igraph(g,
              edge.col = adjustcolor('black',alpha.f = 0.5),
              vertex.color = as.factor(V(g)$LOTR),
              vertex.label = NA,
              vertex.size = 5)
  
  plot.igraph(g,
              edge.col = adjustcolor('black',alpha.f = 0.5),
              vertex.color = as.factor(V(g)$Cluster),
              vertex.label = NA,
              vertex.size = 5)
}
op <- data.frame(op)
op$names <- rownames(op)
op <- op %>%
  separate(names, c(NA,NA,"c1","c2"))

```


### Network Simulation method:

1. Create a network with no edges and N nodes.
2. Cluster Assignment: For each Node randomly assign it to a cluster based on a probability vector of size k where k is number of clusters of interest.
3. Category Assignment: For each Node randomly assign a category level based on a probability matrix. This can be defined by the user. In the LOTR  example I have created a group of three books. each with a higher probability of belonging to a cluster and the res of the books have lower probability of belonging to a cluster.
4. Create a vector of coefficients for each level combination of categories and assigned clusters. This can change depending on how we want to assign the edges. Currently the edge assignment model is using both the cluster assignments and the category assignments. 
5. Based on the above now the simulations are created based on the cluster and cat assignments. 





```{r, warning=FALSE,fig.height = 10, fig.width = 10}

niter= 5
k <- 3
N <- 100
## Almost equally defined clusters
p = c(0.3,0.4,0.3)
## Highly defined clusters
B = c(0.6,0.05,0.6,0.05,0.05,0.6)
## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pC <- list(c(0.04,0.04,0.04,rep(-2.5,6)), # Cluster 1
           c(rep(-2.5,3),0.04,0.04,0.04,rep(-2.5,3)), # Cluster 2
           c(rep(-2.5,6),0.04,0.04,0.04)) # Cluster 3
c1 <- c("FOTR|TT|ROTK")
c2 <- c("Hob|Sil|UT")
c3 <- c("CoH|BL|FoG")
clusts <- c(c1,c2,c3)
cat <- sort(cat, decreasing = TRUE)
combi <- data.frame(rbind(t(combn(cat,2, simplify = TRUE)), cbind(cat,cat)))
combi$prob <- 0
for(i in 1:length(combi$cat)){
  if( which(str_detect(combi[i,1], clusts) == TRUE,arr.ind = TRUE) == which(str_detect(combi[i,2], clusts) == TRUE,arr.ind = TRUE)){
    if(combi[i,1] == combi[i,2]){
      combi$prob[i] = 0.6
    }
    else{
      combi$prob[i] = 0.3
    }
  }
  else{
    combi$prob[i] = 0.1
  }
}
colnames(combi) <- c("cat1","cat2","prob")
combi <- combi[with(combi, order(cat1, cat2)),]
pCat <- data.frame(cat =cat,clust = rep(c("1","2","3"), each = length(cat)), pCat  = unlist(pC)) 
pCat <- pCat[with(pCat, order(clust, cat)),]

superiter <- 1000
opHD <- data.frame(matrix(nrow =0 , ncol = 15))

for(val in 1:superiter){
  ## Simulate network
  #g.sim <- SimNW(pC,k,N,B, formula = NULL)
  #g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat,k)
  
  C = sample(1:k,N,replace = TRUE, prob = p)
  net <- network(N, directed = FALSE, density= 0 )
  
  net %v% 'Cluster' <- C
  
  for (i in 1:k) {
    bk <- net %v% "LOTR"
    bk[which(net %v% 'Cluster' == i)] <- sample(cat,
                                                length( which(net %v% 'Cluster' == i)), 
                                                prob =logit2prob(pC[[i]]),
                                                replace = TRUE)
    net %v% "LOTR" <- bk
  }
  g.sim <- net
  g.sim <- simulate(g.sim ~ nodemix("Cluster", levels = TRUE, levels2 = TRUE) + nodemix(c("LOTR"), levels=TRUE, levels2 = TRUE),
                    nsim = 1,
                    coef = prob2logit(c(B, combi$prob)),
                    control=control.simulate( MCMC.burnin=10000, MCMC.interval=1000))
  
  g.sim <- asIgraph(g.sim)
  V(g.sim)$LOTROrig <- V(g.sim)$LOTR
  g <- data.frame(as.matrix(V(g.sim)$LOTR))
  colnames(g) <- "cat"
  vtx <- left_join(g,col, by = join_by(cat== cat))
  #g.sim <- asIgraph(g.sim)
  V(g.sim)$col <- vtx$catcol
  
  ## Regularized and cova assisted spectral clustering
  coms <- comdet(g.sim, V(g.sim)$LOTR)
  
  pctMsng <- c(5,7,10,20,30,40,50)
  op <- data.frame(matrix(nrow=0,ncol = 9))
  g.imp <- list()
  i <-  1
  for(pt in pctMsng){
    covMsng <- data.frame(name = c("LOTR") ,
                          p = pt,
                          cat = I(list(cat)))
    df <- IterativeImpute(g.sim, N, coms,niter,k,covMsng)
    g.imp[[i]] <- df[[2]]
    op <- rbind(op,df[[1]])
    i <- i+1
  }
  
  op$pcnt <- rep(pctMsng, times = niter*pctMsng)
  op$whichClust <- NA
  op$whichClust <- FALSE
  for(i in 1:dim(op)[1]){
    str <- c(op[i,4], op[i,6])
    op$sameClust[i] <- all(sapply(str, grepl, c1)) | all(sapply(str, grepl, c2)) | all(sapply(str, grepl, c3))
    
    if(as.numeric(which(str_detect(op$AssignedLOTR[i], clusts) == TRUE,arr.ind = TRUE)) == as.numeric(op$Cluster[i])){
      op$whichClust[i] <- TRUE
    }
  }
  op$superiter <- val
  opHD <- rbind(opHD,op)
  print(val)
  
}

for(i in 1:length(pctMsng)){
  plot_combinations(g.imp[[i]], coms, pctMsng[i])
}
propCorClust <- opHD %>%
  group_by(iteration, pcnt,superiter) %>%
  dplyr::summarise(propImputed = sum(sameClust)/n(),
                   propAssigned = sum(whichClust)/n())
#saveRDS(opLD,"HighDefClusters.rds")
```




```{r, warning=FALSE,fig.height = 10, fig.width = 10}

niter= 5
k <- 3
N <- 100
## Almost equally defined clusters
p = c(0.3,0.3,0.3)
## Highly defined clusters
B = c(0.6,0.05,0.6,0.05,0.05,0.6)
## setting color codes
catcol  <- c("#B22222","#FF7F50","#FF8C00",
             "#6B8E23","#7FFF00","#32CD32",
             "#6495ED","#00008B","#87CEEB")
cat <- c("FOTR","TT","ROTK","Hob","Sil", "UT","CoH","BL","FoG")
col <- data.frame(as.matrix(cbind(catcol, cat)))
pC <- list(c(0.04,0.04,0.04,rep(-1,6)), # Cluster 1
           c(rep(-1,3),0.04,0.04,0.04,rep(-1,3)), # Cluster 2
           c(rep(-1,6),0.04,0.04,0.04)) # Cluster 3
c1 <- c("FOTR|TT|ROTK")
c2 <- c("Hob|Sil|UT")
c3 <- c("CoH|BL|FoG")
clusts <- c(c1,c2,c3)
cat <- sort(cat, decreasing = TRUE)
combi <- data.frame(rbind(t(combn(cat,2, simplify = TRUE)), cbind(cat,cat)))
combi$prob <- 0
for(i in 1:length(combi$cat)){
  if( which(str_detect(combi[i,1], clusts) == TRUE,arr.ind = TRUE) == which(str_detect(combi[i,2], clusts) == TRUE,arr.ind = TRUE)){
    if(combi[i,1] == combi[i,2]){
      combi$prob[i] = 0.6
    }
    else{
      combi$prob[i] = 0.3
    }
  }
  else{
    combi$prob[i] = 0.1
  }
}
colnames(combi) <- c("cat1","cat2","prob")
combi <- combi[with(combi, order(cat1, cat2)),]
pCat <- data.frame(cat =cat,clust = rep(c("1","2","3"), each = length(cat)), pCat  = unlist(pC)) 
pCat <- pCat[with(pCat, order(clust, cat)),]

superiter <- 100
opLD <- data.frame(matrix(nrow =0 , ncol = 15))
comDetVals <- data.frame(matrix(nrow = 0, ncol = 4))
for(val in 1:superiter){
  ## Simulate network
  #g.sim <- SimNW(pC,k,N,B, formula = NULL)
  #g.sim <- AssgnCat(g.sim, "LOTR",pCat, cat,k)
  
  C = sample(1:k,N,replace = TRUE, prob = p)
  net <- network(N, directed = FALSE, density= 0 )
  
  net %v% 'Cluster' <- C
  
  for (i in 1:k) {
    bk <- net %v% "LOTR"
    bk[which(net %v% 'Cluster' == i)] <- sample(cat,
                                                length( which(net %v% 'Cluster' == i)), 
                                                prob =logit2prob(pC[[i]]),
                                                replace = TRUE)
    net %v% "LOTR" <- bk
  }
  g.sim <- net
  g.sim <- simulate(g.sim ~ nodemix("Cluster", levels = TRUE, levels2 = TRUE) + nodemix(c("LOTR"), levels=TRUE, levels2 = TRUE),
                    nsim = 1,
                    coef = prob2logit(c(B, combi$prob)),
                    control=control.simulate( MCMC.burnin=10000, MCMC.interval=1000))
  
  g.sim <- asIgraph(g.sim)
  V(g.sim)$LOTROrig <- V(g.sim)$LOTR
  g <- data.frame(as.matrix(V(g.sim)$LOTR))
  colnames(g) <- "cat"
  vtx <- left_join(g,col, by = join_by(cat== cat))
  #g.sim <- asIgraph(g.sim)
  V(g.sim)$col <- vtx$catcol
  
  ## Regularized and cova assisted spectral clustering
  coms <- comdet(g.sim, V(g.sim)$LOTR)
  
  pctMsng <- c(5,7,10,20,30,40,50)
  op <- data.frame(matrix(nrow=0,ncol = 9))
  g.imp <- list()
  i <-  1
  for(pt in pctMsng){
    covMsng <- data.frame(name = c("LOTR") ,
                          p = pt,
                          cat = I(list(cat)))
    df <- IterativeImpute(g.sim, N, coms,niter,k,covMsng)
    g.imp[[i]] <- df[[2]]
    
    ## keeping track of community detection values for percentage missing
    comDetVals <- rbind(comDetVals,
                        c(val,pt,round(mclust::adjustedRandIndex(V(g.imp[[i]])$Cluster,V(g.imp[[i]])$com),3), 
                          round(mclust::adjustedRandIndex(V(g.imp[[i]])$Cluster,coms$origmem),3)))
    
    op <- rbind(op,df[[1]])
    i <- i+1
  }
  
  op$pcnt <- rep(pctMsng, times = niter*pctMsng)
  op$whichClust <- NA
  op$whichClust <- FALSE
  for(i in 1:dim(op)[1]){
    str <- c(op[i,4], op[i,6])
    op$sameClust[i] <- all(sapply(str, grepl, c1)) | all(sapply(str, grepl, c2)) | all(sapply(str, grepl, c3))
    
    if(as.numeric(which(str_detect(op$AssignedLOTR[i], clusts) == TRUE,arr.ind = TRUE)) == as.numeric(op$Cluster[i])){
      op$whichClust[i] <- TRUE
    }
  }
  op$superiter <- val
  opLD <- rbind(opLD,op)
  print(val)
  
}

for(i in 1:length(pctMsng)){
  plot_combinations(g.imp[[i]], coms, pctMsng[i])
}
propCorClust <- opLD %>%
  group_by(iteration, pcnt,superiter) %>%
  dplyr::summarise(propImputed = sum(sameClust)/n(),
                   propAssigned = sum(whichClust)/n())
#saveRDS(opLD,"HighDefClusters.rds")
```






