---
title: "RealDataImplementation"
output: pdf_document
date: "2025-07-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(terra)
library(sf)
library(tidyverse)
library(dplyr)
library(mapview)
library(sp)
library(usmap)
library(raster)
library(igraph)
library(GGally)
library(ggnet)
#library(network)
#library(sna)
#library(ggplot2)
#require(rgdal)
library(geosphere)
library(lubridate)
library(gganimate)
library(gifski)
library(png)
library(legendry)
library(RColorBrewer)
library(ggiraph)
library(plotly)
library(network)
library(intergraph)
library(ergm)
library(gridExtra)
library(ggpubr)
library(kableExtra)
library(ggside)

```


## Loading time series of covid data.

```{r}
##Loading city limits data 
hwpath = "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/OSDLDataExtract/data.gdb"
#rgdal::ogrListLayers(hwpath)
ct <- st_read(hwpath, layer = "City_Limits__2016_")

## reading the 2024 city limits using terra library
#citylim_path <- "C:/Users/gauph/Documents/StatisticsMS_PhD/Wastewater-Surveillance-OSU/RScripts/City_Limits_2022/City_Limits.shp"
#ct <- sf::st_read(citylim_path)

## Loading covid levels data
WD <- paste0(fs::path_home(), "/Box/Preliminary Results Coronavirus Sewer Surveillance/ddPCR results/Covid/R output data/7.11.25/Combined_all_data_2025-07-11.xlsx")
dat <- readxl::read_excel(WD,sheet = "COVID", guess_max = 10000)


## cities present in ct and wastewater data
ct_sbst <- ct$city_name[ct$city_name %in% unique(dat$Location)]

## Which locations are not there in the ct database
no_ct_dat <-  unique(dat$Location)[!(unique(dat$Location) %in% ct_sbst)]
no_ct_dat

df <- dat[dat$Location %in% ct_sbst, ]


df_OHA <- df[df$Study == "OHA",]
#df_OHA <- df_OHA[df_OHA$QualCall == "Negative",]

df_OHA <- df_OHA[!(is.na(df_OHA$Location)),]

df_OHA <- df_OHA[df_OHA$Location %in% ct_sbst,]

df_OHA <- df_OHA[df_OHA$CopiesPerul > 0 , ]

df_OHA <- df_OHA[!is.na(df_OHA$SampleType),]

df_OHA <- df_OHA[!(is.na(df_OHA$County)),]

gbg <- data.frame(table(df_OHA$Location, df_OHA$County))
gbg <- gbg[gbg$Freq > 0,]

## Removing gilliam county

df_OHA <- df_OHA[!(df_OHA$County == "Gilliam County"),]

#gbg <- df_OHA[df_OHA$Location == "Corvallis",]
## remove columns that we wont use

df_OHA <- df_OHA %>%
  mutate(Date = lubridate::mdy(Date)) %>%
  dplyr::mutate(year = lubridate::year(Date), 
                month = lubridate::month(Date), 
                day = lubridate::day(Date))

df_OHA <- df_OHA %>%
  dplyr::mutate(Month_Yr = format(as.Date(Date),"%Y-%m")) %>% 
  mutate(weekno = as.numeric(Date - min(Date, na.rm = TRUE)),
         weekno = (weekno %/% 7) + 1) %>%
  group_by(weekno) %>% 
  arrange(desc(CopiesPerul)) %>%
  mutate(
    maxByVal = if_else(row_number() == 1, "1", "0")
  ) %>%
  arrange(weekno)%>%
  ungroup()

df_OHA <- df_OHA %>% 
  select(c(CopiesPerul,Date,Location,MasterID,logCopies,County,weekno,Month_Yr,
           maxByVal,year,month,day )) %>%
  distinct()


aggr <- df_OHA %>%
  group_by(weekno, Location) %>%
  filter(CopiesPerul == max(CopiesPerul, na.rm = TRUE)) %>%
  mutate(yy = substr(year, 3,4))

# colors <-  c("cornflowerblue", "coral2","chocolate3", "chartreuse4","brown4","blue4",
#              "darkorchid", "orangered","gold1","cyan2","slateblue3","salmon4",
#              "darkolivegreen1", "aquamarine","firebrick2", "maroon2","dodgerblue",
#              "sienna3")
colors <- c(
  "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd", "#8c564b", "#e377c2",
  "#1AFF1A", "#bcbd22", "#17becf", "#aec7e8", "#ffbb78", "#98df8a", "#ff9896",
  "#c5b0d5", "#c49c94", "#f7b6d2", "#c7c7c7", "#dbdb8d", "#9edae5", "#393b79",
  "#637939", "#8c6d31", "#843c39", "#b5cf6b", "#cedb9c", "#8ca252", "#6b6ecf")
colors_cb <- c(
  "#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00",
  "#CC79A7", "#999999", "#332288", "#88CCEE", "#44AA99", "#117733", "#999933",
  "#DDCC77", "#661100", "#CC6677", "#AA4466", "#882255", "#AA4499", "#777777",
  "#5D3A9B", "#E66100", "#40B0A6", "#E1BE6A", "#1AFF1A", "#4B0092", "#FF6E3A"
)


p <- ggplot()+
  geom_point(data = subset(aggr, CopiesPerul < 300) , 
             aes(x = weekno, y = CopiesPerul, group = Location), 
             color = "grey37",alpha =0.2)+
  theme_minimal() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none") + 
  labs(x = "Week number stating from September 2nd 2020", y = "SARS-COV2 concentration in Copies per uL")+
  geom_point(data = subset(aggr, maxByVal == "1" & CopiesPerul < 300), 
             aes(x = weekno, y = CopiesPerul,color = County, group = Location))+
  scale_color_manual(values = colors)

ggplotly(p)
```


## Find the total number missing values per week.

```{r}
length(unique(aggr$Location))
unique(aggr$Location)
unique_count <- as.data.frame(table(aggr$weekno))
unique_loc <- as.data.frame(table(aggr$Location ))
ggplot(unique_count)+ geom_line(aes(x = as.numeric(Var1), y = Freq ))
```


## Decide on the week with the least number of missing data. Maybe 10 such weeks.

```{r}
## looks like week number 102 has the maximum number of locations? 36 locations out of 45. 
aggr_102 <- aggr %>% filter(weekno == 102) %>% ungroup()

```

## Loading the network.
```{r}
## Reading the shortest path graph created in MapNetworkCode.Rmd
directGrph <- readRDS("ShortestPathGrph.rds")

```

## Subsetting network with the selected week.

```{r}
city_cntr <- ct %>% 
  st_as_sf() %>% 
  st_centroid() %>% 
  st_cast("POINT") %>% 
  st_transform(4326) %>% 
  st_coordinates()

O_attr <- as.data.frame(cbind(as.data.frame(vertex_attr(directGrph)), city_cntr))

plot.igraph(directGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(directGrph)$included, 
            vertex.frame.color = V(directGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = city_cntr)


attr <- O_attr[O_attr$name %in% aggr_102$Location,]
attr <- left_join(attr, aggr_102 %>% select(Location, CopiesPerul), by=join_by(name == Location))

G_subGrph <- induced_subgraph(directGrph, vids = attr$name)
plot.igraph(G_subGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(G_subGrph)$included, 
            vertex.frame.color = V(G_subGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = as.matrix(attr[,3:4]))

```

## Running method on the above sub graph induced network.

```{r}
#
G_subGrph <- set_vertex_attr(G_subGrph, name = "X", value = as.matrix(attr[,3]))
G_subGrph <- set_vertex_attr(G_subGrph, name = "Y", value = as.matrix(attr[,4]))
## for now use nc =3
sub_attrs <-  as.data.frame(vertex_attr(G_subGrph))
sub_attrs <- left_join(sub_attrs, aggr_102 %>% 
                         select(CopiesPerul, Location), 
                       by = join_by(name == Location))
G_subGrph <- set_vertex_attr(G_subGrph,name = "CopiesPerul", value = attr$CopiesPerul)
G <- G_subGrph
nc <- 3 ## Can change
N <- nrow(sub_attrs)
lambda <- 0.0001
thresh <- 0.00005
nitermax <- 10000
dir <- "undirected"
alphaLL <- 0.001
alpha  <-  0.0001
test = TRUE
missing <- NULL
covOrig <- sub_attrs$CopiesPerul
alphaLin <- 0.001 
penalty <- "LASSO" 
seed <- 5
covInit <- "Nmean"
printFlg <- FALSE
specOP <- CovAssistedSpecClust(G, as.data.frame(sub_attrs$CopiesPerul), nc, alpha = 0.5)
C <- letters[specOP]
op <- model.matrix( ~ C - 1)
colnames(op) <- letters[1:nc]
orig <- specOP
for (i in 1:nc) {
  G <- G %>%
    set_vertex_attr(name = letters[i], 
                    value = c(op[, i]))
}
as.data.frame(vertex_attr(G))

op <- CoDA(G, nc, k = c(0, 0), o = c(0, 1), N, alpha,lambda, thresh, nitermax,orig, randomize = FALSE, 
           CovNamesLinin = c(),CovNamesLinout= c("CopiesPerul"),CovNamesLPin = c(),CovNamesLPout= c(), 
           dir,alphaLL, test, missing, covOrig,epsilon = 0, impType = "Reg",alphaLin, penalty, seed, 
           covInit, specOP )

delta <- getDelta(N)
Fin_mem <- op$Ffin > delta
colnames(Fin_mem) <- letters[1:nc]
attr <- cbind(as.data.frame(vertex_attr(G))[,1:5], Fin_mem)
eList <- as_edgelist(G)
eList <- as.data.frame(cbind(eList, pair = c(1:nrow(eList)))) %>% 
  pivot_longer(!pair, values_to = "name",names_to = "gbg") %>%
  left_join(attr %>% select(name, X, Y) )

ggplot()+ 
  geom_line(data = eList, aes(x = X, y = Y, group = pair), color = "grey80")+
  geom_point(data = attr, aes(x = X, y = Y), color = "grey30")+
  ggforce::geom_mark_hull(data = attr %>% filter(a == TRUE),
                          aes(x = X, y = Y,fill = a), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#1f77b4", color = "#1f77b4")+
  ggforce::geom_mark_hull(data = attr %>% filter(b == TRUE),
                          aes(x = X, y = Y,fill = b), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#ff7f0e", color = "#ff7f0e")+
  ggforce::geom_mark_hull(data = attr %>% filter(c == TRUE),
                          aes(x = X, y = Y,fill = c), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#2ca02c", color = "#2ca02c")+
  theme(legend.position = "bottom", panel.background = element_blank()) 


```

## Run method on the full network with missing data imputation.

```{r}
G_FullGrph <- delete_vertices(directGrph, V(directGrph)[included == "grey37"])
fg_attr <- O_attr[O_attr$included == "orangered3",]
fg_attr <- fg_attr[fg_attr$name %in% unique(aggr$Location), ]
plot.igraph(G_FullGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(G_FullGrph)$included, 
            vertex.frame.color = V(G_FullGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = city_cntr[V(directGrph)[included != "grey37"], ])
G_FullGrph <- induced_subgraph(G_FullGrph,vids = fg_attr$name)
plot.igraph(G_FullGrph, vertex.label = NA, vertex.size = 1,
            vertex.color = V(G_FullGrph)$included, 
            vertex.frame.color = V(G_FullGrph)$included, 
            edge.color = "darkgrey", edge.width = 1, 
            layout = city_cntr[O_attr$name %in% fg_attr$name, ])
```

```{r}
as.data.frame(vertex_attr(G_FullGrph))

## joining the data and creating na's for where there is no data
fg_attr <- left_join(fg_attr,aggr_102 %>% 
                       select(CopiesPerul, Location), 
                     by = join_by(name == Location))

G_FullGrph <- set_vertex_attr(G_FullGrph,name = "CopiesPerul", value = fg_attr$CopiesPerul )
G_FullGrph <- set_vertex_attr(G_FullGrph, name = "X", value = as.matrix(fg_attr$X ))
G_FullGrph <- set_vertex_attr(G_FullGrph, name = "Y", value = as.matrix(fg_attr$Y ))

```

```{r, warning=FALSE}
G <- G_FullGrph
nc <- 3 ## Can change
N <- nrow(fg_attr)
lambda <- 0.0001
thresh <- 0.00005
nitermax <- 10000
dir <- "undirected"
alphaLL <- 0.001
alpha <- 0.0001
test = TRUE
missing <- NULL
alphaLin <- 0.001 
penalty <- "LASSO" 
seed <- 5
covInit <- "Nmean"
printFlg <- FALSE
cov <- fg_attr$CopiesPerul
cov[is.na(cov)] <- mean(cov, na.rm=T)
covOrig <- as.data.frame(cov)
specOP <- CovAssistedSpecClust(G, as.data.frame(cov), nc, alpha = 0.5)
C <- letters[specOP]
op <- model.matrix( ~ C - 1)
colnames(op) <- letters[1:nc]
orig <- specOP
for (i in 1:nc) {
  G <- G %>%
    set_vertex_attr(name = letters[i], 
                    value = c(op[, i]))
}
as.data.frame(vertex_attr(G))

op <- CoDA(G, nc, k = c(0, 0), o = c(0, 1), N, alpha,lambda, thresh, nitermax,orig, randomize = FALSE,
           CovNamesLinin = c(),CovNamesLinout= c("CopiesPerul"),CovNamesLPin = c(),CovNamesLPout= c(), 
           dir,alphaLL, test, missing = NULL, covOrig,epsilon = 0, impType = "Reg",alphaLin, penalty, 
           seed, covInit, specOP )

delta <- getDelta(N)
Fin_mem <- op$Ffin > delta
colnames(Fin_mem) <- letters[1:nc]
attr <- cbind(as.data.frame(vertex_attr(G))[,1:5], Fin_mem)
eList <- as_edgelist(G)
eList <- as.data.frame(cbind(eList, pair = c(1:nrow(eList)))) %>% 
  pivot_longer(!pair, values_to = "name",names_to = "gbg") %>%
  left_join(attr %>% select(name, X, Y) )

ggplot()+ 
  geom_line(data = eList, aes(x = X, y = Y, group = pair), color = "grey80")+
  geom_point(data = attr, aes(x = X, y = Y), color = "grey30")+
  ggforce::geom_mark_hull(data = attr %>% filter(a == TRUE),
                          aes(x = X, y = Y,fill = a), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#1f77b4", color = "#1f77b4")+
  ggforce::geom_mark_hull(data = attr %>% filter(b == TRUE),
                          aes(x = X, y = Y,fill = b), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#ff7f0e", color = "#ff7f0e")+
  ggforce::geom_mark_hull(data = attr %>% filter(c == TRUE),
                          aes(x = X, y = Y,fill = c), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#2ca02c", color = "#2ca02c")+
  xlab("Latitude") + ylab("Longitude")+
  theme(legend.position = "bottom", panel.background = element_blank()) 


```

## Nocovariate CD

```{r,warning=FALSE}
op_noCov <- CoDA(G, nc, k = c(0, 0), o = c(0, 0), N, alpha, lambda,thresh, nitermax, 
                 orig, randomize = TRUE, CovNamesLinin = c(),CovNamesLinout = c(), 
                 CovNamesLPin = c(), CovNamesLPout = c(),dir, alphaLL, test, missing = missing,
                 covOrig ,epsilon = 0, impType = "", alphaLin, penalty, seed, covInit, specOP)
Fin_mem <- op_noCov$Ffin > delta
colnames(Fin_mem) <- letters[1:nc]
attr <- cbind(as.data.frame(vertex_attr(G))[,1:5], Fin_mem)
eList <- as_edgelist(G)
eList <- as.data.frame(cbind(eList, pair = c(1:nrow(eList)))) %>% 
  pivot_longer(!pair, values_to = "name",names_to = "gbg") %>%
  left_join(attr %>% select(name, X, Y) )

ggplot()+ 
  geom_line(data = eList, aes(x = X, y = Y, group = pair), color = "grey80")+
  geom_point(data = attr, aes(x = X, y = Y), color = "grey30")+
  ggforce::geom_mark_hull(data = attr %>% filter(a == TRUE),
                          aes(x = X, y = Y,fill = a), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#1f77b4", color = "#1f77b4")+
  ggforce::geom_mark_hull(data = attr %>% filter(b == TRUE),
                          aes(x = X, y = Y,fill = b), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#ff7f0e", color = "#ff7f0e")+
  ggforce::geom_mark_hull(data = attr %>% filter(c == TRUE),
                          aes(x = X, y = Y,fill = c), 
                          concavity = 3, expand = unit(2, "mm"),
                          alpha = 0.1, fill = "#2ca02c", color = "#2ca02c")+
  xlab("Latitude") + ylab("Longitude")+ggtitle("Community detection without covariates.")+
  theme(legend.position = "bottom", panel.background = element_blank()) 


```

## Compare the output of community detection of missing data and full network.

```{r}
```


## Applying the method with covariate to different weeks with missing data

```{r, warning = FALSE}

nc <- 3 ## Can change
thresh  <- 0.00005
nitermax <- 10000
dir <- "undirected"
alphaLL <- 0.001
#alpha <- 0.0001
test = FALSE
missing <- NULL
alphaLin <- 0.001
#penalty <- "LASSO"
seed <- 5
#covInit <- "Nmean"
printFlg <- FALSE

## Save output ##MSE, MSEmd, lambda, week, number of available, penalty, initializing of covariate, alpha 
finOP <- matrix(0, nrow =0, ncol = 7)
pdf("COVID_data_plots.pdf", width = 10, height = 6)  # Adjust dimensions as needed

for(covInit in c("NNmedian","Nmedian","Nmode","Nmean")){
  for(alpha in c(0.00001, 0.0001, 0.001, 0.01)){
    for(penalty in c("Ridge","LASSO","ElasticNet")){
      for(week in as.numeric(unique_count$Var1[unique_count$Freq > 24])){
        
        p <- list()
        j <- 1
        
        for(lambda in c(0.00001, 0.0001, 0.001, 0.01)){
          print(paste0("The week number ", week))
          sub_aggr <- aggr %>% filter(weekno == week) %>% ungroup()
          
          ## joining the data and creating na's for where there is no data
          fg_attr <- O_attr[O_attr$included == "orangered3",]
          fg_attr <- fg_attr[fg_attr$name %in% unique(aggr$Location), ]
          fg_attr <- left_join(fg_attr,sub_aggr %>% 
                                 select(CopiesPerul, Location), 
                               by = join_by(name == Location)) %>% distinct()
          
          G_FullGrph <- set_vertex_attr(G_FullGrph,name = "CopiesPerul", value = fg_attr$CopiesPerul )
          G_FullGrph <- set_vertex_attr(G_FullGrph, name = "X", value = as.matrix(fg_attr$X ))
          G_FullGrph <- set_vertex_attr(G_FullGrph, name = "Y", value = as.matrix(fg_attr$Y ))
          
          G <- G_FullGrph
          N <- nrow(fg_attr)
          cov <- fg_attr$CopiesPerul
          cov[is.na(cov)] <- mean(cov, na.rm=T)
          covOrig <- as.data.frame(cov)
          specOP <- CovAssistedSpecClust(G, as.data.frame(cov), nc, alpha = 0.5)
          C <- letters[specOP]
          op <- model.matrix( ~ C - 1)
          colnames(op) <- letters[1:nc]
          orig <- specOP
          for (i in 1:nc){
            G <- G %>% 
              set_vertex_attr(name = letters[i],value = c(op[, i])) 
          }
          
          op <- CoDA(G, nc, k = c(0, 0), o = c(0, 1), N, alpha,lambda, thresh, nitermax,orig, randomize = FALSE,
                     CovNamesLinin = c(),CovNamesLinout= c("CopiesPerul"),CovNamesLPin = c(),CovNamesLPout= c(), 
                     dir,alphaLL, test, missing = NULL, covOrig,epsilon = 0, impType = "Reg",alphaLin, penalty, 
                     seed, covInit, specOP )
          
          delta <- getDelta(N)
          Fin_mem <- op$Ffin > delta
          colnames(Fin_mem) <- letters[1:nc]
          attr <- cbind(as.data.frame(vertex_attr(G))[,1:5], Fin_mem)
          eList <- as_edgelist(G)
          eList <- as.data.frame(cbind(eList, pair = c(1:nrow(eList)))) %>% 
            pivot_longer(!pair, values_to = "name",names_to = "gbg") %>%
            left_join(attr %>% select(name, X, Y))
          
          p[[j]] <- ggplot() +
            geom_line(data = eList, aes(x = X, y = Y, group = pair), color = "grey80") +
            geom_point(data = attr, aes(x = X, y = Y), color = "grey30") +
            ggforce::geom_mark_hull(data = attr %>% filter(a == TRUE),aes(x = X, y = Y,fill = a), 
                                    concavity = 3, expand = unit(2, "mm"),alpha = 0.1, fill = "#1f77b4", color = "#1f77b4") +
            ggforce::geom_mark_hull(data = attr %>% filter(b == TRUE),aes(x = X, y = Y,fill = b), 
                                    concavity = 3, expand = unit(2, "mm"),alpha = 0.1, fill = "#ff7f0e", color = "#ff7f0e") +
            ggforce::geom_mark_hull(data = attr %>% filter(c == TRUE),aes(x = X, y = Y,fill = c), 
                                    concavity = 3, expand = unit(2, "mm"),alpha = 0.1, fill = "#2ca02c", color = "#2ca02c") +
            xlab("Latitude") + ylab("Longitude")+ ggtitle(paste0("lambda ", lambda)) +
            theme(legend.position = "bottom", panel.background = element_blank())
          j <- j + 1
          
          ## filling the final output
          #MSE, MSEmd, lambda, week, number of available, penalty, initializing of covariate, alpha 
          finOP <- rbind(finOP, c(tail(op$MSE,1),tail(op$MSEMD,1),week,unique_count$Freq[week],penalty,covInit,alpha))
        }
        
        pt <- ggarrange(plotlist = p, nrow = 2, ncol = 2)
        fig <- annotate_figure(pt, top = text_grob(paste0("Week ", week, 
                                                         " avail ", unique_count$Freq[week], 
                                                         " penalty ", penalty, 
                                                         " alpha ", alpha)))
        # Convert to grob and draw
        grob <- ggplotGrob(fig)
        grid.newpage()
        grid.draw(grob)
        
      }
    }
  }
}

dev.off()

colnames(finOP) <- c("MSE","MSEMD","Week","Freq","Penalty","covInit","Alpha")
saveRDS(finOP, "realCOVID_DataOP.rds")
```


